### 2024-07-06 Article_Design_of_Experiment-Chamomile.tex
06.07

% ---------------------------------------------------------------
% Preamble
% ---------------------------------------------------------------
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-dc}
%\documentclass[a4paper]{cas-dc}
%\documentclass[a4paper]{cas-sc}
% ---------------------------------------------------------------
% Make margins bigger to fit annotations. Use 1, 2 and 3. TO be removed later
%\paperwidth=\dimexpr \paperwidth + 6cm\relax
%\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
%\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
% -------------------------------------------------------------------- 
% Packages
% --------------------------------------------------------------------
% Figure packages
\usepackage{graphicx,float}
\usepackage{adjustbox}
% Text, input, formatting, and language-related packages
\usepackage[T1]{fontenc}
\usepackage{subcaption}

\usepackage{csvsimple}

% TODO package
\usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
\setlength{\marginparwidth}{1in}
% \usepackage[utf8]{inputenc}
% \usepackage[nomath]{lmodern}

% Margin and formatting specifications
%\usepackage[authoryear]{natbib}
\usepackage[sort]{natbib}
\setcitestyle{square,numbers}

 %\bibliographystyle{cas-model2-names}

\usepackage{setspace}
\usepackage{subfiles} % Best loaded last in the preamble

% \usepackage[authoryear,longnamesfirst]{natbib}

% Math packages
\usepackage{amsmath, amsthm, amssymb, amsfonts, bm, nccmath, mathdots, mathtools, bigints, ulem}

\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{shapes.geometric,angles,quotes,calc}

\usepackage{placeins}

\usepackage[final]{pdfpages}

% --------------------------------------------------------------------
% Packages Configurations
\usepackage{enumitem}
% --------------------------------------------------------------------
% (General) General configurations and fixes
\AtBeginDocument{\setlength{\FullWidth}{\textwidth}}	% Solves els-cas caption positioning issue
\setlength{\parindent}{20pt}
%\doublespacing
% --------------------------------------------------------------------
% Other Definitions
% --------------------------------------------------------------------
\graphicspath{{Figures/}}
% --------------------------------------------------------------------
% Environments
% --------------------------------------------------------------------
% ...

% --------------------------------------------------------------------
% Commands
% --------------------------------------------------------------------

% ==============================================================
% ========================== DOCUMENT ==========================
% ==============================================================
\begin{document} 
%  --------------------------------------------------------------------

% ===================================================
% METADATA
% ===================================================
\title[mode=title]{Optimal design of experiment}                      
\shorttitle{ODOE}

\shortauthors{OS, PO}

\author[1]{Oliwer Sliczniuk}[orcid=0000-0003-2593-5956]
\ead{oliwer.sliczniuk@aalto.fi}
\cormark[1]
\credit{a}

\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
\credit{b}

%\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
%\credit{c}

\address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
%\address[2]{2}

\cortext[cor1]{Corresponding author}

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the process of chamomile oil extraction from flowers. A parameter-distributed model consisting of a set of partial differential equations is used to describe the governing mass transfer phenomena in a solid-fluid environment under supercritical conditions using carbon dioxide as a solvent. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. The empirical correlations used in the model are based on the set of laboratory experiments performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. The model-based design of the experiments technique is applied in this work to improve the precision of the correlation parameters. The mass flow rate and the inlet temperature are used as decision variables to minimizing the volume of the confidence
ellipsoid. As a result, the optimal control problem is numerically solved to obtain the controls, which maximises the Fisher information contained in the yield curve.

\end{abstract}

\begin{keywords}
Supercritical extraction \sep Optimal design of experiment \sep Mathematical modelling
\end{keywords}

% ===================================================
% TITLE
% ===================================================
\maketitle

% ===================================================
% Section: Introduction
% ===================================================

\section{Introduction}

\subfile{Sections/introduction_imp}

\subfile{Sections/Literature_Review}

% ===================================================
% Section: Main
% ===================================================

\subfile{Sections/Model}

\subsection{Optimal design of experiment} \label{CH: DOE}
\subfile{Sections/Optimal_design_of_experiment}

% ===================================================
% Section: Summary
% ===================================================

\section{Results}
\subfile{Sections/Results_DOE}

\section{Conclusions} \label{CH: Conclusion}

% ===================================================
% Bibliography
% ===================================================
%% Loading bibliography style file
\newpage
%\bibliographystyle{model1-num-names}
\bibliographystyle{unsrtnat}
\bibliography{mybibfile}

%\clearpage \appendix \label{appendix}
%\section{Appendix} 
%\subfile{Sections/Qubic_EOS} \label{CH: EOS}
%\subsection{Cardano's Formula} \label{CH: Cardano}
%\subfile{Sections/Cardano}

\end{document}

### 2024-07-06 Sections/Optimal_design_of_experiment.tex
06.07

\documentclass[../Article_Design_of_Experiment.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsubsection{Maximum likelihood}

	Following the work of \citet{Walter2010}, the vector $\hat{\Theta}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function:

	{\footnotesize
	\begin{equation}
		j_{ml}(\Theta) = \pi_y (Y|\Theta) 
	\end{equation} }

	If $\Theta$ were fixed, $\pi_y(Y|\Theta)$ would be the probability density of the random vector $Y$ generated by a model with parameters $\Theta$ and observations $Y$. Considered as a function of $\Theta$, $\pi_y(Y|\Theta)$ is then called the likelihood of $Y$. The maximum-likelihood method looks for the parameter vector $\Theta$ value that gives the observed data the highest likelihood. In practice, it is often easier to look for $\hat{\Theta}_{ml}$ by maximizing the log-likelihood function, yielding the same estimate since the logarithm function is monotonically increasing.

	{\footnotesize
	\begin{equation}
		j_{ml}(\Theta) = \ln ( \pi_y (Y|\Theta) )
	\end{equation} }

	Assume that the observed outputs satisfy

	{\footnotesize
	\begin{equation}
		Y(t_i) = y(t_i, \Theta^*) + \epsilon_i, \qquad i=1,...,n_t
	\end{equation} }

	where the vector $y(t_i, \Theta^*)$ is the output of a deterministic model, $\Theta^*$ is the true value of the parameter vector, and the error $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$. Since the $\epsilon_i$ are independent

	{\footnotesize
	\begin{equation}
		\pi_{\epsilon}(\epsilon_1, \epsilon_2, ..., \epsilon_{n_t}) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(\epsilon_i)
	\end{equation} }

	Consider the output error

	{\footnotesize
	\begin{equation} \label{EQ:Error_measurment}
		e^y(t_i, \Theta) = Y(t_i) - y(t_i, \Theta)
	\end{equation} }

	For the true value of the parameters, it satisfies $e^y(t_i, \Theta^*)\\=\epsilon_i$. and, since $y$ is deterministic, $\pi_{y_i} (Y(t_i)|\Theta) = \pi_{\epsilon_i} (e^y(t_i),\Theta)$. The likelihood of the $n_t$ observations can be written as

	{\footnotesize
	\begin{equation}
		\pi_y (Y|\Theta) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(e^y(t_i,\Theta)) =  \prod_{i=1}^{n_t} \pi_{\epsilon_i}(Y(t_i) - y(t_i, \Theta))
	\end{equation} }

	If the noise is assumed to follow the normal distribution with the standard deviation $\sigma$, which is known from the parameter estimation:

	{\footnotesize
	\begin{equation}
		\pi_y (Y|\Theta) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{Y(t_i) - y(t_i, \Theta)}{\sigma_{t_i}} \right)^2 \right)
	\end{equation} }

	The associated log-likelihood can be written as

	{\footnotesize
	\begin{equation}
		\ln (\pi_y (Y|\Theta)) = (\text{term independent of } \Theta) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{Y(t_i) - y(t_i, \Theta)}{\sigma_{t_i}} \right)^2
	\end{equation} }

	Its gradient is thus

	{\footnotesize
	\begin{equation}
		\frac{\partial}{\partial \Theta} \ln (\pi_y (Y|\Theta)) =  \sum_{i=1}^{n_t}  \left[ \left( \frac{Y(t_i) - y(t_i, \Theta)}{\sigma_{t_i}^2} \right) \frac{\partial y(t_i, \Theta)}{\partial \Theta} \right]
	\end{equation} }

	\subsubsection{Fisher information}

	The Fisher information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable. The Fisher information is related to the second derivative (or the curvature) of the log-likelihood function with respect to the parameter. This relationship provides a measure of how "sensitive" the likelihood is to changes in the parameter value. The Fisher information matrix $\mathcal{F}$ can be calculated as follow.

	{\scriptsize
	\begin{equation}
		\begin{aligned}
		&\mathcal{F}(\Theta) = - \mathop{\mathbb{E}}_{Y|\Theta} \left[ \frac{\partial^2 \ln (\pi_y (Y|\Theta))}{\partial \Theta \partial \Theta^\top} \right] = \mathop{\mathbb{E}}_{Y|\Theta} \left[ \frac{\partial \ln (\pi_y (Y|\Theta))}{\partial \Theta} \frac{\partial \ln (\pi_y (Y|\Theta))}{\partial \Theta^\top} \right] \nonumber \\
		&= \mathop{\mathbb{E}}_{Y|\Theta} \left[ \sum_{k=1}^{n_t} \left( \frac{Y(t_k) - y(t_k, \Theta)}{\sigma_{t_k}^2} \frac{\partial y(t_k, \Theta)}{\partial \Theta} \right) \times  \sum_{i=1}^{n_t} \left( \frac{Y(t_i) - y(t_i, \Theta)}{\sigma_{t_i}^2} \frac{\partial y(t_i, \Theta)}{\partial \Theta^\top} \right) \right] \nonumber \\
		&= \mathop{\mathbb{E}}_{Y|\Theta} \left[ \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \left[ \left( \frac{Y(t_k) - y(t_k, \Theta)}{\sigma_{t_k}^2} \frac{\partial y(t_k, \Theta)}{\partial \Theta} \right) \times \left( \frac{Y(t_i) - y(t_i, \Theta)}{\sigma_{t_i}^2} \frac{\partial y(t_i, \Theta)}{\partial \Theta^\top} \right) \right] \right] \nonumber \\
		&= \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \mathop{\mathbb{E}}_{Y|\Theta} \left[ \left( \frac{Y(t_k) - y(t_k, \Theta)}{\sigma_{t_k}^2} \frac{\partial y(t_k, \Theta)}{\partial \Theta} \right) \times \left( \frac{Y(t_i) - y(t_i, \Theta)}{\sigma_{t_i}^2} \frac{\partial y(t_i, \Theta)}{\partial \Theta^\top} \right) \right] \nonumber \\
		&= \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \frac{1}{\sigma_{t_k}^2} \frac{\partial y(t_k, \Theta)}{\partial \Theta} \frac{1}{\sigma_{t_i}^2} \frac{\partial y(t_i, \Theta)}{\partial \Theta^\top} \mathop{\mathbb{E}}_{Y|\Theta} \left[ \left( Y(t_k) - y(t_k, \Theta) \right) \times \left( Y(t_i) - y(t_i, \Theta) \right) \right] 
	\end{aligned} 
	\end{equation} }

	Considering the mismatch between the dataset and the model output, the Equation \ref{EQ:Error_measurment} can be used to redefine the expectation $\mathop{\mathbb{E}}_{Y|\Theta}$ as $\mathop{\mathbb{E}}_{Y|\Theta} \left[ \left( Y(t_i) - y(t_i, \Theta) \right) \left( Y(t_k) - y(t_k, \Theta) \right) \right]\\ = \mathop{\mathbb{E}}_{Y|\Theta} \left[ \epsilon_i \epsilon_k \right]$. For $i=k$, the expectation of $\epsilon_i$ is the variance of the noise $\sigma_{t_i}^2$. Analogously, the expectation becomes 0 if $i \neq k$ because the measurement noises are independent at different times.

	{\footnotesize
	\begin{equation}
		\mathop{\mathbb{E}}_{Y|\Theta} \left[ \left( Y(t_i) - y(t_k, \Theta) \right) \left( Y(t_i) - y(t_i, \Theta) \right) \right] = \sigma_{t_i}^2 \delta_{ik}
	\end{equation} }

	where $\delta_{ik}$ represents the Kronecker delta. Given the property of the Kronecker delta, the double summation in the Fisher Information matrix reduces to a single summation:

	{\footnotesize
	\begin{equation}
		\mathcal{F}(\Theta) = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y(t_i, \Theta)}{\partial \Theta} \frac{\partial y(t_i, \Theta)}{\partial \Theta^\top} \right)
	\end{equation} }

	If every experiment at time $t_i$ is independent and characterized by its own $\sigma_{t_i}$, then the Fisher information matrix can be presented in the more compact way:

	{\footnotesize
	\begin{equation}
		\mathcal{F}(\Theta) = \frac{\partial y(t, \Theta)}{\partial \Theta} \begin{bmatrix}
			\frac{1}{\sigma_{t_1}^2} & 0 & 0\\
			0 & \ddots & 0 \\
			0 & 0 & \frac{1}{\sigma_{t_{n_t}}^2} 
		\end{bmatrix}\ \frac{\partial y(t, \Theta)}{\partial \Theta^\top} 
	\end{equation} }

	\subsubsection{Cramer-Rao inequality}

	Let $\hat{\Theta}$ be an (absolutely) unbiased estimator $\Theta^*$, i.e. such that it were possible to replicate the same experiment and estimate $\hat{\Theta}$ an infinite number of times, the mean of the estimates would coincide with the true value. Let $\Sigma$ be the covariance matrix of this estimator. Since $\hat{\Theta}$ is unbiased, $\Sigma$ can be written as

	{\footnotesize
	\begin{equation}
		\Sigma = \mathop{\mathbb{E}}_{Y|\Theta^*} \left[ \left( \hat{\Theta}(Y) - \Theta^* \right) \left( \hat{\Theta}(Y) - \Theta^* \right)^\top \right]
	\end{equation} }

	which quantifies how the estimates are spread around the true value $\Theta^*$. One would like the estimates to be as concentrated as possible around this true value. An estimator $\hat{\Theta}_1$ with covariance matrix $\Sigma_1$ is said to be more efficient than an estimator $\hat{\Theta}_2$ with covariance matrix $\Sigma_2$ if $\Sigma_1 < \Sigma_2$, that is if $\Sigma_2 - \Sigma_1$ is positive-definite (i.e. if all the eigenvalues of $\Sigma_2-\Sigma_1$ are strictly positive). Estimators with high efficiency are expected to have $\Sigma$ as small as possible.

	Under the hypotheses that:

	\begin{itemize}
		\item the set of all data vectors $Y$ with $\pi_y(Y|\Theta) > 0$ does not depend on $\Theta$
		\item $\frac{\partial \pi_y(Y|\Theta)}{\partial \Theta_i}~\left(i=1,2,...,n_\Theta\right)$ is absolutely integrable
		\item $\mathop{\mathbb{E}}_{Y|\Theta} \left[ \frac{\partial \ln (\pi_y (Y|\Theta))}{\partial \Theta} \frac{\partial \ln (\pi_y (Y|\Theta))}{\partial \Theta^\top} \right]$ exists and is invertible
	\end{itemize}

	The Cramer-Rao inequality provides that the covariance of any absolutely unbiased estimator satisfies

	{\footnotesize
	\begin{equation}
		\Sigma \geq \mathcal{F}^{-1}(\Theta^*)
	\end{equation} }

	In other words, the precision to which we can estimate $\Theta$ is limited by the Fisher information of the likelihood function. Based on the Cramer-Rao inequality, the Fisher information matrix can used to calculate the covariance matrices associated with maximum-likelihood estimates.

	\subsubsection{Optimal experimental design}

	The optimal design of experiments (DOE) is a statistical concept that refers to the process of planning an experiment, which allow parameters to be estimated without bias and with minimum variance. Optimal design ensures that the experiment can provide the most informative data possible. This often involves balancing the study of main effects and interactions between factors. Moreover, by efficiently planning experiments, optimal design aims to reduce the overall resources required, such as time, materials, and manpower.

	The methodology for data to estimate the parameters of a specific model is influenced by a series of qualitative decisions made throughout the experimental and modelling process, such as: a model structure, a location of sensors or an equipment. Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, etc.). Experiment design aims to determine experimental conditions adapted to the final purpose of the modeling.

	%Assume that the i'th scalar observation can be written as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ (the i'th support point) describes the experimental conditions (e.g., measurement time, the shape of input, etc.) under which the i'th observation is to be collected. When $n_t$ such observations are taken, the concatenation of the vectors $\xi_i$'s yields the $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which characterizes all experimental conditions to be optimized. To make the experiment design realistic, it is necessary to consider several constraints, e.g., the experiments' duration, the inlet stream's temperature, and the minimum time between samples. Let $\bar{\Xi}$ be the set of all feasible values for $\Xi$.

	Let's consider that each scalar observation in a study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ representing the specific experimental conditions (such as the sampling time, operating conditions, etc.) under which the i'th observation is gathered. When collecting $n_t$ such observations, the assembly of these $\xi_i$ vectors forms the matrix $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which combine all the experimental conditions that need optimization. In order to align the design of the experiment with practical realities, it's important to take into account various constraints, such as the total duration of the experiments, the maximum temperature of the inlet stream, or the minimum interval between sampling events. The set of all possible combinations for $\bar{\Xi}$ that adhere to these constraints is denoted as $\Xi$.

	%The definition of a cost function $j$ then permits the optimal experiment design to be cast as a constrained optimization problem, where the optimal experiment $\Xi^*$ is defined by

	The formulation of a cost function $j$ allows for the framing of optimal experiment design as a problem of constrained optimization. In this context, the optimal experiment, denoted as $\Xi^*$:

	{\footnotesize
	\begin{equation}
		\Xi^* = \arg~\underset{\Xi \in \bar{\Xi}}{\text{opt}}~j\left(\Xi\right)
	\end{equation} }

	The cost function should describe the amount of information from an experiment. For that purpose it can be assumed a function $\kappa$ can be related to the Fisher information obtained an arbitrary operating conditions.

	{\footnotesize
	\begin{equation}
		j(\Xi) = \kappa\left[ \mathcal{F}(\Theta, \Xi) \right]
	\end{equation} }

	%Under the hypotheses mentioned above, the distribution of the maximum likelihood estimator is asymptotically Gaussian $\mathop{\mathbb{N}} (p^*, F^{-1}([^*, \Xi])) $ when the number of measurements tends to infinity. Minimizing $j(\Xi)$ then amounts to minimizing a scalar measure of the asymptotic covariance matrix of the parameters.

	A general class of DOE optimality criteria is given by

	{\footnotesize
	\begin{align}
		\kappa_k(\mathcal{F}(\Theta)) &= \left[\frac{1}{n_\Theta} \text{trace}\left( Q\mathcal{F}^{-1}(\Theta, \Xi) Q^\top \right)^k \right]^{1/k} \quad &\text{if} \det \mathcal{F} \neq 0 \nonumber \\
		\kappa_k(\mathcal{F}(\Theta)) &= \infty \quad &\text{if} \det \mathcal{F} = 0
	\end{align} }

	where $Q$ is a weighting matrix. The special case $k = 1$ corresponds to the L-optimality cost function,

	{\footnotesize
	\begin{equation}
		j_L(\Xi) = \text{trace} \left[ Q^\top Q\mathcal{F}^{-1}(\Theta,\Xi) \right]
	\end{equation} }

	and choosing $Q = \textbf{I}_{n_\Theta}$ corresponds to the A-optimality cost function. An A-optimal experiment minimizes the sum of the squares of the lengths of the axes of asymptotic confidence ellipsoids. When $Q$ diagonal, with $[Q]_{ii} = 1/\Theta_i$ this corresponds to C-optimality, which is associated with the relative precision of estimates. Selecting $Q$ as a row vector results in C-optimality. Setting $Q = \textbf{I}_{n_\Theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalues of the Fisher information matrix, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids. The most commonly used optimality criterion involves $k = 0$, $Q = \textbf{I}_{n_\Theta}$, requiring the minimization of $\det \mathcal{F}^{-1}(\Theta, \Xi)$, or, equivalently, maximization of

	{\footnotesize
	\begin{equation}
		j_D(\Xi) = \det \mathcal{F}(\Theta, \Xi)
	\end{equation} }

	A D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters. The graphical representation of the different optimality conditions is shown in Figure \ref{fig:score_fun}.

	\begin{figure}[!h]
		\centering
		\resizebox{0.4\textwidth}{!}{%
			\begin{tikzpicture}
				% Ellipse parameters
				\def\ellipsecenter{(3,3)}
				\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
				\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
				\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow

				% Draw the rotated ellipse
				\draw[fill=gray!10, draw=black, rotate around={45:\ellipsecenter}] \ellipsecenter ellipse (3cm and 1cm);

				% Draw the dashed rectangle
				\draw[dashed] (0.75,0.75) rectangle (5.25,5.25);

				% Draw the arrows and label them with adjustable positions
				\draw [-latex] \ellipsecenter -- \ellipseA node[yshift=-4cm, xshift=2.5cm,rotate around={-45:\ellipsecenter}] {A-optimality};
				\draw [-latex] \ellipsecenter -- \ellipseB node[yshift=0cm, xshift=-3.9cm,rotate around={45:\ellipsecenter}] {E-optimality};
				\draw [-latex] \ellipseC -- (2,2) node[yshift=-1cm, xshift=2cm] {D-optimality};

				% Draw axes
				\draw[thick,->] (0,0) -- (6,0) node[below] {$\theta_1$};
				\draw[thick,->] (0,0) -- (0,6) node[left] {$\theta_2$};
			\end{tikzpicture}
		}%
		\caption{Graphical representation of score functions}
		\label{fig:score_fun}
	\end{figure}

	\subsubsection{Problem formulation}

	Details on the process model can be found in $({\color{red}article~1})$. The model's empirical correlations are derived from laboratory experiments conducted under various constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. This study employs a model-based design of experiments technique to design an experiment with dynamically changing conditions to improve the precision of the correlation for $D_i$. The decision variables are adjusted every 30 minutes and are kept constant within each interval (piecewise constant controls). These controls have lower and upper bounds that match the validated range of the process model detailed in $({\color{red}article~1})$. The sampling time is considered to be 10 minutes, and the total extraction time is 300 minutes. The standard deviation $\sigma^2$ was estimated to be 0.12. The analysed correlations consist of two independent variables: Reynolds number and mass flow rate. The Reynolds number is a function of fluid thermodynamic properties and velocity, and the fluid density can be affected by temperature or pressure changes. In this work, two cases are solved and compared against each other.

	The first case assumes that the decision variables are the inlet temperature ($T^{in}$) and mass flow rate ($F$). Throughout the experiment, the pressure is assumed to remain constant and is set to a value in the middle of the validated range ($150$ bar). The initial state is considered isothermal, so $T^0=T^{in}(t=0)$. The general formulation of the optimal design of the experiment problem is presented below.

	{\footnotesize
	\begin{equation}
		\begin{aligned} 
			&\Xi^* &= \arg &\min_{ T^{in}, F \in \Xi} \int_{t_0}^{t_f} - \ln j_D(\Xi,\dot{x}) dt  \\
			&\text{subject to}
			& \dot{x} &= G(x,t,\Theta;\Xi) \\
			&& t_0&=0\quad~\text{min} \\
			&& t_f&=300~\text{min} \\
			&& T^{0} &= T^{in}(t=0) \\
			&& P(t) &= 150~\text{bar} \\
			%&& \dot{y} = g(x(t)) \\
			&& 30^\circ C \leq &T^{in}(t) \leq 40^\circ C \\
			&& 3.33 \cdot 10^{-5} \leq &F(t) \leq 6.67 \cdot 10^{-5}
		\end{aligned} \label{EQ:Formulation_1}
	\end{equation} }

	The second case assumes that the pressure and mass flow rate are treated as decision variables while the inlet temperature is kept constant at $35^\circ$C. Similarly to the first case, the extractor is assumed to be isothermal at the beginning of the operation. Compared to the previous case, the pressure change affects the temperature inside of the extractor. Any deviation in extractor temperature caused by pressure change will eventually be cancelled out by the inflow of fresh fluid at the designed temperature of $35^\circ$C. The general formulation of the optimal design of the experiment problem is presented below.

	{\footnotesize
		\begin{equation}
			\begin{aligned} 
				&\Xi^* &= \arg &\min_{ P, F \in \Xi} \int_{t_0}^{t_f} - \ln j_D(\Xi,\dot{x}) dt  \\
				&\text{subject to}
				& \dot{x} &= G(x,t,\Theta;\Xi) \\
				&& t_0&=0\quad~\text{min} \\
				&& t_f&=300~\text{min} \\
				&& T^{0} &= T^{in}(t) = 35^\circ C \\
				%&& P(t) &= 150~\text{bar} \\
				%&& \dot{y} = g(x(t)) \\
				&& 100^\circ C \leq &P(t) \leq 200^\circ C \\
				&& 3.33 \cdot 10^{-5} \leq &F(t) \leq 6.67 \cdot 10^{-5}
			\end{aligned} \label{EQ:Formulation_2}
	\end{equation} }

\end{document}

### 2024-07-06 Sections/Results_DOE.tex
06.07

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	%To identify the global solution of the Equation \ref{EQ:Formulation}, the optimization problem is solved multiple times starting from random initial solutions. The solution with the lowest value of the cost function is considered to be the global solution. Figure \ref{fig:scatter}, show an compression between initial and the final values of the cost function for multiple optimization problems. The shaded area is spanned between the smallest and the third smallest final value of the objective function. The black curves on the left and below of the scatter plot indicate distributions of the initial and final values of the cost function, respectively.

	To identify the global solution of Equation \ref{EQ:Formulation}, the optimization problem is solved multiple times starting from random initial solutions. The solution with the lowest cost function value is considered the global solution. Figure \ref{fig:scatter} shows a comparison between the initial and final values of the cost function for multiple optimization runs. The shaded area spans from the smallest to the third smallest final value of the objective function. The black curves on the left and below the scatter plot indicate the distributions of the initial and final cost function values, respectively.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=\columnwidth]{Figures/Results/scatter.png}	
		\caption{Initial vs final values of the cost function}
		\label{fig:scatter}
	\end{figure}

	The optimal inlet temperature and mass flow rate profile are presented on Figure \ref{fig:profile}.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=\columnwidth]{Figures/Results/Profile.png}	
		\caption{Optimal temperature and mass flow rate profiles}
		\label{fig:profile}
	\end{figure}

	\begin{comment}
		\begin{figure}[h!]
			\centering
			\includegraphics[width=\columnwidth]{Figures/Results/Profile_2.png}	
			\caption{2nd Optimal temperature and mass flow rate profiles}
			\label{fig:profile_2}
		\end{figure}

		\begin{figure}[h!]
			\centering
			\includegraphics[width=\columnwidth]{Figures/Results/Profile_3.png}	
			\caption{3rd Optimal temperature and mass flow rate profiles}
			\label{fig:profile_3}
		\end{figure}
	\end{comment}

\end{document}

### 2024-07-09 Sections/Optimal_design_of_experiment.tex
09.07

@@
 
-	Details on the process model can be found in $({\color{red}article~1})$.
-The model's empirical correlations are derived from laboratory experiments conducted under various constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+	Details on the process model can be found in [article 1].
+The model's empirical correlations are derived based on laboratory experiments conducted under various constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
 This study employs a model-based design of experiments technique to design an experiment with dynamically changing conditions to improve the precision of the correlation for $D_i$.
-The decision variables are adjusted every 30 minutes and are kept constant within each interval (piecewise constant controls).
-These controls have lower and upper bounds that match the validated range of the process model detailed in $({\color{red}article~1})$.
-The sampling time is considered to be 10 minutes, and the total extraction time is 300 minutes.
+The decision variables are adjusted every 10 minutes and are kept constant within each interval (piecewise constant controls).
+These controls have lower and upper bounds that match the validated range of the process model detailed in [article 1].
+The sampling time is set to 5 minutes, and the total extraction time is 300 minutes.
 The standard deviation $\sigma^2$ was estimated to be 0.12.
@@
 The Reynolds number is a function of fluid thermodynamic properties and velocity, and the fluid density can be affected by temperature or pressure changes.
-In this work, two cases are solved and compared against each other.
+In this work, both cases are solved and compared.
 
-	The first case assumes that the decision variables are the inlet temperature ($T^{in}$) and mass flow rate ($F$).
-Throughout the experiment, the pressure is assumed to remain constant and is set to a value in the middle of the validated range ($150$ bar).
-The initial state is considered isothermal, so $T^0=T^{in}(t=0)$.
-The general formulation of the optimal design of the experiment problem is presented below.
+	In the first case, the decision variables are the inlet temperature $(T^{in})$ and mass flow rate $(F)$.
+Throughout the experiment, the pressure is assumed to remain constant at 150 bar (the middle of the validated range).
+The initial state is considered isothermal, so $T^0 = T^{in}(t=0)$.
+The problem formulation for Case 1 is given by Equation \ref{EQ:Formulation_1}.
 
@@
 
-	The second case assumes that the pressure and mass flow rate are treated as decision variables while the inlet temperature is kept constant at $35^\circ$C.
-Similarly to the first case, the extractor is assumed to be isothermal at the beginning of the operation.
-Compared to the previous case, the pressure change affects the temperature inside of the extractor.
-Any deviation in extractor temperature caused by pressure change will eventually be cancelled out by the inflow of fresh fluid at the designed temperature of $35^\circ$C.
-The general formulation of the optimal design of the experiment problem is presented below.
+	In the second case, the pressure and mass flow rate are treated as decision variables, while the inlet temperature is kept constant at $35^\circ C$.
+Similar to the first case, the extractor is assumed to be isothermal at the beginning of the operation.
+Unlike the previous case, changes in pressure affect the temperature inside the extractor.
+Any temperature deviation caused by pressure changes will eventually be mitigated by the inflow of fresh fluid at the constant temperature of $35^\circ C$.
+The problem formulation for Case 2 is given by Equation \ref{EQ:Formulation_2}.
 

### 2024-07-09 Sections/Results_DOE.tex
09.07

@@
 
-	%To identify the global solution of the Equation \ref{EQ:Formulation}, the optimization problem is solved multiple times starting from random initial solutions.
-The solution with the lowest value of the cost function is considered to be the global solution.
-Figure \ref{fig:scatter}, show an compression between initial and the final values of the cost function for multiple optimization problems.
-The shaded area is spanned between the smallest and the third smallest final value of the objective function.
-The black curves on the left and below of the scatter plot indicate distributions of the initial and final values of the cost function, respectively.
-
-	To identify the global solution of Equation \ref{EQ:Formulation}, the optimization problem is solved multiple times starting from random initial solutions.
+	To identify the global solution of Equations \ref{EQ:Formulation_1}, the optimization problem is solved multiple times, each starting from a random initial solution.
+Figure \ref{fig:scatter_T} compares the initial and final values of the cost function across multiple optimization runs.
+The shaded area spans from the smallest to the third smallest final values of the objective function.
+The black curves on the left and below the scatter plot represent the distributions of the initial and final cost function values, respectively.
+From Figure \ref{fig:scatter_T}, it can be observed that multiple local solutions exist for Case 1.
 The solution with the lowest cost function value is considered the global solution.
-Figure \ref{fig:scatter} shows a comparison between the initial and final values of the cost function for multiple optimization runs.
-The shaded area spans from the smallest to the third smallest final value of the objective function.
-The black curves on the left and below the scatter plot indicate the distributions of the initial and final cost function values, respectively.
 
@@
 		\centering
-		\includegraphics[width=\columnwidth]{Figures/Results/scatter.png}	
+		\includegraphics[width=\columnwidth]{Figures/Results/scatter_T.png}	
 		\caption{Initial vs final values of the cost function}
-		\label{fig:scatter}
+		\label{fig:scatter_T}
 	\end{figure}
 
-	The optimal inlet temperature and mass flow rate profile are presented on Figure \ref{fig:profile}.
+	The optimal profiles of inlet temperature and mass flow rate are presented in Figure \ref{fig:profile_T}.
+One of the independent parameters in the analysed correlation is the mass flow rate, which is directly modified several times during the experiment.
+The second independent parameter is the Reynolds number, which can be affected by changes in the thermodynamic properties of the fluid.
+The thermal properties of CO$_2$ between $30^\circ$C and $40^\circ$C, assuming a constant pressure of 150 bar, vary only slightly.
+For instance, the dynamic viscosity changes from 67 to $80 \times 10^{-6}$ Pa$\cdot$s.
+The obtained profile of the inlet temperature shows minimal variation, suggesting a limited influence of inlet temperature on the extraction yield.
+Given the narrow operational window for inlet temperature at constant pressure, the mass flow rate becomes the primary variable to control.
 
@@
 		\centering
-		\includegraphics[width=\columnwidth]{Figures/Results/Profile.png}	
+		\includegraphics[width=\columnwidth]{Figures/Results/Profile_T_1.png}	
 		\caption{Optimal temperature and mass flow rate profiles}
-		\label{fig:profile}
+		\label{fig:profile_T}
 	\end{figure}
 
-	\begin{comment}
-		\begin{figure}[h!]
-			\centering
-			\includegraphics[width=\columnwidth]{Figures/Results/Profile_2.png}	
-			\caption{2nd Optimal temperature and mass flow rate profiles}
-			\label{fig:profile_2}
-		\end{figure}
+	Similar to Case 1, Case 2 is solved multiple times starting from random initial solutions to identify the global solution.
+Figure \ref{fig:scatter_P} summarizes the changes in the objective function values across all optimization runs.
+It is evident that both the initial and final values of the cost function are significantly lower than any values obtained in Case 1.
+In Case 2, the wider operating range leads to more significant changes in the physical properties of CO$_2$ compared to Case 1.
+For example, the kinematic viscosity of CO$_2$ ranges from $48 \cdot 10^{-6}$ (at $40^\circ$C and 100 bar) to $90 \cdot 10^{-6}$ Pa$\cdot$s (at $30^\circ$C and 200 bar).
+The greater variability in pressure induces a more complex system response, including temperature variations, resulting in lower values of the objective function compared to Case 1.
 
@@
 		\centering
-			\includegraphics[width=\columnwidth]{Figures/Results/Profile_3.png}	
-			\caption{3rd Optimal temperature and mass flow rate profiles}
-			\label{fig:profile_3}
+		\includegraphics[width=\columnwidth]{Figures/Results/scatter_P.png}	
+		\caption{Initial vs final values of the cost function}
+		\label{fig:scatter_P}
 	\end{figure}
-	\end{comment}
+
+	The optimal profiles of pressure and mass flow rate are presented on Figure \ref{fig:profile_P}.
+Similarly to case 1, only few changes in the mass flow rate are observed in the plot.
+In contrary to the inlet temperature, the pressure changes are frequently applied in the case 2.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=\columnwidth]{Figures/Results/Profile_P_1.png}	
+		\caption{Optimal pressure and mass flow rate profiles}
+		\label{fig:profile_P}
+	\end{figure}
 

### 2024-07-09 SFE_DOE_Chamomile/main_DOE_Chamomile.m

@@ -1,0 +1,441 @@
+startup;
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
+
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+import casadi.*
+
+%% Create the solver
+Iteration_max               = 500;                                          % Maximum number of iterations for optimzer
+Time_max                    = 24;                                           % Maximum time of optimization in [h]
+
+nlp_opts                    = struct;
+nlp_opts.ipopt.max_iter     = Iteration_max;
+nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+%nlp_opts.ipopt.hessian_approximation ='limited-memory';
+%nlp_opts.ipopt.acceptable_tol  = 1e-4;
+%nlp_opts.ipopt.acceptable_iter = 5;
+
+%%
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('wpd_datasets.xlsx');
+which_dataset           = 4;
+
+%SAMPLE                  = LabResults(21:34,1);
+data_org                = LabResults(21:34,which_dataset+1)';
+
+%% Load paramters
+m_total                 = 3.0;
+
+% Bed geometry
+before                  = 0.04;                                             % Precentage of length before which is empty
+bed                     = 0.92;                                             % Percentage of length occupied by fixed bed
+
+% Set time of the simulation
+PreparationTime         = 0;
+ExtractionTime          = 300;
+timeStep                = 1;                                               % Minutes
+OP_change_Time          = 10;                                              % Minutes
+SAMPLING_TIME           = 5;
+
+simulationTime          = PreparationTime + ExtractionTime;
+
+timeStep_in_sec         = timeStep * 60;                                    % Seconds
+Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+Time                    = [0 Time_in_sec/60];                               % Minutes
+
+N_Time                  = length(Time_in_sec);
+OP_change               = OP_change_Time:OP_change_Time:ExtractionTime;
+
[…]

### 2024-07-12 SFE - presentation/SFE — poster.tex
12.07

\documentclass[8pt]{beamer}

\usetheme[progressbar=frametitle]{metropolis}
\setbeamercolor{background canvas}{bg=white}

\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}

\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{pdfpages}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage[document]{ragged2e}

\usepackage{amsbsy}
\newcommand*{\claps}[1]{\hbox to 0pt{\hss#1\hss}}
\newcommand*{\mat}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand*{\subdims}[3]{\clap{\raisebox{#1}[0pt][0pt]{$\scriptstyle(#2 \times #3)$}}}
\fboxrule=1pt

\title{Supercritical Extraction}
\subtitle{A process model and a sensitivity analysis}
% \date{\today}
\date{11.06.2021}
\author{Oliwer Sliczniuk}
\institute{Aalto University}

\begin{document}

	\begin{frame}[fragile]{Model description}
		\large{\textbf{Supercritical Extraction: A process model and a sensitivity analysis}}\\
		\small{Oliwer Sliczniuk, Pekka Oinas, Francesco Corona} 
		\vfill
		\begin{minipage}{0.75\linewidth}
		\includegraphics[trim = 6cm 5cm 6cm 2cm,clip,width=\linewidth]{Figures/SFE.pdf}
		\end{minipage}
		\begin{minipage}{0.24\linewidth}
			\begin{itemize}
				\item One-dimensional model
				\item Plug flow 
				\item No pressure drop
				\item Negligible external diffusion 
				\item Single component
				\item Pseudo-homogeneous thermal properties
				\item Uniformly distribution of the particles
			\end{itemize}
		\end{minipage}
	\\	
	\end{frame}

	\begin{frame}[fragile]{Differential model of the extractor$^1$}\justifying
	\textcolor{blue}{State variables},
	\textcolor{red}{control variables}, 
	\textcolor{magenta}{parameters}, 
	\textcolor{orange}{other variables} (\textcolor{blue}{state vars}, \textcolor{magenta}{parameters})\\
	{\footnotesize\begin{align*}
			\intertext{\textbf{Fluid phase mass balance}}
			\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  \underbrace{-\cfrac{1}{ \textcolor{magenta}{\epsilon A}}\cfrac{\textcolor{red}{F}(t)}{\textcolor{orange}{\rho}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))} \cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial  \textcolor{blue}{z}}}_{\text{Convection}}
			+ \underbrace{ \textcolor{orange}{D^M_e}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 \textcolor{blue}{c}(t,z)}{\partial \textcolor{blue}{z^2}} }_{\text{Diffusion}}
			+ \underbrace{ \cfrac{1-\textcolor{magenta}{\epsilon}}{\textcolor{magenta}{\epsilon}} \textcolor{blue}{r_e}(t,z) }_{\text{Kinetics}}\\
			%		\end{align*}}
			\intertext{\textbf{Solid phase mass balance}}
			%		{\scriptsize\begin{align*}
			\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= \underbrace{ \textcolor{blue}{r_e}(t,z) }_{\text{Kinetics}}\\
			%		\end{align*}}
			\intertext{\textbf{Heat balance}}
			%		{\scriptsize\begin{align*}
			\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= 
			\underbrace{ -\cfrac{\textcolor{red}{F}(t)}{\textcolor{magenta}{A}} \cfrac{\textcolor{orange}{C_p}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))}{ [(1-\textcolor{magenta}{\epsilon})\textcolor{orange}{\rho}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \textcolor{orange}{C_p} (\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) + \textcolor{magenta}{ \epsilon \rho_s C_{ps} } ]} \cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial \textcolor{blue}{z}}  }_{\text{Convection}}
			+ \underbrace{ \textcolor{orange}{D^T_e}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 \textcolor{blue}{T}(t,z)}{\partial \textcolor{blue}{z^2}} }_{\text{Diffusion}}\\ \\
			%		\end{align*}}
			\intertext{Extraction kinetics}
			%		{\scriptsize\begin{align*}
			\textcolor{blue}{r_e}(t,z) &= -\cfrac{\textcolor{orange}{D_i}(\textcolor{blue}{T}(t,z))}{\textcolor{magenta}{ \mu l^2} }\left(\textcolor{blue}{q}(t,z) - \textcolor{blue}{c}(t,z) \cfrac{\textcolor{magenta}{\rho_s}}{\textcolor{orange}{k_m}(\textcolor{blue}{T}(t,z))\textcolor{orange}{\rho}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))} \right)
			%		\end{align*}}
			\\ \\
			\hline 
			\textbf{Measurment - Yield}\\
			%		{\scriptsize\begin{align*}
			y(t) &= \cfrac{\sum\limits_{i=1}^{N_z}  \left(  \textcolor{magenta}{\cfrac{1}{N_z}} \left(\textcolor{magenta}{m_0} - m_i(\textcolor{blue}{q_i}(t,z)) \right) \right) }{\textcolor{magenta}{m_0}} = \underbrace{ \cfrac{\sum\limits_{i=1}^{N_z}  \left(  \textcolor{magenta}{\cfrac{V}{N_z}} \left(\textcolor{magenta}{q_0} - \textcolor{blue}{q}_i(t,z) \right) \right) }{\textcolor{magenta}{q_0 V}} }_{g(x(t))}
	\end{align*}}
	\hrule
	\footnotesize{[1] E. Reverchon, Mathematical modeling of supercritical extraction of sage oil, AIChE J 42 (6), 1996}
	\end{frame}

	\begin{frame}[fragile]{PDE to ODE and sensitivity analysis}\justifying
		Sensitivity analysis$^2$ measures the susceptibility of the model to changes in its parameters\\
		\footnotesize{
			\begin{columns}[c]
				\column{.4\textwidth}
			\begin{align*}
				\cfrac{d x(t)}{d t} &= 
				\begin{bmatrix}
					\cfrac{d c_1(t)}{d t} 	  \\
					\vdots					  \\
					\cfrac{d c_{N_z}(t)}{d t} \\
					\\ \hline \\
					\cfrac{d q_1(t)}{d t} 	  \\
					\vdots					  \\
					\cfrac{d q_{N_z}(t)}{d t} \\
					\\ \hline \\
					\cfrac{d T_1(t)}{d t} 	  \\
					\vdots 					  \\
					\cfrac{d T_{N_z}(t)}{d t}
				\end{bmatrix}
				=
				\underbrace{\begin{bmatrix}
					F_1 \left( c(t),q(t),T(t); p \right)\\ 
					\vdots\\ 
					F_{N_z} \left( c(t),q(t),T(t); p \right)\\ \\
					\\ \hline \\ \\
					F_{N_z+1} \left( c(t),q(t),T(t); p \right)\\
					\vdots\\
					F_{2N_z} \left( c(t),q(t),T(t); p \right)\\ \\
					\\ \hline \\ \\
					F_{2N_z+1} \left( c(t),q(t),T(t); p \right) \\
					\vdots\\
					F_{3N_z} \left( c(t),q(t),T(t); p \right)
				\end{bmatrix}}_{F \left( t; p \right)} \\ 
			%Z &= \cfrac{\partial \textcolor{blue}{x}(t,p)}{\partial \textcolor{magenta}{p}} \nonumber \\
			\end{align*}
			\column{.4\textwidth}
			State sensitivity
			\begin{align*}
			\dot{Z}  & = \partial_t \textcolor{blue}{Z}(t,p) = \partial_t \left( \partial_p \textcolor{blue}{x}(t,p) \right) = \\
			& = \partial_p \left( \partial_t \textcolor{blue}{x}(t,p) \right) = \partial_p \textcolor{blue}{F}(x(t);p) \\
			\partial_p \textcolor{blue}{F}(x(t);p) &=  \underbrace{ \partial_{x(t)} F(x(t);p)}_{J_x(x(t);p)}  \underbrace{\partial_p x(t)}_{S(x(t);p)} + \underbrace{ \partial_p F(x(t);p) }_{J_p(x(t);p)}
		\end{align*}
		\\
		\vspace{0.1cm}
		\hrule
		\vspace{0.1cm}
		Output sensitivity \\
		\begin{align*}
			\cfrac{d y(t)}{dp} &= \cfrac{d g(x(t))}{dp} = \partial_{x(t)} g(x(t)) \; S(x(t);p)
		\end{align*}	
	\end{columns}
}
\hrule
\footnotesize{[2] T. Maly, L. R. Petzold, Numerical methods and software for sensitivity analysis of differential-algebraic systems, Applied Numerical Mathematics 20 (1-2), 1996 }
	\end{frame}

	\begin{frame}[fragile]{Sensitivity analysis - flow rate}
	\begin{table}[!hbt]
		\centering
		\begin{tabular}{ |c|c|c|c|c|c|c|c|c| } 
		\hline
		Ref& $F[kg/hr]$ & $T_{Inlet} [C]$ & $T_{extractor} [C]$ & $P [bar]$ & $c [kg/m^3]$ & $q [kg/m^3]$ \\ \hline
		Vargas$^3$ & 0.035      & 50              & 50		             & 90  	     & 0 		    & 27 		   \\ \hline
		\end{tabular}
	\end{table}				
	\begin{columns}[t]
		\column{.3\textwidth}
		\centering
		\includegraphics[width=3.7cm,height=2.0cm]{Figures/Sensitivity/ConcentrationLiquid.png}\\
		\includegraphics[width=3.7cm,height=2.0cm]{Figures/Sensitivity/Imagesc/2_SS_R_F.png}\\
		\includegraphics[width=3.7cm,height=2.0cm]{Figures/Sensitivity/Plots/2_SS_R_F.png}
		\column{.3\textwidth}
		\centering
		\includegraphics[width=3.7cm,height=2.05cm]{Figures/Sensitivity/ConcentrationSolid.png}\\
		\includegraphics[width=3.7cm,height=2.0cm]{Figures/Sensitivity/Imagesc/3_SS_R_F.png}\\
		\includegraphics[width=3.7cm,height=2.0cm]{Figures/Sensitivity/Plots/3_SS_R_F.png}
		\column{.3\textwidth}
		\centering
		\includegraphics[width=3.7cm,height=2.0cm]{Figures/Sensitivity/Yield.png}\\
		\includegraphics[width=3.7cm,height=2.0cm]{Figures/Sensitivity/Plots/1_SS_R_F.png}
	\end{columns}
\hrule
\footnotesize{[3] R.Vargas, Supercritical extraction of carqueja essential oil: experiments and modeling, Brazilian Journal of Chemical Engineering (2006) }
\end{frame}

\end{document}

### 2024-07-12 SFE - presentation/SFE.tex
12.07

\documentclass[8pt]{beamer}

\usetheme[progressbar=frametitle]{metropolis}
\setbeamercolor{background canvas}{bg=white}

\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}

\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{pdfpages}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{adjustbox}

\usepackage{amsbsy}
\newcommand*{\claps}[1]{\hbox to 0pt{\hss#1\hss}}
\newcommand*{\mat}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand*{\subdims}[3]{\clap{\raisebox{#1}[0pt][0pt]{$\scriptstyle(#2 \times #3)$}}}
\fboxrule=1pt

\title{Supercritical Extraction}
\subtitle{A process model and a sensitivity analysis}
% \date{\today}
\date{15.05.2021}
\author{Oliwer Sliczniuk}
\institute{Aalto University}
% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}

\begin{document}

	\maketitle

	\begin{frame}{Table of contents}
		\begin{enumerate}
			\item Introduction to the process
			\item Process model and assumptions
			\item Sensitivity analysis
			\item Output discussion 
			\item What's next?
		\end{enumerate}
	\end{frame}

	\section[Supercritical extraction - process description]{Introduction}

	\begin{frame}[fragile]{SFE}
	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 4cm 5cm 4cm 3cm,clip,width=\linewidth]{Figures/SFE_Diagram.pdf}
		\caption{Schematic representation of SFE process}
		\label{fig:SFE_drawing}
	\end{figure} 
	\end{frame}

	\section{Model description}

	\begin{frame}{Model of the extractor}
		\textcolor{red}{control variables},
		\textcolor{blue}{state variables},
		\textcolor{orange}{variables} and
		\textcolor{green}{parameters}\par
		{\footnotesize\begin{align*}
			\intertext{(1) Fluid phase mass balance}
			\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  -\cfrac{1}{ \textcolor{green}{\epsilon A}}\cfrac{\textcolor{red}{F}(t)}{\textcolor{orange}{\rho}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))} \cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial  \textcolor{blue}{z}} 
			+ \textcolor{orange}{D^M_e}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 \textcolor{blue}{c}(t,z)}{\partial \textcolor{blue}{z^2}} + \cfrac{1-\textcolor{green}{\epsilon}}{\textcolor{green}{\epsilon}} \textcolor{blue}{r_e}(t,z)\\
%		\end{align*}}
		\intertext{(2) Solid phase mass balance}
%		{\scriptsize\begin{align*}
			\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= \textcolor{blue}{r_e}(t,z)\\
%		\end{align*}}
		\intertext{(3) Heat balance}
%		{\scriptsize\begin{align*}
			\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= -\cfrac{\textcolor{red}{F}(t)}{\textcolor{green}{A}} \cfrac{\textcolor{orange}{C_p}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))}{ [(1-\textcolor{green}{\epsilon})\textcolor{orange}{\rho}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \textcolor{orange}{C_p} (\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) + \textcolor{green}{ \epsilon \rho_s C_{ps} } ]} \cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial \textcolor{blue}{z}} 
			+  \textcolor{orange}{D^T_e}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 \textcolor{blue}{T}(t,z)}{\partial \textcolor{blue}{z^2}}\\
%		\end{align*}}
		\\ \intertext{Extraction kinetic}
%		{\scriptsize\begin{align*}
			\textcolor{blue}{r_e}(t,z) &= -\cfrac{\textcolor{orange}{D_i}(\textcolor{blue}{T}(t,z))}{\textcolor{green}{ \mu l^2} }\left(\textcolor{blue}{q}(t,z) - \textcolor{blue}{c}(t,z) \cfrac{\textcolor{green}{\rho_s}}{\textcolor{orange}{k_m}(\textcolor{blue}{T}(t,z))\textcolor{orange}{\rho}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))} \right)\\
%		\end{align*}}
		\intertext{Output function}
%		{\scriptsize\begin{align*}
			\textcolor{blue}{y}(t) &= \textcolor{blue}{g}(x(t)) =\cfrac{\sum\limits_{i=1}^{N_z}  \left(  \textcolor{green}{\cfrac{1}{N_z}} \left(\textcolor{green}{m_0} - \textcolor{blue}{m}_i(t,z) \right) \right) }{\textcolor{green}{m_0}} =  \cfrac{\sum\limits_{i=1}^{N_z}  \left(  \textcolor{green}{\cfrac{V}{N_z}} \left(\textcolor{green}{q_0} - \textcolor{blue}{q}_i(t,z) \right) \right) }{\textcolor{green}{q_0 V}}
		\end{align*}}
	\end{frame}

	\begin{frame}[fragile]{SFE - assumptions}
	\begin{itemize}
		\item One-dimensional model
		\item Plug flow 
		\item No pressure drop
		\item Negligible external diffusion 
		\item Single component
		\item Pseudo-homogeneous thermal properties
		\item Uniformly distribution of the particles
	\end{itemize}
	\end{frame}

	\begin{frame}{Model dependencies}
		\par
	{\footnotesize\begin{align*}
			\intertext{(1) Density - Peng-Robinson}
			\textcolor{red}{P}(t) &= \frac{RT}{V_m - b} - \frac{a\alpha}{V_m^2 + 2bV_m - b^2}\\
			\intertext{(2) Solid phase mass balance}
			\textcolor{orange}{C_p}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) &= Cp_{Ideal} + Cv_{corr} + T\left(\frac{\partial P}{\partial T}\right)_V\left(\frac{\partial V}{\partial T}\right)_P - R\\
			\intertext{(3) Axial diffusion of the mass }
			\textcolor{orange}{D_e^M} (\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) &= \cfrac{\textcolor{orange}{u}(\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \textcolor{green}{d_p}}{\textcolor{green}{\epsilon} P_e}\\
			\intertext{(4) Axial diffusion of the heat}
			\textcolor{orange}{D_e^T}\left[\cfrac{m^2}{s}\right] (\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) &= \cfrac{\textcolor{orange}{k^T} (\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))}{\textcolor{orange}{\rho} (\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t)) \textcolor{orange}{C_p} (\textcolor{blue}{T}(t,z)\textcolor{red}{P}(t))}
			\intertext{(5) Internal diffusion}
			\textcolor{orange}{D_i}(\textcolor{blue}{T}(t,z)) \left[\cfrac{m^2}{s}\right] &= \textcolor{green}{D_{i_0}} \exp\left(\cfrac{-\textcolor{green}{EA_{D_i}}}{\textcolor{green}{R} \textcolor{blue}{T}(t,z)}\right) \\
			\intertext{(6) Partition coefficient}
			\textcolor{orange}{k_m}(\textcolor{blue}{T}(t,z))\left[-\right]  &=\textcolor{green}{k_{m_0}} \exp\left(\cfrac{-\textcolor{green}{EA_{k_m}}}{\textcolor{green}{R} \textcolor{blue}{T}(t,z)}\right)
	\end{align*}}
	\end{frame}

	\begin{frame}[fragile]{SFE - state-space model}
		\begin{align*}
			\begin{bmatrix}
				\cfrac{\partial c(t,z)}{\partial t}\\
				\cfrac{\partial q(t,z)}{\partial t}\\
				\cfrac{\partial T(t,z)}{\partial t} 
			\end{bmatrix}
			=
			\begin{bmatrix}
				\phi_1 \left( c(t,z),q(t,z),T(t,z); \theta \right)\\
				\phi_2 \left( c(t,z),q(t,z),T(t,z); \theta \right)\\
				\phi_3 \left( c(t,z),q(t,z),T(t,z); \theta \right)
			\end{bmatrix}
			= \phi \left( t,z; \theta \right) &= \cfrac{\partial \chi(t,z)}{\partial t}
		\end{align*}
	\\
	where $\theta$ is a set of parameters present in the model, $\phi$ is a set of functions which correspond to state equations of the model and $\chi$ is the state space model.
	\end{frame}

	\begin{frame}[fragile]{SFE - discretization}
		\small{
		\begin{align*}
			\cfrac{d x(t)}{d t} &= 
			\begin{bmatrix}
				\cfrac{d c_1(t)}{d t} 	  \\
				\vdots					  \\
				\cfrac{d c_{N_z}(t)}{d t} \\
				\cfrac{d q_1(t)}{d t} 	  \\
				\vdots					  \\
				\cfrac{d q_{N_z}(t)}{d t} \\
				\cfrac{d T_1(t)}{d t} 	  \\
				\vdots 					  \\
				\cfrac{d T_{N_z}(t)}{d t}
			\end{bmatrix}
			=
			\begin{bmatrix}
				F_1 \left( c(t),q(t),T(t); p \right)\\ 
				\vdots\\ 
				F_{N_z} \left( c(t),q(t),T(t); p \right)\\ \\
				F_{N_z+1} \left( c(t),q(t),T(t); p \right)\\
				\vdots\\
				F_{2N_z} \left( c(t),q(t),T(t); p \right)\\ \\
				F_{2N_z+1} \left( c(t),q(t),T(t); p \right) \\
				\vdots\\
				F_{3N_z} \left( c(t),q(t),T(t); p \right)
			\end{bmatrix}
			= F \left( t; p \right)
		\end{align*} }\\
		where $x \in \mathbb{R}^{N_x = 3N_z} $ and $p \in \mathbb{R}^{N_p =  N_{\theta} + N_u } $
	\end{frame}

	\section{Sensitivity Analysis}

	\begin{frame}[fragile]{Sensitivity Analysis}
		Local derivative-based methods involve taking the partial derivative of the output with respect to an input parameter. In sensitivity analysis the original system of equations is solved simultaneously with $\cfrac{\partial \textcolor{blue}{F}(x(t);p)}{\partial p}$, where $p$ is a vector of all the parameters and the control variables.
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis}
		\small{
		\begin{align*}
			Z &= \cfrac{\partial \textcolor{blue}{x}(t,p)}{\partial \textcolor{green}{p}} \nonumber \\
			\dot{Z}  &= \cfrac{\partial \textcolor{blue}{Z}(t,p)}{\partial t} = \cfrac{\partial }{\partial t} \left( \cfrac{\partial \textcolor{blue}{x}(t,p)}{\partial p} \right) = \cfrac{\partial }{\partial p} \left( \cfrac{\partial \textcolor{blue}{x}(t,p)}{\partial t} \right) = \cfrac{\partial \textcolor{blue}{F}(x(t);p)}{\partial p} \\
			\cfrac{d \textcolor{blue}{F}(x(t);p)}{d p} &=  \cfrac{\partial F(x(t);p)}{\partial x(t)} \cfrac{\partial x(t)}{\partial p} + \cfrac{\partial F(x(t);p)}{\partial p}  \\
			& = J_x(x(t);p)S(x(t);p) + J_p(x(t);p)
		\end{align*}
		}
		\tiny{
		\[
		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat {\cfrac{d F(x(t);p)}{dp}} $}}\subdims{-1.5cm} {N_x} {N_p}} =
		\framebox[2.0cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat J_x$}}\subdims{-1.5cm} {N_x} {N_x}} \ 
		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat S$}}  \subdims{-1.5cm} {N_x} {N_p}} + 
		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat J_p$}}\subdims{-1.5cm} {N_x} {N_p}}
		\]}

	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis}
		\tiny{\begin{align*}
			\begin{split}
				\cfrac{d F(x(t);p)}{dp} &=\left(\begin{array}{cccc}
					\cfrac{\partial F_{1}(x(t);p)}{\partial x_{1}(t)} & \cfrac{\partial F_{1}(x(t);p)}{\partial x_{2}(t)} & \cdots & \cfrac{\partial F_{1}(x(t);p)}{\partial x_{N_x}(t)}\\
					\cfrac{\partial F_{2}(x(t);p)}{\partial x_{1}(t)} & \cfrac{\partial F_{2}(x(t);p)}{\partial x_{2}(t)} & \cdots & \cfrac{\partial F_{2}(x(t);p)}{\partial x_{N_x}(t)}\\
					\vdots & \vdots & \ddots & \vdots\\ 
					\cfrac{\partial F_{N_x}(x(t);p)}{\partial x_{1}(t)} & \cfrac{\partial F_{N_x}(x(t);p)}{\partial x_{2}(t)} & \cdots & \cfrac{\partial F_{N_x}(x(t);p)}{\partial x_{N_x}(t)}
				\end{array}\right)
			\begin{pmatrix}
				\cfrac{d x_{1}(t)}{d p_{1}} 	& \cfrac{d x_{1}(t)}{d p_{2}}     & \cdots & \cfrac{d x_{1}(t)}{d p_{N_p}}\\
				\cfrac{d x_{2}(t)}{d p_{1}}		& \cfrac{d x_{2}(t)}{d p_{2}}     & \cdots & \cfrac{d x_{2}(t)}{d p_{N_p}}\\
				\vdots					 	    & \vdots 					   	  & \ddots & \vdots\\
				\cfrac{d x_{N_x}(t)}{d p_{1}} 	& \cfrac{d x_{N_x}(t)}{d p_{2}}   & \cdots & \cfrac{d x_{N_x}(t)}{d p_{N_p}}
			\end{pmatrix}
		 + \\
	   & + \left(\begin{array}{cccc}
				\cfrac{\partial F_{1}(x(t);p)}{\partial p_{1}} & \cfrac{\partial F_{1}(x(t);p)}{\partial p_{2}} & \cdots & \cfrac{\partial F_{1}(x(t);p)}{\partial p_{N_p}}\\
				\cfrac{\partial F_{2}(x(t);p)}{\partial p_{1}} & \cfrac{\partial F_{2}(x(t);p)}{\partial p_{2}} & \cdots & \cfrac{\partial F_{2}(x(t);p)}{\partial p_{N_p}}\\
				\vdots & \vdots & \ddots & \vdots\\
				\cfrac{\partial F_{N_x}(x(t);p)}{\partial p_{1}} & \cfrac{\partial F_{N_x}(x(t);p)}{\partial p_{2}} & \cdots & \cfrac{\partial F_{N_x}(x(t);p)}{\partial p_{N_p}}
			\end{array}\right)
	\end{split}\end{align*}
	}
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis}
		The$F(x(t);p)$ is augmented with sensitivity equations and denoted as \textbf{F}$\left(x(t);p\right)$. The size of \textbf{F}$\left(x(t);p\right)$ is equal to $N_s = N_x(N_p + 1)$.
		\small{
		\begin{align*}
			\textbf{F}\left(x(t);p\right) = 
			\begin{bmatrix}
				F(x(t);p)\\
				J_x(x(t);p)S(x(t);p) + J_p(x(t);p)
			\end{bmatrix}
		\end{align*} } \\
		The initial conditions are described as
		\small{
		\begin{align*}
			\textbf{F}\left(x(t_0);p\right)  = 
			\begin{bmatrix} x(t_0),			& 
				\cfrac{ \text{d}x(t_0) }{ dp_1 },		& 
				\cdots,					 	&
				\cfrac{ dx(t_0) }{ dp_{N_p} } 
			\end{bmatrix}^T
		\end{align*} }
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis}

		\footnotesize{\begin{align*}
		\textcolor{blue}{y}(t) &= \textcolor{blue}{g}(x(t)) =\cfrac{\sum\limits_{i=1}^{N_z}  \left(  \textcolor{green}{\cfrac{1}{N_z}} \left(\textcolor{green}{m_0} - \textcolor{blue}{m}_i(t,z) \right) \right) }{\textcolor{green}{m_0}} =  \cfrac{\sum\limits_{i=1}^{N_z}  \left(  \textcolor{green}{\cfrac{V}{N_z}} \left(\textcolor{green}{q_0} - \textcolor{blue}{q}_i(t,z) \right) \right) }{\textcolor{green}{q_0 V}}\\ 
		\end{align*}}
		By taking a total derivative of $y(t)$ with respect to $p$, the new sensitivity equation can found.\\
		\footnotesize{\begin{align*}
		\cfrac{d y(t)}{dp} &= \cfrac{d g(x(t))}{dp} = \cfrac{\partial g(x(t))}{\partial x(t)} \cfrac{\partial x(t)}{\partial p} + \cfrac{\partial g(x(t))}{\partial p}\\
		\cfrac{\partial g(x(t))}{\partial p} &= \cfrac{\partial g(x(t))}{\partial x(t)} \cfrac{\partial x(t)}{\partial p} + 0 = \cfrac{\partial g(x(t))}{\partial x(t)}  S(x(t);p) = \\
		\begin{split}
				&\left(\begin{array}{cccc}
					\cfrac{\partial g_{1}(x(t))}{\partial x_{1}} & \cfrac{\partial g_{1}(x(t))}{\partial x_{2}} & \cdots & \cfrac{\partial g_{1}(x(t))}{\partial x_{N_x}}\\
					\cfrac{\partial g_{2}(x(t))}{\partial x_{1}} & \cfrac{\partial g_{2}(x(t))}{\partial x_{2}} & \cdots & \cfrac{\partial g_{2}(x(t))}{\partial x_{N_x}}\\
					\vdots & \vdots & \ddots & \vdots\\
					\cfrac{\partial g_{N_g}(x(t))}{\partial x_{1}} & \cfrac{\partial g_{N_g}(x(t))}{\partial x_{2}} & \cdots & \cfrac{\partial g_{N_g}(x(t))}{\partial x_{N_x}}
				\end{array}\right)
				\left(\begin{array}{cccc}
					s_{({1,1})} & s_{({1,2})} & \cdots & s_{({1,N_p})}\\
					s_{({2,1})} & s_{({2,2})} & \cdots & s_{({2,N_p})}\\
					\vdots & \vdots & \ddots & \vdots\\
					s_{({N_x,1})} & s_{({N_x,2})} & \cdots & s_{({N_x,N_p})}\\
				\end{array}\right)
		\end{split}
	\end{align*}}
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis}
		Because the output function returns only one value, the equation becomes
		\footnotesize{\begin{align*}\begin{split}
				& \left( \cfrac{\partial y(x(t))}{\partial p_{1}}, \cfrac{\partial y(x(t))}{\partial p_{2}}, \cdots, \cfrac{\partial y(x(t))}{\partial p_{N_p}} \right) = \\
				& =\left( \cfrac{\partial g(x(t))}{\partial x_{1}}, \cfrac{\partial g(x(t))}{\partial x_{2}}, \cdots, \cfrac{\partial g(x(t))}{\partial x_{N_x}} \right)
				\left(\begin{array}{cccc}
					s_{({1,1})} & s_{({1,2})} & \cdots & s_{({1,N_p})}\\
					s_{({2,1})} & s_{({2,2})} & \cdots & s_{({2,N_p})}\\
					\vdots & \vdots & \ddots & \vdots\\
					s_{({N_x,1})} & s_{({N_x,2})} & \cdots & s_{({N_x,N_p})}
				\end{array}\right)
		\end{split}\end{align*}}

		\tiny{
		\[
		\framebox[1.5cm]{\claps{\raisebox{0pt}[0.3cm][0.3cm]{$\mat {\cfrac{d g(x(t))}{dp} } $}}		\subdims{-1.7cm} {1} {N_p}} =
		\framebox[2.5cm]{\claps{\raisebox{0pt}[0.3cm][0.3cm]{$\mat {\cfrac{d g(x(t))}{d x(t)} } $}} \subdims{-1.7cm} {1} {N_x}} \ 
		\framebox[1.5cm]{\claps{\raisebox{0pt}[1.25cm][1.25cm]{$\mat S$}}  							\subdims{-1.7cm} {N_x} {N_p}}
		\]}

	\end{frame}

	\section{Results}

	\begin{frame}[fragile]{Results of the simulation}
	\centering Product: CARQUEJA essential oil
	\begin{table}[!hbt]
		\centering
		\begin{tabular}{ |c|c|c|c|c|c|c|c|c| } 
			\hline
			Ref& $F[kg/hr]$ & $T_{Inlet} [C]$ & $T_{extractor} [C]$ & $P [bar]$ & $c [kg/m^3]$ & $q [kg/m^3]$ \\ \hline
			Vargas & 0.035      & 50              & 50		             & 90  	     & 0 		    & 27 		   \\ \hline
		\end{tabular}
		\caption{Initial conditions}
	\end{table}					
	\begin{columns}[t]
		\column{.5\textwidth}
		\centering
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Yield.png}\\
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Temperature.png}
		\column{.5\textwidth}
		\centering
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/ConcentrationSolid.png}\\
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/ConcentrationLiquid.png}
	\end{columns}
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis - Pressure}
		\tiny{
			\begin{align*}
				\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  -\cfrac{F(t)}{\epsilon A\rho(T(t,z)\textcolor{red}{P}(t))} \cfrac{\partial c(t,z)}{\partial z} 
				+ D^M_e(T(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 c(t,z)}{\partial z^2} + \cfrac{1-\epsilon}{\epsilon} \cfrac{D_i(T(t,z))}{\mu l^2 }\left(q(t,z) - \cfrac{c(t,z)\rho_s}{k_m(T(t,z))\rho(T(t,z)\textcolor{red}{P}(t))} \right)\\
				\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= -\cfrac{D_i(T(t,z))}{\mu l^2 }\left(q(t,z) - c(t,z) \cfrac{\rho_s}{k_m(T(t,z))\rho(T(t,z)\textcolor{red}{P}(t))} \right)\\
				\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= -\cfrac{F(t)}{A} \cfrac{C_p(T(t,z)\textcolor{red}{P}(t))}{ [(1-\epsilon)\rho(T(t,z)\textcolor{red}{P}(t)) C_p(T(t,z)\textcolor{red}{P}(t)) + \epsilon \rho_s C_{ps} ]} \cfrac{\partial T(t,z)}{\partial z} 
				+ D^T_e(T(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 T(t,z)}{\partial z^2}
		\end{align*}}
		\begin{columns}[t]
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/2_SS_R_P.png}\\
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/3_SS_R_P.png}
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Imagesc/2_SS_R_P.png}\\
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Imagesc/3_SS_R_P.png}
		\end{columns}
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis - Pressure}	
		\tiny{
	\begin{align*}
		\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  -\cfrac{F(t)}{\epsilon A\rho(T(t,z)\textcolor{red}{P}(t))} \cfrac{\partial c(t,z)}{\partial z} 
		+ D^M_e(T(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 c(t,z)}{\partial z^2} + \cfrac{1-\epsilon}{\epsilon} \cfrac{D_i(T(t,z))}{\mu l^2 }\left(q(t,z) - \cfrac{c(t,z)\rho_s}{k_m(T(t,z))\rho(T(t,z)\textcolor{red}{P}(t))} \right)\\
		\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= -\cfrac{D_i(T(t,z))}{\mu l^2 }\left(q(t,z) - c(t,z) \cfrac{\rho_s}{k_m(T(t,z))\rho(T(t,z)\textcolor{red}{P}(t))} \right)\\
		\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= -\cfrac{F(t)}{A} \cfrac{C_p(T(t,z)\textcolor{red}{P}(t))}{ [(1-\epsilon)\rho(T(t,z)\textcolor{red}{P}(t)) C_p(T(t,z)\textcolor{red}{P}(t)) + \epsilon \rho_s C_{ps} ]} \cfrac{\partial T(t,z)}{\partial z} 
		+ D^T_e(T(t,z)\textcolor{red}{P}(t)) \cfrac{\partial^2 T(t,z)}{\partial z^2}\\
	\end{align*}}		
		\begin{columns}[t]
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Yield.png}\\
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/1_SS_R_P.png}\\
		\end{columns}	
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis - Void Fraction}
		\tiny{
			\begin{align*}
				\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  -\cfrac{F(t)}{\textcolor{green}{\epsilon}A\rho(T(t,z)P(t))} \cfrac{\partial c(t,z)}{\partial z}
				+ D^M_e(T(t,z)P(t)) \cfrac{\partial^2 c(t,z)}{\partial z^2} + \cfrac{1-\textcolor{green}{\epsilon}}{\textcolor{green}{\epsilon}} \cfrac{D_i(T(t,z))}{\mu l^2 }\left(q(t,z) - \cfrac{c(t,z)\rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
				\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= -\cfrac{D_i(T(t,z))}{\mu l^2}\left(q(t,z) - c(t,z) \cfrac{\rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
				\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= -\cfrac{F(t)}{A} \cfrac{C_p(T(t,z)P(t))}{ [(1-\textcolor{green}{\epsilon})\rho(T(t,z)P(t)) C_p(T(t,z)P(t)) + \textcolor{green}{ \epsilon}\rho_s C_{ps} ]} \cfrac{\partial T(t,z)}{\partial z} 
				+  D^T_e(T(t,z)P(t)) \cfrac{\partial^2 T(t,z)}{\partial z^2}
		\end{align*}}
		\begin{columns}[t]
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/2_SS_R_epsi.png}\\
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/3_SS_R_epsi.png}
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Imagesc/2_SS_R_epsi.png}\\
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Imagesc/3_SS_R_epsi.png}
		\end{columns}
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis - Void Fraction}	
		\tiny{
			\begin{align*}
				\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  -\cfrac{F(t)}{\textcolor{green}{\epsilon}A\rho(T(t,z)P(t))} \cfrac{\partial c(t,z)}{\partial z}
				+ D^M_e(T(t,z)P(t)) \cfrac{\partial^2 c(t,z)}{\partial z^2} + \cfrac{1-\textcolor{green}{\epsilon}}{\textcolor{green}{\epsilon}} 	\cfrac{D_i(T(t,z))}{\mu l^2 }\left(q(t,z) - \cfrac{c(t,z)\rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
				\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= -\cfrac{D_i(T(t,z))}{\mu l^2}\left(q(t,z) - c(t,z) 	\cfrac{\rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
				\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= -\cfrac{F(t)}{A} \cfrac{C_p(T(t,z)P(t))}{ 	[(1-\textcolor{green}{\epsilon})\rho(T(t,z)P(t)) C_p(T(t,z)P(t)) + \textcolor{green}{ \epsilon}\rho_s C_{ps} ]} \cfrac{\partial T(t,z)}{\partial z} 
				+  D^T_e(T(t,z)P(t)) \cfrac{\partial^2 T(t,z)}{\partial z^2}\\
		\end{align*}}		
		\begin{columns}[t]
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Yield.png}\\
			\column{.5\textwidth}
			\centering
			\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/1_SS_R_epsi.png}\\
		\end{columns}	
	\end{frame}

	\begin{frame}[fragile]{Sensitivity Analysis - Internal Diffusion}
	\tiny{
		\begin{align*}
			\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  -\cfrac{F(t)}{\epsilon A\rho(T(t,z)P(t))} \cfrac{\partial c(t,z)}{\partial z} 
			+ D^M_e(T(t,z)P(t)) \cfrac{\partial^2 c(t,z)}{\partial z^2} + \cfrac{1-\epsilon}{\epsilon} \cfrac{\textcolor{orange}{D_i}(\textcolor{blue}{T}(t,z))}{\mu l^2 }\left(q(t,z) - \cfrac{c(t,z)\rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
			\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= -\cfrac{\textcolor{orange}{D_i}(\textcolor{blue}{T}(t,z))}{\mu l^2 }\left(q(t,z) - \cfrac{c(t,z) \rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
			\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= -\cfrac{F(t)}{A} \cfrac{C_p(T(t,z)P(t))}{ [(1-\epsilon)\rho(T(t,z)P(t)) C_p (T(t,z)P(t)) + \epsilon \rho_s C_{ps} ]} \cfrac{\partial T(t,z)}{\partial z} 
			+ D^T_e(T(t,z)P(t)) \cfrac{\partial^2 T(t,z)}{\partial z^2}
	\end{align*}}
	\begin{columns}[t]
		\column{.5\textwidth}
		\centering
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/2_SS_R_betah_{Di}.png}\\
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/3_SS_R_betah_{Di}.png}
		\column{.5\textwidth}
		\centering
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Imagesc/2_SS_R_betah_{Di}.png}\\
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Imagesc/3_SS_R_betah_{Di}.png}
	\end{columns}
\end{frame}

\begin{frame}[fragile]{Sensitivity Analysis - Internal Diffusion}	
	\tiny{
		\begin{align*}
			\cfrac{\partial \textcolor{blue}{c}(t,z)}{\partial t} &=  -\cfrac{F(t)}{\epsilon A\rho(T(t,z)P(t))} \cfrac{\partial c(t,z)}{\partial z} 
			+ D^M_e(T(t,z)P(t)) \cfrac{\partial^2 c(t,z)}{\partial z^2} + \cfrac{1-\epsilon}{\epsilon} 	\cfrac{\textcolor{orange}{D_i}(\textcolor{blue}{T}(t,z))}{\mu l^2 }\left(q(t,z) - \cfrac{c(t,z)\rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
			\cfrac{\partial \textcolor{blue}{q}(t,z)}{\partial t} &= -\cfrac{\textcolor{orange}{D_i}(\textcolor{blue}{T}(t,z))}{\mu l^2 }\left(q(t,z) - 	\cfrac{c(t,z) \rho_s}{k_m(T(t,z))\rho(T(t,z)P(t))} \right)\\
			\cfrac{\partial \textcolor{blue}{T}(t,z)}{\partial t} &= -\cfrac{F(t)}{A} \cfrac{C_p(T(t,z)P(t))}{ [(1-\epsilon)\rho(T(t,z)P(t)) C_p 	(T(t,z)P(t)) + \epsilon \rho_s C_{ps} ]} \cfrac{\partial T(t,z)}{\partial z} 
			+ D^T_e(T(t,z)P(t)) \cfrac{\partial^2 T(t,z)}{\partial z^2}\\
	\end{align*}}		
	\begin{columns}[t]
		\column{.5\textwidth}
		\centering
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Yield.png}\\
		\column{.5\textwidth}
		\centering
		\includegraphics[width=5.5cm,height=2.5cm]{Figures/Sensitivity/Plots/1_SS_R_betah_{Di}.png}\\
	\end{columns}	
	\end{frame}

	\begin{frame}[fragile]{What's next?}
		\begin{itemize}
			\item Paper related to the sensitivity analysis
			\item Control of the extraction process
			\item NovelBaltic
			\item Laboratory work 
		\end{itemize}
	\end{frame}

\end{document}

### 2024-07-17 SFE_poster_DOE/main.tex
17.07

\documentclass[20pt,margin=1in,innermargin=-4.5in,blockverticalspace=-0.25in]{tikzposter}
\geometry{paperwidth=42in,paperheight=30in}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{enumitem}
\usepackage[backend=biber,style=numeric]{biblatex}
\usepackage{emory-theme}

\usepackage{mwe} % for placeholder images

\addbibresource{refs.bib}

% set theme parameters
\tikzposterlatexaffectionproofoff
\usetheme{EmoryTheme}
\usecolorstyle{EmoryStyle}

\title{Optimal design of experiment: supercritical fluid extraction case}
\author{O.Sliczniuk\textsuperscript{$\dagger$} and P.Oinas\textsuperscript{$\dagger$}}
\institute{\textsuperscript{$\dagger$}School of Chemical Engineering, Aalto University, Finland}
\titlegraphic{\includegraphics[width=0.07\textwidth]{Aalto_University_logo.png}}

% begin document
\begin{document}
\maketitle
\centering
\begin{columns}
    \column{0.32}
    \block{Abstract}{
         This study investigates the extraction of valuable components from biomass using supercritical carbon dioxide as a solvent. The interest is in essential oils retrieved from chamomile flowers in cylindrical extractors operated in a semi-batch mode. A mathematical model, which describe the extraction process is proposed and validated in the range of operating conditions. The process model includes empirical correlations, which describe the relation between the extraction kinetics parameters and the operating conditions. This work aims to validate the empirical correlations by designing a new experiment with dynamically changing operating conditions.
    }
    \block{Model}{
         The extraction process is represented by a distributed-parameter model consisting of partial differential equations. This model has been validated within the operating conditions: temperatures between $30 - 40^\circ C$, pressures between 100 – 200 bar, and mass flow rates between $3.33 - 6.67 \times 10^{-5}$ kg/s. The solute extraction from the solid to the fluid phase is described using the two-film theory for a single component. The physical properties of the fluid and pseudo-homogeneous phase are considered to be locally dependent on temperature and pressure and are calculated using the Peng-Robinson equation of state. By incorporating the enthalpy balance, the extraction kinetic becomes a function of operating conditions. Empirical correlations were developed to generalize the process model across the entire range of operating conditions.
         \begin{align*} 
            \frac{\partial c_f}{\partial t} + \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z} &= \frac{1-\phi}{\phi} r_e + \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right) \\
            \cfrac{\partial c_s}{\partial t} &= r_e \\
            \cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h} A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) \\
            \cfrac{dy}{dt} &= \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} \\
            r_e &= -\cfrac{ D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
         \end{align*}

        \vspace{1em}
        \begin{tikzfigure}[Empirical correlations]
        	\includegraphics[width=0.45\linewidth]{Di_Re_F_1}
        	\includegraphics[width=0.45\linewidth]{Gamma_Re_F_1}
        \end{tikzfigure}
        \vspace{1em}
    }

    \column{0.36}
    \block{Model-based optimal design of experiment}{
        The Fisher information $\mathcal{F}$ is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable. The $\mathcal{F}$ is related to the second derivative of the log-likelihood function with respect to the parameters $\Theta$, given the standard deviation $\sigma^2$. Based on the Cramer-Rao inequality, $\mathcal{F}$ can used to calculate the covariance matrices associated with maximum-likelihood estimates.

        \begin{equation*}
        	%\Sigma^{-1} \geq
        	\mathcal{F}(\Theta) = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y(t_i, \Theta)}{\partial \Theta} \frac{\partial y(t_i, \Theta)}{\partial \Theta^\top} \right) 
        \end{equation*}

        The optimal design of experiments is a statistical concept that refers to the process of planning an experiment, which allow parameters to be estimated without bias and with minimum variance.

        The D-optimality criterion is selected as the objective function, which leads to the minimisation of the volume of the ellipsoidal confidence region of parameter estimates. This criterion seeks to maximize the determinant of the information matrix $\mathcal{F}$ of the design $\Xi$ (set of controls).

        \begin{equation*}
        	\begin{aligned} 
        		&\Xi^* &= \arg &\min_{ T^{in},~F,~P~\in~\Xi}\quad\int_{t_0=0~min}^{t_f=300~min} - \ln \det \mathcal{F}(\Theta, \Xi)~dt  \\
        		&\text{subject to}
        		& \dot{x} &= G(x,t,\Theta;\Xi) \\
        		&& T^{0} &= T^{in}(t=0) \\
        		&& 30^\circ C &\leq T^{in}(t) ~ \leq 40^\circ C \\
        		&& 3.33 \cdot 10^{-5} &\leq F(t)\quad \leq 6.67 \cdot 10^{-5} \\
        		&& 100~bar&\leq P(t)\quad \leq 200~bar \\
        	\end{aligned}
        \end{equation*}

    }
    \block{Results}{    
        \vspace{1em}
        \begin{tikzfigure}[Big fancy graphic.]
            \includegraphics[width=0.9\linewidth]{Di_Re_F_1}
        \end{tikzfigure}
        \vspace{1em}

        It was Levi-Civita--Littlewood who first asked whether essentially negative definite paths can be computed. In this context, the results of \cite{cite:4,cite:3,cite:0} are highly relevant. Here, existence is clearly a concern. Hence in \cite{cite:5}, the authors characterized primes. Now is it possible to derive pairwise empty equations? Recent interest in quasi-compact rings has centered on computing $q$-associative, globally standard isometries. Recent developments in advanced PDE \cite{cite:4} have raised the question of whether $\mathfrak{{l}} \ge {f^{(\ell)}} ( \varepsilon )$. Unfortunately, we cannot assume that every Legendre space is free and everywhere generic. It is essential to consider that $y$ may be bounded. Let us suppose ${\mathscr{{K}}_{\mathscr{{M}}}} = \| S \|$.  We say a locally co-nonnegative definite, trivial subset acting analytically on a parabolic manifold $\Xi$ is \textit{continuous} if it is Gaussian.
    }

    \column{0.32}
    \block{Comparison}{
        Recent developments in symbolic group theory \cite{cite:0} have raised the question of whether $\mathscr{{J}} \le I$. The groundbreaking work of Q. Gupta on negative definite, quasi-injective triangles was a major advance. Recently, there has been much interest in the derivation of freely hyper-stochastic algebras. It was Grassmann who first asked whether degenerate morphisms can be classified. In \cite{cite:4}, the main result was the derivation of sub-analytically degenerate classes. Unfortunately, we cannot assume that $\mathfrak{{\ell}} ( \mathfrak{{z}}' ) \ne \| {\varepsilon_{\xi}} \|$.

        \begin{tikzfigure}[Look, my method is better.]
            \includegraphics[width=0.5\linewidth]{example-image}
        \end{tikzfigure}
    }

    \block{Remarks}{
        In \cite{cite:3}, the main result was the characterization of normal, orthogonal matrices. This could shed important light on a conjecture of Cardano--Pascal. In this context, the results of \cite{cite:2} are highly relevant. The work in \cite{cite:1} did not consider the countably minimal case. A {}useful survey of the subject can be found in \cite{cite:4}. Unfortunately, we cannot assume that $0 \cong \cosh x$.
    }

    \block{Acknowledgements}{
        Lorem ipsum dolor sit amet, probo dolorem cu vis. Cu mei audire fabulas scriptorem, cu has clita fabulas. Sea id veritus maiorum indoctum, mea cu assum cetero. Ei posse movet maluisset vim.
    }

    \block{References}{
        \vspace{-1em}
        \begin{footnotesize}
        \printbibliography[heading=none]
        \end{footnotesize}
    }
\end{columns}
\end{document}

### 2024-07-17 SFE_DOE_Chamomile/SFE_map.m

@@ -1,0 +1,302 @@
+startup;
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
+
+addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+import casadi.*
+
+%% Create the solver
+tic
+Iteration_max               = 100;                                           % Maximum number of iterations for optimzer
+Time_max                    = 1;                                             % Maximum time of optimization in [h]
+
+nlp_opts                    = struct;
+nlp_opts.ipopt.max_iter     = Iteration_max;
+nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+%nlp_opts.ipopt.hessian_approximation ='limited-memory';
+%nlp_opts.ipopt.acceptable_tol  = 1e-4;
+%nlp_opts.ipopt.acceptable_iter = 5;
+
+OPT_solver                  = casadi.Opti();
+ocp_opts                    = {'nlp_opts', nlp_opts};
+OPT_solver.solver(             'ipopt'   , nlp_opts)
+
+%%
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('wpd_datasets.xlsx');
+which_dataset           = 4;
+
+SAMPLE                  = LabResults(21:34,1);
+data_org                = LabResults(21:34,which_dataset+1)';
+
+%% Load paramters
+N_exp                   = 6;
+N_core                  = 6;
+
+m_total                 = 3.0;
+
+% Bed geometry
+before                  = 0.04;                                             % Precentage of length before which is empty
+bed                     = 0.92;                                              % Percentage of length occupied by fixed bed
+
+% Set time of the simulation
+PreparationTime         = 0;
+ExtractionTime          = 300;
+timeStep                = 10;                                                % Minutes
+SamplingTime            = 10;                                                % Minutes
+OP_change_Time          = 10;                                                % Minutes
+
[…]

### 2024-07-17 SFE_DOE_Chamomile/modelSFE.m

@@ -8,7 +8,7 @@ function xdot = modelSFE(x, p, mask, dt)
     %% Load Paramters
     T_u           =     p{1};
     P_u           =     p{2};
-    F_u           =     p{3};
+    F_u           =     p{3} * 10^(-5);
 
     parameters    =     p(4:end);
 
@@ -48,7 +48,8 @@ function xdot = modelSFE(x, p, mask, dt)
     RHO           =     rhoPB_Comp(     TEMP, PRESSURE, Z, parameters);   
     MU            =     Viscosity(TEMP,RHO);
 
-    VELOCITY      =     Velocity(F_u, mean([RHO(2:25:end)]), parameters);
+    %VELOCITY      =     Velocity(F_u, mean([RHO(2:25:end)]), parameters);
+    VELOCITY      =     Velocity(F_u, RHO(2), parameters);
 
     RE            =     dp .* RHO .* VELOCITY ./ MU;
     

### 2024-07-18 SFE_DOE_Chamomile/SFE_map.m
18.07

@@ -1,15 +1,17 @@
-startup;
-delete(gcp('nocreate'));
-% %p = Pushbullet(pushbullet_api);
+%startup;
+%delete(gcp('nocreate'));
+%p = Pushbullet(pushbullet_api);
+initParPool
 
-addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpatch('casadi_folder')
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
 %addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
 %% Create the solver
 tic
 Iteration_max               = 100;                                           % Maximum number of iterations for optimzer
-Time_max                    = 1;                                             % Maximum time of optimization in [h]
+Time_max                    = 12;                                             % Maximum time of optimization in [h]
 
 nlp_opts                    = struct;
 nlp_opts.ipopt.max_iter     = Iteration_max;
@@ -33,8 +35,8 @@ SAMPLE                  = LabResults(21:34,1);
 data_org                = LabResults(21:34,which_dataset+1)';
 
 %% Load paramters
-N_exp                   = 6;
-N_core                  = 6;
+N_exp                   = 12;
+N_core                  = 14;
 
 m_total                 = 3.0;
 
@@ -243,7 +245,7 @@ toc
 %}
 %%
 tic
-H = OPT_solver.to_function('H',{T0homog,Flow},{T0homog,Flow})
+H = OPT_solver.to_function('H',{T0homog,Flow},{T0homog,Flow});
 toc
 %%
 tic
@@ -257,20 +259,21 @@ toc
 
 %%
 tic
-[HH_map_1, HH_map_2] = H_map(T0, F0)
+[HH_map_1, HH_map_2] = full( H_map(T0, F0) );
 toc
 
 %%
 tic
-COST_0 = full( GG([T0, T0] ,  [F0, F0]  , cell2mat(Parameters(which_theta)) ));
+COST_0 = GG([T0, T0] ,  [F0, F0]  , cell2mat(Parameters(which_theta)) );
 toc
 tic 
-COST   = full( GG(HH_1, HH_2, cell2mat(Parameters(which_theta)) ));
+COST   = GG(HH_map_1, HH_map_2, cell2mat(Parameters(which_theta)) );
 toc 
 
[…]

### 2024-07-18 SFE_DOE_Chamomile/parallel.sh

@@ -1,0 +1,9 @@
+#!/bin/bash 
+#SBATCH --time=14:00:00
+#SBATCH --mem-per-cpu=3G
+#SBATCH --cpus-per-task=12
+#SBATCH --output=matlab_parallel.out
+
+module load matlab
+
+srun matlab -nodisplay -r 'SFE_map'

### 2024-08-02 SFE_poster_DOE/conference_poster_6.tex
02.08

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% a0poster Portrait Poster
% LaTeX Template
% Version 1.0 (22/06/13)
%
% The a0poster class was created by:
% Gerlinde Kettl and Matthias Weiser (tex@kettl.de)
% 
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a0,portrait]{a0poster}

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster

\usepackage[svgnames]{xcolor} % Specify colors by their 'svgnames', for a full list of all colors available see here: http://www.latextemplates.com/svgnames-colors

\usepackage{times} % Use the times font
%\usepackage{palatino} % Uncomment to use the Palatino font

\usepackage{graphicx} % Required for including images
\graphicspath{{figures/}} % Location of the graphics files
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures

\usepackage{tcolorbox}

\begin{document}
\pagecolor{white!90!black}
%----------------------------------------------------------------------------------------
%	POSTER HEADER 
%----------------------------------------------------------------------------------------

% The header is divided into two boxes:
% The first is 75% wide and houses the title, subtitle, names, university/organization and contact information
% The second is 25% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit

\begin{minipage}[b]{0.75\linewidth}
\veryHuge \color{NavyBlue} \textbf{Optimal design of experiment:} \color{Black}\\ % Title
\Huge\textit{supercritical fluid extraction case}\\[2cm] % Subtitle
\huge \textbf{Oliwer Sliczniuk \& Pekka Oinas}\\[0.5cm] % Author(s)
\huge School of Chemical Engineering, Aalto University, Finland\\[0.4cm] % University/organization
%\Large \texttt{john@LaTeXTemplates.com} --- 1 (000) 111 1111\\
\end{minipage}
%
\begin{minipage}[b]{0.25\linewidth}
\includegraphics[width=15cm]{Aalto_University_logo.png}\\ \\
\end{minipage}

%\vspace{0.5cm} % A bit of extra whitespace between the header and poster content
\noindent\rule{\textwidth}{3pt}
%\vspace{0.25cm} % A bit of extra whitespace between the header and poster content

%----------------------------------------------------------------------------------------

\begin{multicols}{2} % This is how many columns your poster will be broken into, a portrait poster is generally split into 2 columns

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

%\color{Navy} % Navy color for the abstract

%\begin{abstract}

%\end{abstract}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

%\color{Navy} % SaddleBrown color for the introduction

\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
	{\LARGE Introduction\\}

This study investigates the extraction of valuable components from biomass using supercritical carbon dioxide as a solvent. The interest is in essential oils extracted from chamomile flowers in cylindrical extractors operated in a semi-batch mode. The extraction process is described by a distributed-parameter model, and set of empirical correlations. This work aims \underline{to validate the empirical correlations by designing a new experiment} with dynamically changing operating conditions. %The process model includes empirical correlations, which describe the relation between the extraction kinetics parameters and the operating conditions. 
\end{tcolorbox}

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

%\color{DarkSlateGray} % DarkSlateGray color for the rest of the content

%\section*{Main Objectives}

%\begin{enumerate}
%\item Lorem ipsum dolor sit amet, consectetur.
%\item Nullam at mi nisl. Vestibulum est purus, ultricies cursus volutpat sit amet, vestibulum eu.
%\item Praesent tortor libero, vulputate quis elementum a, iaculis.
%\item Phasellus a quam mauris, non varius mauris. Fusce tristique, enim tempor varius porta, elit purus commodo velit, pretium mattis ligula nisl nec ante.
%\item Ut adipiscing accumsan sapien, sit amet pretium.
%\item Estibulum est purus, ultricies cursus volutpat
%\item Nullam at mi nisl. Vestibulum est purus, ultricies cursus volutpat sit amet, vestibulum eu.
%\item Praesent tortor libero, vulputate quis elementum a, iaculis.
%\end{enumerate}

%----------------------------------------------------------------------------------------
%	MATERIALS AND METHODS
%----------------------------------------------------------------------------------------

%\section*{Materials and Methods}

%Fusce magna risus, molestie ut porttitor in, consectetur sed mi. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque consectetur blandit pellentesque. Sed odio justo, viverra nec porttitor vel, lacinia a nunc. Suspendisse pulvinar euismod arcu, sit amet accumsan enim fermentum quis. In id mauris ut dui feugiat egestas. Vestibulum ac turpis lacinia nisl commodo sagittis eget sit amet sapien.

%------------------------------------------------

%\vspace{0.1cm}
%\section*{Process Model}
\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
	{\LARGE Process Model\\}

\begin{minipage}[b]{0.45\linewidth}
	\begin{itemize}
		\item One-dimensional
		\item Plug flow
		\item No pressure drop
		\item Uniform particle distribution
	\end{itemize}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
	\begin{itemize}
		\item Based on the two-film theory for a single component
		\item Peng-Robinson equation of state
		\item Decaying extraction kinetic
		\item Empirical correlations
	\end{itemize}
\end{minipage}

%\begin{minipage}[b]{0.5\linewidth}
%	\begin{itemize}
%		\item Based on the two-film theory for a single component
%		\item Peng-Robinson equation of state
%		\item Decaying extraction kinetic
%		\item Empirical correlations
%	\end{itemize}
%\end{minipage}

%The extraction process is represented by a \underline{distributed-parameter model} consisting of partial differential equations. This model has been validated within the operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33 - 6.67 \times 10^{-5}$ kg/s. The solute extraction from the solid to the fluid phase is described using the two-film theory for a single component. The physical properties of the fluid and pseudo-homogeneous phase are considered to be locally dependent on temperature and pressure and are calculated using the Peng-Robinson equation of state. By incorporating the enthalpy balance, the extraction kinetic becomes a function of operating conditions. Empirical correlations were developed to generalize the process model across the entire range of operating conditions.

\begin{align*}
	\dot{x} = \cfrac{d x}{d t} = 
	\begin{bmatrix}
		\frac{\partial c_f}{\partial t} \\
		\\
		\cfrac{\partial c_s}{\partial t} \\
		\\
		\cfrac{\partial \left(\rho_f h A_f\right)}{\partial t} \\
		\\
		\cfrac{d y}{d t}
	\end{bmatrix}
	=
\underbrace{\begin{bmatrix}
		-\frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z} + \frac{1-\phi}{\phi} \cfrac{\partial c_s}{\partial t} + \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right) \\
		-\cfrac{ D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right) \\
		- \cfrac{\partial \left( \rho_f h A_f {\color{red}v} \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) \\
		\cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L}
	\end{bmatrix}}_{G(x,t,\Theta;\Xi)}
\end{align*}

\begin{minipage}[h!]{0.5\linewidth}
	\begin{align*}
		c_f &- \text{Soluts concentration in the fluid phase}\\
		c_s &- \text{Soluts concentration in the solid phase}\\
		h~  &- \text{Enthalpy}\\
		y~ &- \text{Extraction yield}\\
		\rho_f &- \text{Density of fluid}\\
		A_f &- \text{Cross-section of the bed}\\
		u~~ &- \text{Darcy velocity}\\
		\phi~~ &- \text{Void fraction}
	\end{align*}
\end{minipage}
%
\begin{minipage}[h!]{0.5\linewidth}
	\begin{align*}
		D_e^M &- \text{Axial mass diffusivity}\\
		D_i^R &- \text{Internal mass diffusivity}\\
		\Upsilon~~ &- \text{Decaying factor}\\
		\rho_s~ &- \text{Bulky density of solid bed}\\
		~k_m &- \text{Partition factor}\\
		P~~ &- \text{Pressure}\\
		T~~ &- \text{Temperature}\\
		F~~ &- \text{Mass flow rate}
	\end{align*}
\end{minipage}

\begin{center}%\vspace{1cm}
	\includegraphics[width=0.49\linewidth]{Di_Re_F_1.png}
	\includegraphics[width=0.49\linewidth]{Gamma_Re_F_1.png}
	\captionof{figure}{Empirical correlations}
\end{center}%\vspace{1cm}

\end{tcolorbox}

\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
%------------------------------------------------
%\vspace{1cm}
%\section*{Model-based optimal design of experiment}
\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
	{\LARGE Model-based optimal design of experiment\\}
\end{tcolorbox}

\underline{Fisher information $\mathcal{F}$ measures the amount of information} that an observable random variable carries about an unknown parameter of a distribution that models the random variable. $\mathcal{F}$ is defined as Hessian of the log-likelihood function with respect to the parameters $\Theta$, given the covariance matrix $\Sigma$. %Based on the Cramer-Rao inequality, $\mathcal{F}$ can used to calculate the covariance matrices associated with maximum-likelihood estimates.

\begin{equation*}
	%\Sigma^{-1} \geq
	\mathcal{F}(t,\Theta; \Xi) = \frac{\partial y(t, \Theta; \Xi)}{\partial \Theta} \Sigma \frac{\partial y(t, \Theta; \Xi)}{\partial \Theta^\top}
\end{equation*}

The optimal design of experiments is a concept that refers to planning an experiment, which allow parameters to be estimated without bias and with minimum variance. The D-optimality criterion is selected as the objective function, which leads to \underline{the minimisation of the volume of the ellipsoidal confidence region of parameter estimates} given the experimental condition $\Xi$.

\begin{equation*}
	\begin{aligned} 
		&\Xi^* &= \arg &\min_{ T^{in},~F\in~\Xi}\quad\int_{t_0}^{t_f} - \ln \det \mathcal{F}(t,\Theta; \Xi)~dt  \\
		&\text{subject to}
		& \dot{x} = ~&G~~(x,t,\Theta;\Xi) \\
		&& T^{0} = ~&T^{in}(t=0) \\
		&& 30^\circ C \leq ~&T^{in}(t) ~ \leq 40^\circ C \\
		&& 3.33 \cdot 10^{-5}~\text{kg/s} \leq ~&F~~(t)~ \leq 6.67 \cdot 10^{-5}~\text{kg/s}\\
		&& 100~\text{bar} \leq ~&P~~(t)~ \leq 200~\text{bar} \\
	\end{aligned}
\end{equation*}

\underline{This work aims to design a dynamic experiment to improve precision of correlation for $D_i^R$}. The system is assumed to run for 300 min, with sampling time of 10 min. The set of decision variables consists of $T^{in}$ and $F$, and each of them is manipulated every 15 min. Each of five analysed cases assumes that P is kept constant at 100, 125, 150, 175 and 200 bar, respectively.
\end{tcolorbox}
%----------------------------------------------------------------------------------------
%	RESULTS 
%----------------------------------------------------------------------------------------
\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
	{\LARGE Results\\}

	To identify the global solution, the optimization problem is solved multiple times, each starting from a random initial solution. Figure 2 compares the initial and final values of the cost function across multiple optimization runs for different cases of pressure value.

	\begin{center}%\vspace{1cm}
		\includegraphics[width=\linewidth]{scatter.png}
		\captionof{figure}{Values of the objective function}
	\end{center}%\vspace{1cm}

	The optimal profiles of the inlet temperature and flow rates for each case are showed in Figure 3

	\begin{center}%\vspace{1cm}
		\includegraphics[width=0.49\linewidth]{Profile_T.png}
		\includegraphics[width=0.49\linewidth]{Profile_F.png}
		\captionof{figure}{Optimal profiles}
	\end{center}%\vspace{1cm}

\end{tcolorbox}

%----------------------------------------------------------------------------------------
%	CONCLUSIONS
%----------------------------------------------------------------------------------------

\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out

\section*{Conclusions}

\begin{itemize}
\item Pellentesque eget orci eros. Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh. Phasellus fermentum rutrum elementum. Nam quis justo lectus.
\item Vestibulum sem ante, hendrerit a gravida ac, blandit quis magna.
\item Donec sem metus, facilisis at condimentum eget, vehicula ut massa. Morbi consequat, diam sed convallis tincidunt, arcu nunc.
\item Nunc at convallis urna. isus ante. Pellentesque condimentum dui. Etiam sagittis purus non tellus tempor volutpat. Donec et dui non massa tristique adipiscing.
\end{itemize}

\color{DarkSlateGray} % Set the color back to DarkSlateGray for the rest of the content

%----------------------------------------------------------------------------------------
%	FORTHCOMING RESEARCH
%----------------------------------------------------------------------------------------

\section*{Forthcoming Research}

Vivamus molestie, risus tempor vehicula mattis, libero arcu volutpat purus, sed blandit sem nibh eget turpis. Maecenas rutrum dui blandit lorem vulputate gravida. Praesent venenatis mi vel lorem tempor at varius diam sagittis. Nam eu leo id turpis interdum luctus a sed augue. Nam tellus.

 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\nocite{*} % Print all references regardless of whether they were cited in the poster or not
\bibliographystyle{plain} % Plain referencing style
\bibliography{sample} % Use the example bibliography file sample.bib

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\section*{Acknowledgements}

Etiam fermentum, arcu ut gravida fringilla, dolor arcu laoreet justo, ut imperdiet urna arcu a arcu. Donec nec ante a dui tempus consectetur. Cras nisi turpis, dapibus sit amet mattis sed, laoreet.

%----------------------------------------------------------------------------------------

\end{multicols}
\end{document}

### 2024-08-02 Sections/Optimal_design_of_experiment.tex
17.07
02.08

@@
 Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, etc.).
-Experiment design aims to determine experimental conditions adapted to the final purpose of the modeling.
+Experiment design aims to determine experimental conditions adapted to the final purpose of the modelling.
 
@@
 Setting $Q = \textbf{I}_{n_\Theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalues of the Fisher information matrix, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.
-The most commonly used optimality criterion involves $k = 0$, $Q = \textbf{I}_{n_\Theta}$, requiring the minimization of $\det \mathcal{F}^{-1}(\Theta, \Xi)$, or, equivalently, maximization of
+The most commonly used criterion is the D-optimality that involves $k = 0$, $Q = \textbf{I}_{n_\Theta}$, requiring the minimization of $\det \mathcal{F}^{-1}(\Theta, \Xi)$, or, equivalently, maximization of
 
@@
 
-	A D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.
-The graphical representation of the different optimality conditions is shown in Figure \ref{fig:score_fun}.
+	The D-optimality criterion originates from the geometric interpretation of the determinant.
+A two-dimensional matrix with real number entries can represent two linear maps: one mapping the standard basis vectors to the rows and the other to the columns.
+In both cases, the images of the basis vectors form a parallelogram that represents the image of the unit square under the mapping.
+The absolute value of the determinant is the area of this parallelogram, reflecting the scale factor by which the matrix transforms areas.
+The signed value of the determinant indicates the oriented area of the parallelogram, which is negative when the angle from the first to the second defining vector is clockwise.
+In the multi-dimensional case, the matrix maps the n-cube to an n-dimensional parallelotope.
+The determinant provides the signed n-dimensional volume of this parallelotope, describing the volume scaling factor of the linear transformation produced by the matrix.
+Based on this geometric interpretation, a D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.
+Figure \ref{fig:score_fun} illustrates the graphical representation of different optimality conditions.
 

### 2024-08-02 SFE_DOE_Chamomile/Case_1_T_F/main_Results.m

@@ -1,0 +1,94 @@
+startup;
+delete(gcp('nocreate'));
+%p = Pushbullet(pushbullet_api);
+%initParPool
+
+%addpatch('casadi_folder')
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+%import casadi.*
+
+%% Load data
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+r                       = Parameters{3};                                    % Radius of the extractor  [m]
+epsi                    = Parameters{4};                                    % Fullness [-]
+dp                      = Parameters{5};                                    % Paritcle diameter
+L                       = Parameters{6};                                    % Total length of the extractor [m]
+
+V                       = L  * pi * r^2;                                    % Total volume of the extractor [m3]
+A                       = pi *      r^2;                                    % Extractor cross-section
+
+%--------------------------------------------------------------------
+
+N_exp    = 50;
+COST_I   = []; COST_F   = []; GROUP    = [];
+%hold on
+for ii = [100, 125, 150, 175, 200]
+    AA       = readlines(['Cost_',num2str(ii),'.txt']);
+    InitCost = str2num(AA(1));
+    FinaCost = str2num(AA(2));
+    COST_I   = [ COST_I , InitCost];
+    COST_F   = [ COST_F , FinaCost];
+    GROUP    = [GROUP; repmat(['P = ', num2str(ii),' bar'], numel(FinaCost),1) ];
+    
+    AA       = readlines(['Control_',num2str(ii),'.txt']);
+    TempCont = str2num(AA(1));
+    TempCont = reshape(TempCont,[],N_exp);
+    FlowCont = str2num(AA(2));
+    FlowCont = reshape(FlowCont,[],N_exp);
+    
+    Time     = linspace(0,300,size(TempCont,1)+1);
+
+    % Plots of controls
+    ind      = find( FinaCost == min(FinaCost));
+    
[…]

### 2024-08-04 SFE_poster_DOE/conference_poster_6.tex
04.08

@@
 \Huge\textit{supercritical fluid extraction case}\\[2cm] % Subtitle
-\huge \textbf{Oliwer Sliczniuk \& Pekka Oinas}\\[0.5cm] % Author(s)
+\huge \textbf{Oliwer Sliczniuk, Pekka Oinas}\\[0.5cm] % Author(s)
 \huge School of Chemical Engineering, Aalto University, Finland\\[0.4cm] % University/organization
@@
 The interest is in essential oils extracted from chamomile flowers in cylindrical extractors operated in a semi-batch mode.
-The extraction process is described by a distributed-parameter model, and set of empirical correlations.
-This work aims \underline{to validate the empirical correlations by designing a new experiment} with dynamically changing operating conditions.
+The process is described by a distributed-parameter model, and set of empirical correlations.
+This work aims \underline{to validate empirical} \underline{correlations by designing a new experiment with dynamically changing operating conditions}.
 %The process model includes empirical correlations, which describe the relation between the extraction kinetics parameters and the operating conditions.
@@
 
-%\vspace{0.1cm}
 %\section*{Process Model}
@@
 
-\begin{minipage}[b]{0.45\linewidth}
+\vspace{0.5cm}
+
+\begin{minipage}[b]{0.5\linewidth}
 	\begin{itemize}
@@
 \hfill
-\begin{minipage}[b]{0.45\linewidth}
+\begin{minipage}[b]{0.5\linewidth}
 	\begin{itemize}
-		\item Based on the two-film theory for a single component
+		\item Two-film theory for a single component
 		\item Peng-Robinson equation of state
@@
 \underbrace{\begin{bmatrix}
-		-\frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z} + \frac{1-\phi}{\phi} \cfrac{\partial c_s}{\partial t} + \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right) \\
+		-\frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z} - \frac{1-\phi}{\phi} \cfrac{\partial c_s}{\partial t} + \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right) \\
 		-\cfrac{ D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right) \\
@@
 	\begin{align*}
-		c_f &- \text{Soluts concentration in the fluid phase}\\
-		c_s &- \text{Soluts concentration in the solid phase}\\
+		c_f &- \text{Solutes concentration in the fluid phase}\\
+		c_s &- \text{Solutes concentration in the solid phase}\\
 		h~  &- \text{Enthalpy}\\
@@
 		u~~ &- \text{Darcy velocity}\\
-		\phi~~ &- \text{Void fraction}
+		\phi~~ &- \text{Void fraction}\\
+		D_i^R &- \text{Internal mass diffusivity}
 	\end{align*}
@@
 		D_e^M &- \text{Axial mass diffusivity}\\
-		D_i^R &- \text{Internal mass diffusivity}\\
-		\Upsilon~~ &- \text{Decaying factor}\\
-		\rho_s~ &- \text{Bulky density of solid bed}\\
-		~k_m &- \text{Partition factor}\\
-		P~~ &- \text{Pressure}\\
-		T~~ &- \text{Temperature}\\
-		F~~ &- \text{Mass flow rate}
+		\mu~ &- \text{Particle shape coefficient}\\
+		l~ &- \text{Particle length}\\
+		\Upsilon~ &- \text{Decaying factor}\\
+		\rho_s &- \text{Bulk density of solid bed}\\
+		k_m &- \text{Partition factor}\\
+		P~ &- \text{Pressure}\\
+		T~ &- \text{Temperature}\\
+		F~ &- \text{Mass flow rate}
 	\end{align*}
@@
 
-\begin{center}%\vspace{1cm}
+\begin{center}\vspace{0.5cm}
 	\includegraphics[width=0.49\linewidth]{Di_Re_F_1.png}
@@
 \underline{Fisher information $\mathcal{F}$ measures the amount of information} that an observable random variable carries about an unknown parameter of a distribution that models the random variable.
-$\mathcal{F}$ is defined as Hessian of the log-likelihood function with respect to the parameters $\Theta$, given the covariance matrix $\Sigma$.
+$\mathcal{F}$ is defined as Hessian of the likelihood function with respect to parameters $\Theta$, given the covariance matrix $\Sigma$.
 %Based on the Cramer-Rao inequality, $\mathcal{F}$ can used to calculate the covariance matrices associated with maximum-likelihood estimates.
@@
 The optimal design of experiments is a concept that refers to planning an experiment, which allow parameters to be estimated without bias and with minimum variance.
-The D-optimality criterion is selected as the objective function, which leads to \underline{the minimisation of the volume of the ellipsoidal confidence region of parameter estimates} given the experimental condition $\Xi$.
+The D-optimality criterion is selected as the objective function, which leads to \underline{the minimisation of the volume} \underline{of the ellipsoidal confidence region of parameter estimates} given the experimental condition $\Xi$.
 
@@
 
-	\begin{center}%\vspace{1cm}
+	\begin{center}\vspace{0.5cm}
 		\includegraphics[width=\linewidth]{scatter.png}
@@
 
-	\begin{center}%\vspace{1cm}
-		\includegraphics[width=0.49\linewidth]{Profile_T.png}
-		\includegraphics[width=0.49\linewidth]{Profile_F.png}
+	\begin{center}\vspace{0.5cm}
+		\includegraphics[width=\linewidth]{Profiles.png}
 		\captionof{figure}{Optimal profiles}
@@
 
-\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out
-
-\section*{Conclusions}
+\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
+	{\LARGE Conclusions\\}
 
 	\begin{itemize}
-\item Pellentesque eget orci eros.
-Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.
-Phasellus fermentum rutrum elementum.
-Nam quis justo lectus.
-\item Vestibulum sem ante, hendrerit a gravida ac, blandit quis magna.
-\item Donec sem metus, facilisis at condimentum eget, vehicula ut massa. Morbi consequat, diam sed convallis tincidunt, arcu nunc.
-\item Nunc at convallis urna. isus ante. Pellentesque condimentum dui. Etiam sagittis purus non tellus tempor volutpat. Donec et dui non massa tristique adipiscing.
+		\item The optimal profiles of controls are similar for all the cases
+		\item Low values of the objective are obtained at pressures close to supercritical point, where the variation in the inlet temperature cause large deviation in the physical properties of CO$_2$ and Reynolds number
+		\item The mass flow rate is used as main control variable, which suggest that the system is more sensitive to the mass flow rate than the inlet temperature
 	\end{itemize}
 
-\color{DarkSlateGray} % Set the color back to DarkSlateGray for the rest of the content
+\end{tcolorbox}
 

### 2024-08-05 SFE_poster_DOE/conference_poster_6.tex
05.08

@@
 \usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
-\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
+\usepackage{amsfonts, amsmath, amsthm, amssymb, enumitem} % For math fonts, symbols and environments
 \usepackage{wrapfig} % Allows wrapping text around tables and figures
@@
 
-This study investigates the extraction of valuable components from biomass using supercritical carbon dioxide as a solvent.
-The interest is in essential oils extracted from chamomile flowers in cylindrical extractors operated in a semi-batch mode.
-The process is described by a distributed-parameter model, and set of empirical correlations.
-This work aims \underline{to validate empirical} \underline{correlations by designing a new experiment with dynamically changing operating conditions}.
-%The process model includes empirical correlations, which describe the relation between the extraction kinetics parameters and the operating conditions.
+This study investigates the extraction of essential oils from chamomile flowers using supercritical carbon dioxide as a solvent in a semi-batch mode.
+The process is described by a mathematical model incorporating empirical correlations.
+The goal of this work is to \underline{improve the precision of the} \underline{model parameters by designing a new experiment} and validating the model against it.
 \end{tcolorbox}
@@
 
-\vspace{0.5cm}
+	The process is described by a first-principle distributed-parameter model [1,2] with a set of empirical correlations [2]. The model assumptions are \\
 
@@
 
-\begin{minipage}[h!]{0.5\linewidth}
+\begin{minipage}[h!]{0.33\linewidth}
 	\begin{align*}
@@
 		\phi~~ &- \text{Void fraction}\\
+		D_e^M &- \text{Axial mass diffusivity}\\
 		D_i^R &- \text{Internal mass diffusivity}
@@
 %
-\begin{minipage}[h!]{0.5\linewidth}
+\begin{minipage}[h!]{0.33\linewidth}
 	\begin{align*}
-		D_e^M &- \text{Axial mass diffusivity}\\
 		\mu~ &- \text{Particle shape coefficient}\\
@@
 		T~ &- \text{Temperature}\\
-		F~ &- \text{Mass flow rate}
+		F~ &- \text{Mass flow rate} \\
+		\Sigma~ &- \text{Covariance matrix} \\
+		\Theta~ &- \text{Vector of parameters}
 	\end{align*}
@@
 
-\underline{Fisher information $\mathcal{F}$ measures the amount of information} that an observable random variable carries about an unknown parameter of a distribution that models the random variable.
-$\mathcal{F}$ is defined as Hessian of the likelihood function with respect to parameters $\Theta$, given the covariance matrix $\Sigma$.
-%Based on the Cramer-Rao inequality, $\mathcal{F}$ can used to calculate the covariance matrices associated with maximum-likelihood estimates.
+\underline{Fisher information $\mathcal{F}$ (Hessian of the likelihood function) measurs the amount of information} observable random variables carry about a parameters of a distribution that models these variables[3]:
 
@@
 
-The optimal design of experiments is a concept that refers to planning an experiment, which allow parameters to be estimated without bias and with minimum variance.
-The D-optimality criterion is selected as the objective function, which leads to \underline{the minimisation of the volume} \underline{of the ellipsoidal confidence region of parameter estimates} given the experimental condition $\Xi$.
+%The optimal design of experiments involves planning an experiment in such a way that parameters can be estimated without bias and with minimal variance. 
+The D-optimality criterion is chosen as the objective function, aiming to \underline{minimize the volume} \underline{of the ellipsoidal confidence region of parameter estimates} under the experimental conditions $\Xi$.
 
@@
 
-\underline{This work aims to design a dynamic experiment to improve precision of correlation for $D_i^R$}.
-The system is assumed to run for 300 min, with sampling time of 10 min.
-The set of decision variables consists of $T^{in}$ and $F$, and each of them is manipulated every 15 min.
-Each of five analysed cases assumes that P is kept constant at 100, 125, 150, 175 and 200 bar, respectively.
+This work aims \underline{to improve the precision of the correlation for $D_i^R$} by designing an experiment with dynamically changing operating conditions (\underline{$F$ and $T^{in}$)}. \\
+
+The method of lines is employed to transform the process model equations into a set of ODEs.
+The first- and second-order derivatives are approximated using the backward and central difference schemes, respectively.
+The time integral and all time-dependent functions are discretized using the single-shooting approach with piecewise-constant controls to obtain a static non-linear program.
 \end{tcolorbox}
+
 %----------------------------------------------------------------------------------------
@@
 
-	To identify the global solution, the optimization problem is solved multiple times, each starting from a random initial solution.
-Figure 2 compares the initial and final values of the cost function across multiple optimization runs for different cases of pressure value.
+	The system operates for 300 minutes, with a sampling interval of 10 minutes and decision variables adjusted every 15 minutes.
+Each of the five analysed cases assumes a constant pressure, set at 100, 125, 150, 175, and 200 bar.
+To identify the global solution, the optimization problem is solved multiple times, each starting from a random initial solution sampled from a uniform distribution.
+%Figure 2 compares the initial and final values of the cost function across multiple optimization runs for different cases of pressure value.
 
@@
 	\begin{itemize}
-		\item The optimal profiles of controls are similar for all the cases
-		\item Low values of the objective are obtained at pressures close to supercritical point, where the variation in the inlet temperature cause large deviation in the physical properties of CO$_2$ and Reynolds number
-		\item The mass flow rate is used as main control variable, which suggest that the system is more sensitive to the mass flow rate than the inlet temperature
+		\item The optimal control profiles are similar across all cases.
+		\item Low objective values are achieved at pressures near the supercritical point, where variations in the inlet temperature cause significant deviations in the physical properties of CO$_2$ and consequently in the Reynolds number
+		\item The mass flow rate is the primary control variable, indicating that the system is more sensitive to mass flow rate changes than to inlet temperature variations.
 	\end{itemize}
@@
 
-\section*{Forthcoming Research}
+%\section*{Forthcoming Research}
 
-Vivamus molestie, risus tempor vehicula mattis, libero arcu volutpat purus, sed blandit sem nibh eget turpis.
+%Vivamus molestie, risus tempor vehicula mattis, libero arcu volutpat purus, sed blandit sem nibh eget turpis.
 Maecenas rutrum dui blandit lorem vulputate gravida.
@@
 %----------------------------------------------------------------------------------------
-
-\nocite{*} % Print all references regardless of whether they were cited in the poster or not
-\bibliographystyle{plain} % Plain referencing style
-\bibliography{sample} % Use the example bibliography file sample.bib
-
+\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
+	{\LARGE References\\}
+	\begin{enumerate}[label={[\arabic*]}]
+		\item E. Reverchon. Mathematical modeling of supercritical extraction of sage oil. AIChE Journal, 42(6):1765–1771, June 1996. ISSN 1547-5905. doi: 10.1002/aic.690420627.
+		\item O. Sliczniuk and P. Oinas. Supercritical fluid extraction of essential oil from chamomile flowers: modelling and parameter estimation. CJCE Journal. June 2024. Under review.
+		\item E. Walter and L. Pronzato. Identification of parametric models from experimental data. Communications and control engineering. Springer, London, 2010. ISBN 9781849969963
+	\end{enumerate}
+\end{tcolorbox}
 %----------------------------------------------------------------------------------------
@@
 
-\section*{Acknowledgements}
+%\section*{Acknowledgements}
 
-Etiam fermentum, arcu ut gravida fringilla, dolor arcu laoreet justo, ut imperdiet urna arcu a arcu. Donec nec ante a dui tempus consectetur. Cras nisi turpis, dapibus sit amet mattis sed, laoreet.
+%Etiam fermentum, arcu ut gravida fringilla, dolor arcu laoreet justo, ut imperdiet urna arcu a arcu. Donec nec ante a dui tempus consectetur. Cras nisi turpis, dapibus sit amet mattis sed, laoreet.
 

### 2024-08-06 SFE_poster_DOE/CHISA_2024_Sliczniuk.tex
06.08

--- 2024-08-05 SFE_poster_DOE/conference_poster_6.tex
@@
 \veryHuge \color{NavyBlue} \textbf{Optimal design of experiment:} \color{Black}\\ % Title
-\Huge\textit{supercritical fluid extraction case}\\[2cm] % Subtitle
-\huge \textbf{Oliwer Sliczniuk, Pekka Oinas}\\[0.5cm] % Author(s)
+\Huge\textit{supercritical fluid extraction case}\\[1cm] % Subtitle
+\huge \textbf{Oliwer Sliczniuk, Pekka Oinas}\\%[0.5cm] % Author(s)
 \huge School of Chemical Engineering, Aalto University, Finland\\[0.4cm] % University/organization
@@
 \begin{minipage}[b]{0.25\linewidth}
-\includegraphics[width=15cm]{Aalto_University_logo.png}\\ \\
+\includegraphics[width=12cm]{Aalto_University_logo.png}\\ \\
 \end{minipage}
 
-%\vspace{0.5cm} % A bit of extra whitespace between the header and poster content
+\vspace{-2cm} % A bit of extra whitespace between the header and poster content
 \noindent\rule{\textwidth}{3pt}
@@
 
-\begin{minipage}[b]{0.5\linewidth}
+\begin{minipage}[b]{0.1\linewidth}
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.45\linewidth}
 	\begin{itemize}
@@
 \hfill
-\begin{minipage}[b]{0.5\linewidth}
+\begin{minipage}[b]{0.45\linewidth}
 	\begin{itemize}
@@
 
-\begin{minipage}[h!]{0.33\linewidth}
+\begin{center}\vspace{0.5cm}
+	\includegraphics[width=0.49\linewidth]{Di_Re_F.png}
+	\hfill
+	\includegraphics[width=0.49\linewidth]{Gamma_Re_F.png}
+	\captionof{figure}{Empirical correlations}
+\end{center}%\vspace{1cm}
+
+\end{tcolorbox}
+
+%------------------------------------------------
+%\vspace{1cm}
+%\section*{Model-based optimal design of experiment}
+\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
+	{\LARGE Model-based optimal design of experiment\\}
+
+%\underline{Fisher information $\mathcal{F}$ (Hessian of the likelihood function) measurs the amount of information} observable random variables carry about a parameters of a distribution that models these variables[3]:
+
+\begin{equation*}
+	%\Sigma^{-1} \geq
+	\underbrace{\mathcal{F}(t,\Theta; \Xi)}_{\text{Fisher Information}} = \frac{\partial y(t, \Theta; \Xi)}{\partial \Theta} \Sigma \frac{\partial y(t, \Theta; \Xi)}{\partial \Theta^\top}
+\end{equation*}
+
+%The optimal design of experiments involves planning an experiment in such a way that parameters can be estimated without bias and with minimal variance. 
+The D-optimality criterion is chosen as the objective function, aiming to \underline{minimize the volume} \underline{of the ellipsoidal confidence region of parameter estimates} under the experimental conditions $\Xi$ [3].
+
+\begin{equation*}
+	\begin{aligned} 
+		&\Xi^* &= \arg &\min_{ T^{in},~F\in~\Xi}\quad\int_{t_0 = 0 \text{min}}^{t_f=300 \text{min}} - \ln \det \mathcal{F}(t,\Theta; \Xi)~dt  \\
+		&\text{subject to}
+		& \dot{x} = ~&G~~(x,t,\Theta;\Xi) \\
+		&& T^{0} = ~&T^{in}(t=0) \\
+		&& 30^\circ C \leq ~&T^{in}(t) ~ \leq 40^\circ C \\
+		&& 3.33 \cdot 10^{-5}~\text{kg/s} \leq ~&F~~(t)~ \leq 6.67 \cdot 10^{-5}~\text{kg/s}\\
+		&& 100~\text{bar} \leq ~&P~~(t)~ \leq 200~\text{bar} \\
+	\end{aligned}
+\end{equation*}
+
+The aim is \underline{to improve the precision of the correlation for $D_i^R$} by designing an experiment with dynamically changing operating conditions for five cases of constant pressure: 100, 125, 150, 175, and 200 bar.
+The yield is measured every 10 min and decision variables are adjusted every 15 min.
+\end{tcolorbox}
+
+\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
+	{\LARGE Numerics\\}
+
+The method of lines is employed to transform the process model equations into a set of ODEs.
+The first- and second-order derivatives are approximated using the backward and central difference schemes, respectively.
+The time integral and all time-dependent functions are discretized using the single-shooting approach with piecewise-constant controls to obtain a static non-linear program.
+\end{tcolorbox}
+
+\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
+	{\LARGE Legend\\}
+	\begin{minipage}[b]{0.05\linewidth}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[h!]{0.475\linewidth}
 		\begin{align*}
@@
 	%
-\begin{minipage}[h!]{0.33\linewidth}
+	\begin{minipage}[h!]{0.475\linewidth}
 		\begin{align*}
@@
 			T~ &- \text{Temperature}\\
+			T^{in} &- \text{Inlet temperature}\\
 			F~ &- \text{Mass flow rate} \\
@@
 	\end{minipage}
-
-\begin{center}\vspace{0.5cm}
-	\includegraphics[width=0.49\linewidth]{Di_Re_F_1.png}
-	\includegraphics[width=0.49\linewidth]{Gamma_Re_F_1.png}
-	\captionof{figure}{Empirical correlations}
-\end{center}%\vspace{1cm}
-
-\end{tcolorbox}
-
-\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
-%------------------------------------------------
-%\vspace{1cm}
-%\section*{Model-based optimal design of experiment}
-\begin{tcolorbox}[width=\linewidth, boxrule=0mm, sharp corners=all, colback=white]
-	{\LARGE Model-based optimal design of experiment\\}
-\end{tcolorbox}
-
-\underline{Fisher information $\mathcal{F}$ (Hessian of the likelihood function) measurs the amount of information} observable random variables carry about a parameters of a distribution that models these variables[3]:
-
-\begin{equation*}
-	%\Sigma^{-1} \geq
-	\mathcal{F}(t,\Theta; \Xi) = \frac{\partial y(t, \Theta; \Xi)}{\partial \Theta} \Sigma \frac{\partial y(t, \Theta; \Xi)}{\partial \Theta^\top}
-\end{equation*}
-
-%The optimal design of experiments involves planning an experiment in such a way that parameters can be estimated without bias and with minimal variance. 
-The D-optimality criterion is chosen as the objective function, aiming to \underline{minimize the volume} \underline{of the ellipsoidal confidence region of parameter estimates} under the experimental conditions $\Xi$.
-
-\begin{equation*}
-	\begin{aligned} 
-		&\Xi^* &= \arg &\min_{ T^{in},~F\in~\Xi}\quad\int_{t_0}^{t_f} - \ln \det \mathcal{F}(t,\Theta; \Xi)~dt  \\
-		&\text{subject to}
-		& \dot{x} = ~&G~~(x,t,\Theta;\Xi) \\
-		&& T^{0} = ~&T^{in}(t=0) \\
-		&& 30^\circ C \leq ~&T^{in}(t) ~ \leq 40^\circ C \\
-		&& 3.33 \cdot 10^{-5}~\text{kg/s} \leq ~&F~~(t)~ \leq 6.67 \cdot 10^{-5}~\text{kg/s}\\
-		&& 100~\text{bar} \leq ~&P~~(t)~ \leq 200~\text{bar} \\
-	\end{aligned}
-\end{equation*}
-
-This work aims \underline{to improve the precision of the correlation for $D_i^R$} by designing an experiment with dynamically changing operating conditions (\underline{$F$ and $T^{in}$)}. \\
-
-The method of lines is employed to transform the process model equations into a set of ODEs.
-The first- and second-order derivatives are approximated using the backward and central difference schemes, respectively.
-The time integral and all time-dependent functions are discretized using the single-shooting approach with piecewise-constant controls to obtain a static non-linear program.
 \end{tcolorbox}
@@
 
-	The system operates for 300 minutes, with a sampling interval of 10 minutes and decision variables adjusted every 15 minutes.
-Each of the five analysed cases assumes a constant pressure, set at 100, 125, 150, 175, and 200 bar.
 	To identify the global solution, the optimization problem is solved multiple times, each starting from a random initial solution sampled from a uniform distribution.
@@
 
-	The optimal profiles of the inlet temperature and flow rates for each case are showed in Figure 3
+	The optimal profiles of the controls and the yield curves are showed below
 
 	\begin{center}\vspace{0.5cm}
-		\includegraphics[width=\linewidth]{Profiles.png}
+		\includegraphics[width=0.92\linewidth]{Profiles_all.png}
 		\captionof{figure}{Optimal profiles}
@@
 	\begin{itemize}
-		\item The optimal control profiles are similar across all cases.
-		\item Low objective values are achieved at pressures near the supercritical point, where variations in the inlet temperature cause significant deviations in the physical properties of CO$_2$ and consequently in the Reynolds number
-		\item The mass flow rate is the primary control variable, indicating that the system is more sensitive to mass flow rate changes than to inlet temperature variations.
+		\item The lowest values of the cost function are achieved near the supercritical point, where variations in the inlet temperature cause significant deviations in the physical properties of CO$_2$ and $Re$
+		\item The optimal profiles of the controls are similar across all cases
+		\item The mass flow rate is the primary control variable, indicating that the system is more sensitive to mass flow rate changes than to inlet temperature variations
+		\item The optimal yield profiles are characterized by waving behaviour 
+		\item Experiments which result in the highest yields are not necessary the most informative
 	\end{itemize}

### 2024-08-06 SFE_DOE_Chamomile/Case_1_T_F/Yield_Plot.m

@@ -1,0 +1,191 @@
+function [Yield] = Yield_Plot(feedPress, T0homog, Flow)
+    % FeedPress[bar]               - one element vector
+    % T0homog[kg], Flow[kg/s*1e5]   - vectors of OP_change size
+    
+    %%
+    %addpath('casadi_folder')
+    %addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+    addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+    import casadi.*
+        
+    %% Load paramters
+    Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+    Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+    
+    m_total                 = 3.0;
+    
+    % Bed geometry
+    before                  = 0.04;                                             % Precentage of length before which is empty
+    bed                     = 0.92;                                              % Percentage of length occupied by fixed bed
+    
+    % Set time of the simulation
+    PreparationTime         = 0;
+    ExtractionTime          = 300;
+    timeStep                = 5;                                                 % Minutes
+    SamplingTime            = 10;                                                % Minutes
+    OP_change_Time          = 15;                                                % Minutes
+    
+    simulationTime          = PreparationTime + ExtractionTime;
+    
+    timeStep_in_sec         = timeStep * 60;                                    % Seconds
+    Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+    Time                    = [0 Time_in_sec/60];                               % Minutes
+    
+    N_Time                  = length(Time_in_sec);
+    SAMPLE                  = SamplingTime:SamplingTime:ExtractionTime;
+    OP_change               = OP_change_Time:OP_change_Time:ExtractionTime;
+    
+    % Check if the number of data points is the same for both the dataset and the simulation
+    N_Sample                = [];
+    for i = 1:numel(SAMPLE)
+        N_Sample            = [N_Sample ; find(round(Time,3) == round(SAMPLE(i))) ];
+    end
+    if numel(N_Sample) ~= numel(SAMPLE)
+        keyboard
+    end
+    
+    %% Specify parameters to estimate
+    nstages                 = Parameters{1};
+    
[…]

### 2024-08-06 SFE_DOE_Chamomile/Case_1_T_F/main_Results.m

@@ -21,10 +21,10 @@ A                       = pi *      r^2;                                    % Ex
 
 %--------------------------------------------------------------------
 
-N_exp    = 50;
-COLORS = ['b','r','k','m','g'];
-COST_I   = []; COST_F   = []; GROUP    = [];
-PP = [100, 125, 150, 175, 200];
+N_exp                   = 50;
+COLORS                  = ['b','r','k','m','g'];
+COST_I   = []; COST_F   = []; GROUP    = []; Yield      = [];
+PP                      = [100, 125, 150, 175, 200];
 %hold on
 for ii = 1:numel(PP)
     PRES = PP(ii);
@@ -46,43 +46,45 @@ for ii = 1:numel(PP)
     % Plots of controls
     ind      = find( FinaCost == min(FinaCost));
     
-    subplot(1,2,1)
+    %{\
+    subplot(3,1,1)
     hold on
     stairs(Time, [TempCont(:, ind); TempCont(end,ind)]-273, 'LineWidth', 2 ,'Color',COLORS(ii));
     hold off
-    ylabel('Temperature [$^\circ$C]')
+    ylabel('$T^{in}~^\circ$C')
     xlabel('Time [min]')
-    legend('P = 100 bar','P = 125 bar','P = 150 bar','P = 175 bar','P = 200 bar', 'Location','best','NumColumns',5)
-    legend box off
-    axis square
+    %legend('P = 100 bar','P = 125 bar','P = 150 bar','P = 175 bar','P = 200 bar', 'Location','best','NumColumns',5)
+    %legend box off
+    %axis square
     set(gca,'FontSize',16)
     
-    subplot(1,2,2)
+    subplot(3,1,2)
     hold on
     stairs(Time, [FlowCont(:, ind); FlowCont(end,ind)], 'LineWidth', 2, 'Color',COLORS(ii));
     hold off
-    ylabel('Mass flow rate $\times 10^{-5}$ [$kg/s$]')
+    ylabel('$F\cdot 10^{-5}$ $kg/s$')
     xlabel('Time [min]')
-    axis square
+    %axis square
     set(gca,'FontSize',16)
+    %}
+
+    Yield = [Yield; Yield_Plot(PRES,TempCont(:, ind),FlowCont(:, ind))];
+
+    Time     = linspace(0,300,size(Yield,2));
+
+    subplot(3,1,3)
+    hold on
[…]

### 2024-08-06 SFE_DOE_Chamomile/Case_1_T_F/modelSFE.m

@@ -1,0 +1,140 @@
+function xdot = modelSFE(x, p, mask, dt)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% Load Paramters
+    T_u           =     p{1};
+    P_u           =     p{2};
+    F_u           =     p{3} * 10^(-5);
+
+    parameters    =     p(4:end);
+
+    %nstages       =     parameters{1};
+    C0solid       =     parameters{2};     % Extractor initial concentration of extract
+    r             =     parameters{3};     % Extractor radius (m)
+    epsi          =     parameters{4};     % Void bed fraction
+    dp            =     parameters{5};     % Diameter of the particle (m)
+    L             =     parameters{6};     % Length of the extractor (m)
+    rho_s         =     parameters{7};     %
+    mi            =     parameters{9};
+
+    km            =     parameters{8} ;
+    %Di            =     parameters{44}* 1e-13;      
+    %Dx            =     parameters{45}* 1e-12;      
+    Dx            =     1e-15;      
+    %gamma         =     parameters{46};
+
+    nstages_index =     numel(mask);
+    
+    %% Properties of the bed
+    A             =     pi*r^2 ;       % Cross-section of the extractor (m^2)
+    rp            =     dp / 2;
+    lp2           =     (rp / 3)^2;
+
+    %% States
+    FLUID         =     x(0*nstages_index+1:1*nstages_index);
+    SOLID         =     x(1*nstages_index+1:2*nstages_index);
+    ENTHALPY_RHO  =     x(2*nstages_index+1:3*nstages_index);
+    PRESSURE      =     x(3*nstages_index+1);
+
+    TEMP          =     Reconstruct_T_from_enthalpy(ENTHALPY_RHO, PRESSURE, parameters);
+      
+    %Properties of the fluid in the extractor
+    Z             =     Compressibility(TEMP, PRESSURE,    parameters);
+
+    RHO           =     rhoPB_Comp(     TEMP, PRESSURE, Z, parameters);   
+    MU            =     Viscosity(TEMP,RHO);
+
+    %VELOCITY      =     Velocity(F_u, mean([RHO(2:25:end)]), parameters);
+    VELOCITY      =     Velocity(F_u, RHO(2), parameters);
+
[…]

### 2024-08-06 SFE_DOE_Chamomile/Fit_Correlations.m

@@ -3,8 +3,8 @@ delete(gcp('nocreate'));
 
 %%
 AA = xlsread('Regression.xlsx');
-DI = [0.701472275, 1.331443055, 2.239307889, 2.711813187, 1.32629228, 1.485504345, 1.73827467, 2.59502961, 0.48656241, 1.363499511, 0.72227, 0.756214019];
-GG = [4.274825704, 2.189390368, 2.552240039, 1.365163176, 2.830760407, 2.573487374, 1.642279591, 1.906200052, 4.287215235, 2.723682117, 3.82240, 3.35589348];
+DI = [0.71383013	1.076801997	2.179470155	2.475532632	1.390707877	1.336111172	1.882954204	2.457886055	0.564935512	1.542106938	0.835725102	0.87349666];
+GG = [4.229739602	3.091520556	2.359538225	1.132795818	2.204975712	2.739220425	1.868538631	1.69935869	3.452308202	1.995905641	3.012676539	2.596460037];
 RE = [0.4632, 0.3783, 0.3029, 0.2619, 0.3579, 0.3140, 0.2635, 0.2323, 0.1787, 0.1160, 0.1889, 0.1512];
 TT = [313, 313, 313, 313, 303, 303, 303, 303, 303, 303, 313, 313];
 Tr = TT ./ 304;
@@ -80,72 +80,50 @@ ylabel('$D_i^R \gamma(\Upsilon, C_s) [m^2/s] $')
 xlabel('Normalized $C_s [kg/m^3]$')
 set(gca,'FontSize',42)
 %exportgraphics(figure(1), ['Gamma_function.png'], "Resolution",300);
-%close all
+close all
 %}
 
 %% Fit a surface in RE and F space
-
+%{\
 figure()
-[ml3, sf3] = fit([RHO', FF'],DI','poly11');
-h3 = plot(ml3, [RHO', FF'],DI');
+tiledlayout(1,2)
+
+pbaspect([2 1 1])
+[ml3, sf3] = fit([RE', FF'],DI','poly11');
+h3 = plot(ml3, [RE', FF'],DI');
 set(h3,'linestyle','none');
 alpha(.5)
 
 p3 = coeffvalues(ml3);
[…]

### 2024-09-13 Sections/Optimal_design_of_experiment.tex
13.09

@@
 	Details on the process model can be found in [article 1].
-The model's empirical correlations are derived based on laboratory experiments conducted under various constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The model's empirical correlations are derived based on laboratory experiments conducted under various but constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
 This study employs a model-based design of experiments technique to design an experiment with dynamically changing conditions to improve the precision of the correlation for $D_i$.
@@
 The sampling time is set to 5 minutes, and the total extraction time is 300 minutes.
-The standard deviation $\sigma^2$ was estimated to be 0.12.
+The standard deviation $\sigma^2$ was estimated to be 0.10.
 The analysed correlations consist of two independent variables: Reynolds number and mass flow rate.
 The Reynolds number is a function of fluid thermodynamic properties and velocity, and the fluid density can be affected by temperature or pressure changes.
-In this work, both cases are solved and compared.
+In this work, the decision variables are the inlet temperature $(T^{in})$ and mass flow rate $(F)$, while the pressure is assumed to remain constant.
+The initial state is considered isothermal, so $T^0 = T^{in}(t=0)$.
+The optimal design of experiment problem is solved for multiple values of pressure, namely 100, 125, 150, 175 and 200 bar.
+%The problem formulation is given by Equation \ref{EQ:Formulation_1}.
 
-	In the first case, the decision variables are the inlet temperature $(T^{in})$ and mass flow rate $(F)$.
-Throughout the experiment, the pressure is assumed to remain constant at 150 bar (the middle of the validated range).
-The initial state is considered isothermal, so $T^0 = T^{in}(t=0)$.
-The problem formulation for Case 1 is given by Equation \ref{EQ:Formulation_1}.
+	\begin{comment}
 
@@
 			&& T^{0} &= T^{in}(t=0) \\
-			&& P(t) &= 150~\text{bar} \\
+			&& P(t) & \in \{100, 125, 150, 175, 200\}~\text{bar} \\
 			%&& \dot{y} = g(x(t)) \\
@@
 
-	In the second case, the pressure and mass flow rate are treated as decision variables, while the inlet temperature is kept constant at $35^\circ C$.
-Similar to the first case, the extractor is assumed to be isothermal at the beginning of the operation.
-Unlike the previous case, changes in pressure affect the temperature inside the extractor.
-Any temperature deviation caused by pressure changes will eventually be mitigated by the inflow of fresh fluid at the constant temperature of $35^\circ C$.
-The problem formulation for Case 2 is given by Equation \ref{EQ:Formulation_2}.
+	\end{comment}
+
+	%The analysed correlation depends on the mass flow-rate and the Reynolds number, which suggest that using a mass-flow rate as an decision variable allow to investigate the whole correlation.
+Following the general formulation of many control problems such as Linear Quadratic Regulator, a quadratic penalty term is introduced to the cost function to avoid overuse of the mass-flow rate.
+The penalty term increase the value of the objective function in case of rapid changes of the mass flow-rate.
+
+	In a real system, the mass flow rate and inlet temperature cannot be changed instantaneously, as they depend on the dynamics of the pump and heat exchanger, respectively.
+To prevent bang-bang-like control between the lower and upper bounds of the decision variables, a penalty term is introduced.
+Similar to many control problems, such as the Linear Quadratic Regulator, a quadratic penalty term is added to the cost function.
+This penalty increases the cost function value when there are rapid changes in the decision variables.
+The matrix $R$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$.
+The problem formulation is given by Equation \ref{EQ:Formulation_2}.
 
@@
 			\begin{aligned} 
-				&\Xi^* &= \arg &\min_{ P, F \in \Xi} \int_{t_0}^{t_f} - \ln j_D(\Xi,\dot{x}) dt  \\
+				&\Xi^* &= \arg &\min_{ T^{in}, F \in \Xi} \int_{t_0}^{t_f} - \ln j_D(\Xi,\dot{x}) + u(t) R u(t)^\top dt  \\
 				&\text{subject to}
@@
 				&& t_f&=300~\text{min} \\
-				&& T^{0} &= T^{in}(t) = 35^\circ C \\
-				%&& P(t) &= 150~\text{bar} \\
+				&& T^{0} &= T^{in}(t=0) \\
+				&& P(t) & \in \{100, 125, 150, 175, 200\}~\text{bar} \\
+				&& R &= \begin{bmatrix}
+						10^{-1} & 0  \\
+						0 & 10^{-2}
+					\end{bmatrix}  \\
+				&& u(t) &= \begin{bmatrix}
+					\frac{dF(t)}{dt}  \\
+					\frac{dT^{in}(t)}{dt} 
+				\end{bmatrix}  \\
 				%&& \dot{y} = g(x(t)) \\
-				&& 100^\circ C \leq &P(t) \leq 200^\circ C \\
+				&& 30^\circ C \leq &T^{in}(t) \leq 40^\circ C \\
 				&& 3.33 \cdot 10^{-5} \leq &F(t) \leq 6.67 \cdot 10^{-5}

### 2024-09-13 SFE_DOE_Chamomile/main_DOE_Chamomile.m

@@ -7,14 +7,14 @@ addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matl
 import casadi.*
 
 %% Create the solver
-Iteration_max               = 500;                                          % Maximum number of iterations for optimzer
-Time_max                    = 24;                                           % Maximum time of optimization in [h]
+Iteration_max               = 2;                                         % Maximum number of iterations for optimzer
+Time_max                    = 15;                                           % Maximum time of optimization in [h]
 
 nlp_opts                    = struct;
 nlp_opts.ipopt.max_iter     = Iteration_max;
 nlp_opts.ipopt.max_cpu_time = Time_max*3600;
-%nlp_opts.ipopt.hessian_approximation ='limited-memory';
-%nlp_opts.ipopt.acceptable_tol  = 1e-4;
+nlp_opts.ipopt.hessian_approximation ='limited-memory';
+%nlp_opts.ipopt.acceptable_tol  = 1e-2;
 %nlp_opts.ipopt.acceptable_iter = 5;
 
 %%
@@ -36,8 +36,8 @@ bed                     = 0.92;                                             % Pe
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 300;
-timeStep                = 1;                                               % Minutes
+ExtractionTime          = 600;
+timeStep                = 5;                                               % Minutes
 OP_change_Time          = 10;                                              % Minutes
 SAMPLING_TIME           = 5;
 
@@ -140,7 +140,7 @@ C0fluid                 = m_fluid * 1e-3 ./ V_fluid';
 
 %% Set operating conditions
 T0homog                 = 35+273;                                           % K
-feedPress               = 150;                                              % MPa -> bar
+feedPress               = 100;                                              % MPa -> bar
 Flow                    = 5;                                                % kg/s
 
[…]

### 2024-09-13 SFE_DOE_Chamomile/modelSFE.m

@@ -8,7 +8,7 @@ function xdot = modelSFE(x, p, mask, dt)
     %% Load Paramters
     T_u           =     p{1};
     P_u           =     p{2};
-    F_u           =     p{3} * 10^(-5);
+    F_u           =     p{3};
 
     parameters    =     p(4:end);
 
@@ -51,7 +51,7 @@ function xdot = modelSFE(x, p, mask, dt)
     %VELOCITY      =     Velocity(F_u, mean([RHO(2:25:end)]), parameters);
     VELOCITY      =     Velocity(F_u, RHO(2), parameters);
 
-    RE            =     dp .* RHO .* VELOCITY ./ MU;
+    RE            =     dp .* RHO .* VELOCITY ./ MU .* 1.3;
     
     %% Thermal Properties
     CP            =     SpecificHeatComp(TEMP, PRESSURE, Z, RHO,                 parameters);            % [kJ/kg/K]

### 2024-09-19 Article_Design_of_Experiment-Chamomile.tex
19.09

@@
 \usepackage{subcaption}
+
+\usepackage{nomencl}
+\makenomenclature
+
+\usepackage{etoolbox}
+\renewcommand\nomgroup[1]{%
+	\item[\bfseries
+	\ifstrequal{#1}{A}{Latin symbols}{%
+		\ifstrequal{#1}{B}{Greek symbols}{%
+			\ifstrequal{#1}{C}{Abberivations}{
+	}}}%
+	]}
 
@@
 The empirical correlations used in the model are based on the set of laboratory experiments performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-The model-based design of the experiments technique is applied in this work to improve the precision of the correlation parameters.
-The mass flow rate and the inlet temperature are used as decision variables to minimizing the volume of the confidence
-ellipsoid. As a result, the optimal control problem is numerically solved to obtain the controls, which maximises the Fisher information contained in the yield curve.
+A model-based design of experiments with D-optimality criterion is applied to improve the precision of the correlation parameters by designing a new dynamic experiment.
+The mass flow rate and inlet temperature are used as decision variables to maximize the Fisher Information embedded in the yield curve with respect to the empirical correlations.
 
@@
 \section{Conclusions} \label{CH: Conclusion}
+This paper introduces the D-optimal experimental design (D-OED) as a model-based method for finding an experimental procedure in chemical engineering problems.
+D-OED forms the objective function, which can be interpreted as minimising the volume of uncertainty ellipsoid.
+Compared to the classical formulation of D-OED, a penalty term was introduced to the cost function to prevent infeasibly rapid changes in operating conditions or bang-bang type control.
+The method is demonstrated through a case study on supercritical extraction.
+This work aims to design an experiment to improve the precision of the correlation for $D_i$.
+While the original experiments were conducted under constant operating conditions, this work looks for an experimental procedure with dynamically changing operating conditions.
+In such a case, the D-OED solution can also be used for model validation.
+
+The analysis was repeated for multiple pressure values, and the obtained optimal profiles of inlet temperature and mass flow rate were similar across all cases.
+The resulting yield curves exhibit wavy patterns due to the relationship between the Hessian and the curvature of a multi-variable function.
+The analysis of the yield curves and scatter plots reveals that applying the same experimental strategy at different operating conditions results in varying amounts of information being collected.
+Consequently, it is concluded that the operating conditions should always be carefully chosen to conduct the most informative experiments.
+This is because the physical properties of CO$_2$ vary less at pressures far from the critical point, meaning that the same set of controls has less impact on the system at high pressures than at low pressures.
 
@@
 
+\newpage
+
+\nomenclature[A]{\(P\)}{Pressure}
+\nomenclature[A]{\(T\)}{Temperature}
+\nomenclature[A]{\(T^{in}\)}{Inlet temperature}
+\nomenclature[A]{\(T^{out}\)}{Outlet temperature}
+\nomenclature[A]{\(F\)}{Mass flow rate}
+\nomenclature[A]{\(u\)}{Superfical velocity}
+\nomenclature[A]{\(v\)}{Linear velocity}
+\nomenclature[A]{\(z\)}{Spatial direction}
+\nomenclature[A]{\(e\)}{Internal energy}
+\nomenclature[A]{\(e^y\)}{Output error}
+\nomenclature[A]{\(h\)}{Enthalpy}
+\nomenclature[A]{\(t\)}{Time}
+\nomenclature[A]{\(t_f\)}{Total extraction time}
+\nomenclature[A]{\(t_0\)}{Inital extraction time}
+\nomenclature[A]{\(A\)}{Total cross section of the bed}
+\nomenclature[A]{\(A_f\)}{Cross section of the bed accupied by the fluid}
+\nomenclature[A]{\(c_f\)}{Concentration of solute in fluid phase}
+\nomenclature[A]{\(c_{f0}\)}{Inital concentration of solute in fluid phase}
+\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface}
+\nomenclature[A]{\(c_s\)}{Concentration of solute in solid phase}
+\nomenclature[A]{\(c_{s0}\)}{Inital concentration of solute in solid phase}
+\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface}
+\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore}
+\nomenclature[A]{\(c_{pf}\)}{Concentration of solute in the pore opening}
+\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficeint}
+\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term}
+\nomenclature[A]{\(L\)}{Length of fixed bed}
+\nomenclature[A]{\(j\)}{Objective function}
+\nomenclature[A]{\(j_{ml}\)}{Maximum Likelihood}
+\nomenclature[A]{\(S\)}{Sensitivity equations}
+\nomenclature[A]{\(Q\)}{Weighting matrix}
+\nomenclature[A]{\(R\)}{Control cost matrix}
+%\nomenclature[A]{\(\textbf{G}\)}{Augumented system}
+%\nomenclature[A]{\(\dot{S}\)}{Time derivative of sensitivity equations}
+%\nomenclature[A]{\(\bar{S}\)}{Sensitivity matrix}
+%\nomenclature[A]{\(\bar{J}_x\)}{Jacobian matrix with respect to the state space}
+%\nomenclature[A]{\(\bar{J}_\Theta\)}{Jacobian matrix with respect to the paramters}
+%\nomenclature[A]{\(\mathcal{L}\)}{Log-likelihood function}
+\nomenclature[A]{\(l\)}{Characterisitic diemsinon of particles}
+\nomenclature[A]{\(D_i\)}{Interanl diffusion coefficient}
+\nomenclature[A]{\(D_i^R\)}{Reference value of interanl diffusion coefficient}
+\nomenclature[A]{\(r\)}{Particle radius}
+\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient}
+\nomenclature[A]{\(k_m\)}{Mass partition coefficient}
+\nomenclature[A]{\(y\)}{Extraction yield}
+\nomenclature[A]{\(Y\)}{Yield measurment}
+\nomenclature[A]{\(x\)}{State vector}
+\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
+\nomenclature[A]{\(p\)}{Probaility disribution model}
+\nomenclature[A]{\(R_e\)}{Reynolds number}
+\nomenclature[A]{\(\mathcal{F}\)}{Fisher information}
+
+\nomenclature[B]{\(\rho_f\)}{Fluid density}
+\nomenclature[B]{\(\Phi\)}{Bed porosity}
+\nomenclature[B]{\(\rho_s\)}{Bulk density of solid}
+\nomenclature[B]{\(\mu\)}{Sphericity coefficient}
+\nomenclature[B]{\(\pi\)}{Probability desnsity}
+\nomenclature[B]{\(\gamma\)}{Decaying function}
+\nomenclature[B]{\(\Upsilon\)}{Decay coefficient}
+\nomenclature[B]{\(\Theta\)}{Paramter space}
+\nomenclature[B]{\(\theta\)}{vector of unknown parameters}
+\nomenclature[B]{\(\epsilon\)}{Unobervable error}
+\nomenclature[B]{\(\sigma\)}{Standard deviation}
+\nomenclature[B]{\(\Sigma\)}{Covariance matrix}
+\nomenclature[B]{\(\xi\)}{Vector of experimental condtions}
+\nomenclature[B]{\(\Xi\)}{Matrix of experimental condtions}
+
+\nomenclature[C]{BIC}{Broke-and-Intact Cell model}
+%\nomenclature[C]{MLE}{Maximum Likelihood Estimation}
+\nomenclature[C]{SFE}{Supercritical Fluid Extraction}
+\nomenclature[C]{DoE}{Design of Experiment}
+\nomenclature[C]{m-DoE}{Model-based Design of Experiment}
+\nomenclature[C]{HBD}{Hot Ball Diffusion}
+\nomenclature[C]{SC}{Shrinking Core}
+
+\printnomenclature
+
 \end{document}

### 2024-09-19 Sections/Literature_Review.tex
19.09

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Design of Experiments (DoE) is a structured approach that examines how various elements influence a particular result. By evaluating multiple factors at once, DoE allows the uncovering of the impacts of each element and their combinations, yielding a comprehensive comprehension of the entire system. DoE begins with determining an experiment's objectives and selecting the study's process factors. DoE aims to obtain the maximum information from an experimental apparatus modelled by devising experiments that will yield the most informative data in a statistical sense for use in parameter estimation and model validation.

	The first ideas of DoE were introduced by \citet{Fisher1935}, who described the fundamental problem of experimental design as deciding what pattern of factors combination will best reveal the properties of the response, and this response is influenced by the factors. This type of DoE views an experiment as simply connecting inputs with outputs and is therefore called a "black-box experiment design". It aims to select the combinations of factor values that will provide the most information on the input-output relationship in the presence of variation. This type's main class of statistical design techniques is the so-called factorial method. These methods are created to measure the additive effects on a response for each input factor and investigate the effects of interactions between factors. Factorial methods are unsuitable for situations where constraints exist on the output or internal states. They must also be better suited for dynamic experiments, where inputs and outputs are complex time profiles. However, this group of methods is still widely used due to its simplicity.

	The factorial methods can be used for parameter screening, giving main interaction effects of the considered factors with fewer runs. \citet{Ramandi2011} applied a full factorial design for screening the extraction parameters of fatty acids from \textit{Borago officinalis L.} flowers by SFE technique before optimisation using central composition design. Four factors: temperature, pressure, modifier volume and static extraction time were considered independent variables for full factorial design. All these factors were studied at two levels.

	\citet{Caldera2012} optimised extraction parameters of SFE to extract antioxidant compounds from rosemary. $2^3$ full factorial design was used to select important variables before optimisation of the selected factors by Box-Behnken design. Three factors, namely temperature, pressure and static extraction time, were studied in this experiment.

	As opposed to the "black-box" statistical experiment design methods, another form of optimal design has been developed, which takes explicit advantage of some knowledge of the structure underlying the system, represented by a mathematical model, in particular in the form of differential and algebraic equations. What characterises the model-based experiment design approach is :

	\begin{enumerate}
		\item the explicit use of the model equations and current parameters to predict the "information content" of the next experiment
		\item the application of an optimisation framework to the solution of the resulting numerical problem
	\end{enumerate}

	After an initial dataset has been collected and fitted to a mathematical model, the model undergoes further analysis. Additional experiments may be designed and conducted to differentiate between competing models that passed the preliminary tests. Once inadequate models are rejected, the remaining model may undergo another round of experiment design to enhance the precision of its parameters. This paper focuses on the final step of the validation procedure, known as model-based Design of Experiments (m-DoE), aimed at improving parameter precision. To the authors' knowledge, the m-DoE has not been applied to any case of supercritical extraction. The literature review below provides examples of this technique used in crystallization and pharmacology processes.

	\citet{Chung2000} applied model-based experimental design to a batch crystallization process with a cooling jacket. A dynamic programming formulation minimizes the volume of a confidence hyper-ellipsoid for the estimated nucleation and growth parameters over the supersaturation profile and the seed characteristics, namely, the crystal mass, mean size, and width of the seed distribution. As a result, the accuracy of the parameter estimates can be improved by identifying the optimal temperature profile.

	\citet{Duarte2019} investigated compartment models incorporating Michaelis-Menten elimination kinetics for pharmacological applications. The authors designed both static and dynamic experiments for 2- and 3-compartment models using D-optimality criteria. The dynamic experiments for both models involved determining the initial concentration in the first compartment and optimizing the profile of the mass flow rate of the drug entering this compartment.

\end{document}

### 2024-09-19 Sections/Optimal_design_of_experiment.tex
19.09

@@
 
-	\subsubsection{Fisher information}
+	\subsubsection{Fisher Information}
 
-	The Fisher information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable.
-The Fisher information is related to the second derivative (or the curvature) of the log-likelihood function with respect to the parameter.
+	The Fisher Information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable.
+The Fisher Information is related to the second derivative (or the curvature) of the log-likelihood function with respect to the parameter.
 This relationship provides a measure of how "sensitive" the likelihood is to changes in the parameter value.
-The Fisher information matrix $\mathcal{F}$ can be calculated as follow.
+The Fisher Information matrix $\mathcal{F}$ can be calculated as follow.
 
@@
 
-	If every experiment at time $t_i$ is independent and characterized by its own $\sigma_{t_i}$, then the Fisher information matrix can be presented in the more compact way:
+	If every experiment at time $t_i$ is independent and characterized by its own $\sigma_{t_i}$, then the Fisher Information matrix can be presented in the more compact way:
 
@@
 
-	In other words, the precision to which we can estimate $\Theta$ is limited by the Fisher information of the likelihood function.
-Based on the Cramer-Rao inequality, the Fisher information matrix can used to calculate the covariance matrices associated with maximum-likelihood estimates.
+	In other words, the precision to which we can estimate $\Theta$ is limited by the Fisher Information of the likelihood function.
+Based on the Cramer-Rao inequality, the Fisher Information matrix can used to calculate the covariance matrices associated with maximum-likelihood estimates.
 
@@
 
-	The optimal design of experiments (DOE) is a statistical concept that refers to the process of planning an experiment, which allow parameters to be estimated without bias and with minimum variance.
+	The optimal design of experiments is a statistical concept that refers to the process of planning an experiment, which allow parameters to be estimated without bias and with minimum variance.
 Optimal design ensures that the experiment can provide the most informative data possible.
@@
 	The cost function should describe the amount of information from an experiment.
-For that purpose it can be assumed a function $\kappa$ can be related to the Fisher information obtained an arbitrary operating conditions.
+For that purpose it can be assumed a function $\kappa$ can be related to the Fisher Information obtained an arbitrary operating conditions.
 
@@
 Selecting $Q$ as a row vector results in C-optimality.
-Setting $Q = \textbf{I}_{n_\Theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalues of the Fisher information matrix, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.
+Setting $Q = \textbf{I}_{n_\Theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalues of the Fisher Information matrix, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.
 The most commonly used criterion is the D-optimality that involves $k = 0$, $Q = \textbf{I}_{n_\Theta}$, requiring the minimization of $\det \mathcal{F}^{-1}(\Theta, \Xi)$, or, equivalently, maximization of

### 2024-09-19 Sections/Results_DOE.tex
19.09

@@
 \begin{document}
+
+	\begin{comment}
 
@@
 
+	\end{comment}
+
+	To identify the global solution for Equations \ref{EQ:Formulation_2}, the optimization problem is solved multiple times, each run starting from a random initial solution sampled from a uniform distribution.
+Figure \ref{fig:scatter} compares the initial and final cost function values across multiple optimization runs for all cases.
+The solution with the lowest cost function value is considered the global solution for each case.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=\columnwidth]{Figures/Results/scatter.png}	
+		\caption{Initial vs final values of the cost function}
+		\label{fig:scatter}
+	\end{figure}
+
+	From Figure \ref{fig:scatter}, it is evident that multiple local solutions exist.
+By analyzing locations of the clusters in Figure \ref{fig:scatter}, it can be concluded that experiments conducted near the critical point provide more information regarding the correlation than those conducted farther from it.
+The closer the pressure is to the critical point, the larger the deviations in the physical properties of $CO_2$ caused by changes in the controls, leading to greater variation in the Reynolds number, and consequently to more informative experiments.
+
+	For each pressure case, the profiles with the lowest value of the objective function are further analysed.
+As shown in Figure \ref{fig:profiles_T}, all the inlet temperature profiles follow the same pattern.
+Initally, the system starts from the highest temperature (upper control bound) and gradually decreasing to lowest temperatures (lower control bound).
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=\columnwidth]{Figures/Results/Profile_T.png}	
+		\caption{Optimal inlet temperature profile}
+		\label{fig:profiles_T}
+	\end{figure}
+
+	As presented in Figure \ref{fig:profiles_F}, in four out of five analysed cases, the corresponding mass flow rate profiles initially start at low values and gradually increase, reaching their maximum when the inlet temperature reaches its minimum.
+Later, the mass flow rates decrease to minimum values, and eventually, they rise again to reach their maximums at the final time.
+The only solution, which has different mass flow rate profile corresponds to pressure of 100 bar.
+The mass flow rate profile make the U-shape pattern, which starts the maximum value, then diminish to minimum and increases to the maximum value.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=\columnwidth]{Figures/Results/Profile_F.png}	
+		\caption{Optimal mass flow rate profiles}
+		\label{fig:profiles_F}
+	\end{figure}
+
+	Figure \ref{fig:profiles_y} shows the predicted yield curves.
+The yield and scatter plots show that the most informative experiments do not necessarily correspond to those with the highest yield.
+This is because the variation in $CO_2$'s physical properties differs depending on the system's pressure.
+At higher pressures, the extraction rates are high enough that the amount of collected oils becomes almost the same, which makes it difficult to distinguish between experiments.
+The optimal yield profiles are characterized by a wavy pattern rather than the smooth exponential-like pattern observed under steady conditions.
+This behaviour is expected, as the determinant of the Hessian matrix, when evaluated at a critical point of a function, is equal to the Gaussian curvature of the function considered as a manifold.
+When the sum of the Hessian determinants is maximized, the number of critical points increases, leading to the wavy pattern observed in the yield curves.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=\columnwidth]{Figures/Results/yield.png}	
+		\caption{Optimal yield profiles}
+		\label{fig:profiles_y}
+	\end{figure}
+
 \end{document}

### 2024-09-19 Sections/introduction_imp.tex
19.09

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Supercritical CO$_2$ is defined as carbon dioxide that is pressurized and heated above its critical point (31.1 $^\circ C$, 74 bar). Depending on the operating conditions, the fluid properties such as viscosity and density can vary, which leads to multiple industrial applications of CO$_2$.

	The supercritical carbon dioxide is commonly used for impregnation as described by \citet{Weidner2018}, \citet{Machado2022} or \citet{Fathi2022}. Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces. The main advantage of using supercritical CO$_2$ is that after depressurization, it desorbs from the surface and evaporates, leaving a solvent-free product. On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.

	Another application of supercritical CO$_2$ is nanoparticles formation as investigated by \citet{Padrela2018}, \citet{Franco2021}, \citet{SaadatiArdestani2020} or \citet{Sodeifian2022}. Supercritical carbon-dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating operating conditions. Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nanosized particles or crystals, such as reduced use of toxic solvents. Moreover, the CO$_2$ is completely removed from the final product by simple depressurization.

	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993} or \citet{Sovova1994}. Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks. Distillation, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds. This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction. Supercritical CO$_2$ is appealing due to its distinctive properties: it is inflammable, non-toxic and non-corrosive. Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.

	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process. Chamomile is a medicinal herb widely cultivated in southern and eastern Europe — in countries such as Germany, Hungary, France and Russia. It can be found outside Europe, for instance in Brazil as discussed by \citet{Singh2011}. This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets. Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy. Extracts of chamomile are widely used to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia and other sleep-related conditions, according to \citet{Srivastava2009}. \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg. The highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine. In comparison, chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.

	The literature offers various mathematical models to describe the extraction of valuable compounds from biomass. Selecting a process model is case-to-case dependent and requires analysis of each model's specific assumptions about mass transfer and thermodynamic equilibrium.

	\citet{Goto1996} presented the Shrinking Core (SC) model, which describes a process of irreversible desorption that is followed by diffusion through the pores of a porous solid. When the mass transfer rate of the solute in the non-extracted inner region is significantly slower than in the outer region, where most of the solute has already been extracted, or when the solute concentration exceeds its solubility in the solvent, a distinct boundary may form between the inner and outer regions. As extraction progresses, the core of the inner region shrinks. The model envisions supercritical CO$_2$ extraction as a sharp, inward-moving front, with a completely non-extracted core ahead of the front and a fully extracted shell behind it.

	\citet{Sovova1994} proposed The Broken-and-Intact Cell (BIC) model, which assumes that a portion of the solute, initially stored within plant structures and protected by cell walls, is released during the mechanical breakdown of the material. The solute located in the region of broken cells near the particle surface is directly exposed to the solvent, while the core of the particle contains intact cells with undamaged walls. This model describes three extraction phases: a fast extraction phase for accessible oil, a transient phase, and a slow phase controlled by diffusion. The model has been successfully applied to the extraction of grape oil (\citet{Sovova1994b}) and caraway oil (\citet{Sovova1994a}).

	The Supercritical Fluid Extraction (SFE) process can be be treated similarly to heat transfer, considering solid particles like hot balls cooling down in a uniform environment. \citet{Bartle1990} introduced the hot ball diffusion (HBD) model, where spherical particles with uniformly distributed solute diffuse similarly to heat diffusion. Unlike the BIC model, where solute is readily available on the particle surface, the HBD model is suited for systems with small quantities of extractable materials and is not limited by solubility. The model is particularly relevant when internal diffusion controls mass transfer, allowing results from single particles to be extended to the entire bed under uniform conditions. \citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes for natural materials.

	\citet{Reverchon1996} proposed a model for extraction of essential oils, which are mainly located inside the vegetable cells in organules called vacuoles. Only a small fraction of essential oil might be near the particle surface due to the breaking up of cells during grinding or in epidermal hairs located on the leaf surface. The fraction of oil freely available on the particle surface should not be significant in the case of SFE from leaves. Consequently, SFE of essential oil from leaves should be mainly controlled by the internal mass-transfer resistance. Therefore, the external mass-transfer coefficient was neglected in the development of the model of \citet{Reverchon1996}. The mass balances were developed in the additional hypotheses that the axial dispersion can be neglected and that the solvent density and flow rate are constant along the bed.

	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process. This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel. The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract. Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T^{in}$) are adjustable and measurable, while the outlet temperature ($T^{out}$) and the amount of product at the outlet can only be monitored. Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=\columnwidth]{Figures/PFD.drawio.pdf}
		\caption{Process flow diagram.}
		\label{fig: SFE_drawing}
	\end{figure}

\end{document}

### 2024-09-19 SFE_DOE_Chamomile/Case_1_T_F/Yield_Plot.m

@@ -20,10 +20,10 @@ function [Yield] = Yield_Plot(feedPress, T0homog, Flow)
     
     % Set time of the simulation
     PreparationTime         = 0;
-    ExtractionTime          = 300;
+    ExtractionTime          = 600;
     timeStep                = 5;                                                 % Minutes
-    SamplingTime            = 10;                                                % Minutes
-    OP_change_Time          = 15;                                                % Minutes
+    SamplingTime            = 5;                                                % Minutes
+    OP_change_Time          = 10;                                                % Minutes
     
     simulationTime          = PreparationTime + ExtractionTime;
     

### 2024-09-19 SFE_DOE_Chamomile/Case_1_T_F/test_RQ.m

@@ -1,0 +1,88 @@
+% Ensure CasADi is installed and available in your MATLAB environment
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+% Ensure CasADi is installed and available in your MATLAB environment
+import casadi.*
+
+% Number of data points
+N = 100;    % Number of points in the dataset
+alpha_init = 1.0;  % Initial value of Rational quadratic kernel parameter
+
+% Generate sine wave data
+x_data = linspace(0, 2*pi, N)';
+y_data = sin(x_data) + 0.1*randn(N, 1);  % Adding a bit of noise
+
+% Select every third data point for the kernel (downsampling)
+indices = 1:3:N;
+x_selected = x_data(indices);  % Use every third point for kernel calculations
+
+% Rational Quadratic Kernel function
+function K = RationalQuadratic_kernel(x, x_prime, l, alpha)
+    % x and x_prime are input vectors
+    % l is the length-scale
+    % alpha is the relative weighting parameter
+    K = (1 + ((x - x_prime).^2) / (2 * alpha * l^2)).^(-alpha);
+end
+
+% Setting up CasADi OptiStack for optimization
+opti = Opti();
+
+% Define Rational Quadratic Kernel parameters for optimization
+l = opti.variable(1);           % Length-scale parameter
+alpha = opti.variable(1);        % Alpha parameter for kernel flexibility
+kernel_weights = opti.variable(length(indices), 1);  % Weights for each selected data point
+
+% Initialize the Rational Quadratic kernel matrix for the full dataset
+K_full = MX(zeros(N, length(indices)));  % Only uses the selected data points
+
+% Fill the kernel matrix using the Rational Quadratic Kernel
+for i = 1:N
+    for j = 1:length(indices)
+        K_full(i, j) = RationalQuadratic_kernel(x_data(i), x_selected(j), l, alpha);
+    end
+end
+
+% Construct the model: linear combination of kernel weights and kernel matrix
+model = K_full * kernel_weights;
+
+% Define the loss function: least squares error between the model and actual data
+loss = sum((model - y_data).^2);
+
+% Set the objective to minimize the loss
+opti.minimize(loss);
+
+% Set initial guesses for the kernel parameters and weights
+opti.set_initial(l, 1);
[…]

### 2024-09-21 Sections/Literature_Review.tex
21.09

@@
 
-	The factorial methods can be used for parameter screening, giving main interaction effects of the considered factors with fewer runs.
-\citet{Ramandi2011} applied a full factorial design for screening the extraction parameters of fatty acids from \textit{Borago officinalis L.} flowers by SFE technique before optimisation using central composition design.
-Four factors: temperature, pressure, modifier volume and static extraction time were considered independent variables for full factorial design.
-All these factors were studied at two levels.
+	\citet{Ramandi2011} conducted a study to identify the variables with the greatest influence on the extraction yield of fatty acids from \textit{Borago officinalis L.} flowers using Supercritical Fluid Extraction (SFE).
+A Full Factorial Design was employed as a screening method, resulting in a design matrix of 32 runs ($2^5$) carried out randomly to minimize the impact of extraneous or nuisance variables.
+The low and high values for the factors were selected based on previous research.
+After determining the most significant variables, a Central Composite Design was applied to three factors—temperature, pressure, and modifier volume—to optimize the SFE conditions.
+This allowed for the modeling of the response surface by fitting a second-order polynomial.
 
-	\citet{Caldera2012} optimised extraction parameters of SFE to extract antioxidant compounds from rosemary.
-$2^3$ full factorial design was used to select important variables before optimisation of the selected factors by Box-Behnken design.
-Three factors, namely temperature, pressure and static extraction time, were studied in this experiment.
+	Similarly, \citet{Caldera2012} conducted a study to optimize SFE variables, specifically extraction pressure, extraction temperature, and static extraction time, for the maximum extraction of carnosol and carnosic acid from Venezuelan rosemary (\textit{Rosmarinus officinalis L.}) leaves.
+A $2^3$ Full Factorial Design was initially used to examine these three variables.
+Based on the statistically significant variables, a Box-Behnken design was employed to create a matrix of 15 experiments, which was used to further optimize the SFE process for maximum carnosol and carnosic acid extraction using Response Surface Methodology.
 
@@
 This paper focuses on the final step of the validation procedure, known as model-based Design of Experiments (m-DoE), aimed at improving parameter precision.
-To the authors' knowledge, the m-DoE has not been applied to any case of supercritical extraction.
-The literature review below provides examples of this technique used in crystallization and pharmacology processes.
+To the authors' knowledge, the m-DoE has not been applied to any case of supercritical extraction, so the further literature review provides examples of application in crystallization and pharmacology processes.
 

### 2024-10-30 Sections/DOE.tex
30.10

\documentclass[../Article_Design_of_Experiment.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsubsection{Bayesian Estimation}

	After selecting a process model and estimating its parameters based on initial experiments, additional experiments may be planned to further refine the estimates of the model coefficients. An optimal experimental design enables parameters to be estimated without bias and with minimum variance. A model-based approach to experimental design allows for the consideration of system complexity and constraints, such as practical infeasibility due to safety concerns.

	Building on the work of\citet{Walter2010} and \citet{Himmelblau1970}, Bayes' Theorem can be employed to define a general cost function:

	{\footnotesize
		\begin{equation}
			\max p\left(\theta \mid Y, \Xi \right) = \frac{p\left(Y \mid \theta, \Xi\right) p\left(\theta\right)}{\int p\left(Y \mid \theta, \Xi\right) p\left(\theta\right) d\theta} \propto p\left(Y \mid \theta, \Xi\right) p\left(\theta\right)
		\end{equation}
	}

	The aim of experimental design is to maximize the posterior probability of estimating $\theta$ ($p\left(\theta \mid Y, \Xi \right)$) given the prior distribution of $\theta$ ($p(\theta)$) obtained from previous experiments, and the likelihood of obtaining observations $Y$ given $\theta$ and experimental conditions $\Xi$. The new observations $Y$, under a set of experimental conditions $\Xi$, are assumed to be normally distributed around the model output $y$, with measurement error covariance $\Sigma_Y$. Similarly, $\theta$ is assumed to be normally distributed around the true parameter values $\hat{\theta}$, with covariance matrix $\Sigma_\theta$ estimated from previous experiments. The probabilities can be defined as

	{\footnotesize
		\begin{align} 
			p\left(Y \mid \theta, \Xi \right) &= \frac{|\Sigma_Y|^{-1/2}}{\left(2\pi\right)^{n_Y/2}} \exp\left( -\frac{1}{2} \left(Y - y\right)^\top \Sigma_Y^{-1} \left(Y - y\right) \right), \\ 
			p\left(\theta\right) &= \frac{|\Sigma_\theta|^{-1/2}}{\left(2\pi\right)^{n_\theta/2}} \exp\left( -\frac{1}{2} \left(\theta - \hat{\theta}\right)^\top \Sigma_\theta^{-1} \left(\theta - \hat{\theta}\right) \right),
		\end{align}
	}

	where $n_Y$ is the number of observations and $n_\theta$ is the number of parameters to be estimated. By substituting these expressions into the cost function:

	{\footnotesize 
		\begin{equation} 
			\ln p\left(\theta \mid Y, \Xi \right) \propto -\frac{1}{2} \left[ \left(Y - y\right)^\top \Sigma_Y^{-1} \left(Y - y\right) + \left(\theta - \hat{\theta}\right)^\top \Sigma_\theta^{-1} \left(\theta - \hat{\theta}\right) \right] 
		\end{equation} }

	By linearizing the model output around $\hat{\theta}$, the model output becomes: $y = y(\hat{\theta}) + J \Delta_\theta$, where $J = \frac{\partial y(\hat{\theta})}{\partial \theta}$ is the Jacobian matrix evaluated at $\hat{\theta}$, and $\Delta_\theta = \theta - \hat{\theta}$. To simplify the equation, we introduce the residual term $\Delta_y = Y - y(\hat{\theta})$. Substituting these into the expression for $\ln p\left(\theta \mid Y, \Xi \right)$:

	{\footnotesize 
		\begin{flalign*} 
			\ln p\left(\theta \mid Y, \Xi \right) &\propto -\frac{1}{2} \left[ \left(\Delta_y - J \Delta_\theta \right)^\top \Sigma_Y^{-1} \left(\Delta_y - J \Delta_\theta \right) + \Delta_\theta^\top \Sigma_\theta^{-1} \Delta_\theta \right] && \\
			&= -\frac{1}{2} \left[ \Delta_y^\top \Sigma_Y^{-1} \Delta_y - 2 \Delta_y^\top \Sigma_Y^{-1} J \Delta_\theta + \Delta_\theta^\top \left( J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1} \right) \Delta_\theta \right] &&
		\end{flalign*} }

	This equation can be reformulated by expanding the quadratic terms:

	{\footnotesize
		\begin{flalign*}
			\ln p\left(Y \mid \theta, \Xi \right) &\propto -\frac{1}{2} \left( \underbrace{r^\top \Sigma_Y^{-1} r}_{C} - 2 \underbrace{ J^\top \Sigma_Y^{-1} \Delta_y }_{B} \Delta_\theta + \Delta_\theta^\top \underbrace{\left( J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1} \right)}_{A} \Delta_\theta \right) && \\
			&=-\frac{1}{2} \left( \Delta_\theta^\top A \Delta_\theta - 2 B^\top \Delta_\theta + C \right) &&
		\end{flalign*}
	}

	By completing the square, we introduce $\theta^* = \hat{\theta} + A^{-1} B$, and the cost function becomes:

	{\footnotesize 
		\begin{equation} 
			\ln p\left(\theta \mid Y, \Xi \right) \propto -\frac{1}{2} \left( \left( \theta - \theta^* \right)^\top A \left( \theta - \theta^* \right) + C - B^\top A^{-1} B \right) 
		\end{equation} }

	It can be observed that the quadratic term represents the spread of the posterior multivariate distribution around the mean $\theta^*$. The constant term $C - B^\top A^{-1} B$ is independent of $\theta$ and does not affect the shape of the posterior distribution but is still important for normalization. This constant term is absorbed into the normalizing constant of the posterior distribution. It does not affect the estimation of $\theta$ or the shape of the posterior distribution and thus can be neglected when focusing on parameter estimation or experimental design. Therefore, the posterior distribution of $\theta$ given $Y$ and $\Xi$ is:

	{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) \propto \exp \left( -\frac{1}{2} \left( \theta - \theta^* \right)^\top A \left( \theta - \theta^* \right) \right) \end{equation} }

	This is the expression of a multivariate normal distribution with mean $\theta^*$ and covariance matrix $A^{-1}$:

	{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) = \mathcal{N}\left( \theta^*, A^{-1} \right) \end{equation} }

	As the goal of optimal experimental design is to improve the precision of parameters, the main focus is on the matrix $A$, which consists of two terms. The first corresponds to the information gained from new observations based on the model and measurement error ($J^\top \Sigma_Y^{-1} J$), while the second is the prior information ($\Sigma_\theta^{-1}$).

	\subsubsection{Fisher Information}

	The Fisher Information $\mathcal{F}$ measures the amount of information that an observable random variable carries about an unknown parameter of the distribution that models the random variable. It is related to the negative expected value of the second derivative (or curvature) of the log-likelihood function with respect to the parameter, providing a measure of how "sensitive" the likelihood is to changes in the parameter value.

	{\footnotesize \begin{equation} \mathcal{F}(\theta, \Xi) = -\mathop{\mathbb{E}}_{Y \mid \theta, \Xi} \left[ \frac{\partial^2 \ln p \left( Y \mid \theta, \Xi \right)}{\partial \theta \partial \theta^\top} \right] \end{equation} }

	Under regularity conditions, the Fisher Information can also be expressed as:

	{\footnotesize \begin{equation} \mathcal{F}(\theta, \Xi) = \mathop{\mathbb{E}}_{Y \mid \theta, \Xi} \left[ \left( \frac{\partial \ln p\left( Y \mid \theta, \Xi \right)}{\partial \theta} \right) \left( \frac{\partial \ln p\left( Y \mid \theta, \Xi \right)}{\partial \theta} \right)^\top \right] \end{equation} }

	By inserting the expression for $p\left( Y \mid \theta, \Xi \right)$ and performing similar manipulations as in the previous section, the Fisher Information becomes:

	{\footnotesize \begin{equation} \mathcal{F}(\theta, \Xi) = J^\top \Sigma_Y^{-1} J \end{equation} }

	Since the likelihood is Gaussian and linearized, the second derivative of the log-likelihood with respect to $\theta$ simplifies to $J^\top \Sigma_Y^{-1} J$, and its negative expected value yields the same expression because the expectation of the Hessian is constant in this linear approximation.
	\begin{comment}

	Under the hypotheses that:

	\begin{itemize}
		\item The set of all data vectors $Y$ with $p(Y \mid \theta, \Xi) > 0$ does not depend on $\theta$.
		\item The partial derivatives $\frac{\partial p(Y \mid \theta, \Xi)}{\partial \theta_i}$ for $i=1,2,...,n_\theta$ are absolutely integrable.
		\item The expected value $\mathop{\mathbb{E}}_{Y \mid \theta, \Xi} \left[ \frac{\partial^2 \ln p \left( Y \mid \theta, \Xi \right)}{\partial \theta \partial \theta^\top} \right]$ exists and is invertible.
	\end{itemize}

	\end{comment}
	The Cramér-Rao inequality provides that the covariance of any unbiased estimator $\hat{\theta}$ satisfies:

	{\footnotesize \begin{equation} \operatorname{Cov}(\hat{\theta}) \geq \mathcal{F}^{-1}(\theta) \end{equation} }

	In other words, the precision with which we can estimate $\theta$ is limited by the Fisher Information of the likelihood function. Based on the Cramér-Rao inequality, the Fisher Information matrix can be used to calculate the covariance matrices associated with maximum-likelihood estimates.

	\subsubsection{Optimal experimental design}

	The optimal design of experiments is a statistical concept that refers to the process of planning an experiment that allows parameters to be estimated without bias and with minimum variance. Optimal design ensures that the experiment can provide the most informative data possible. This often involves balancing the study of main effects and interactions between factors. Moreover, by efficiently planning experiments, optimal design aims to reduce the overall resources required, such as time, materials, and manpower.

	The methodology for collecting data to estimate the parameters of a specific model is influenced by a series of qualitative decisions made throughout the experimental and modeling process, such as model structure, sensor locations, or equipment choices. Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, etc.). Experiment design aims to determine experimental conditions adapted to the final purpose of the modeling.

	Consider that each scalar observation in a study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ represents the specific experimental conditions (such as sampling time, operating conditions, etc.) under which the $i$-th observation is gathered. When collecting $n_t$ such observations, the assembly of these $\xi_i$ vectors forms the matrix $\Xi = (\xi_1, \xi_2, \dots, \xi_{n_t})$, which combines all the experimental conditions that need optimization. To align the design of the experiment with practical realities, it's important to take into account various constraints, such as the total duration of the experiments, the maximum temperature of the inlet stream, or the minimum interval between sampling events. The set of all possible combinations for $\Xi$ that adhere to these constraints is denoted as $\bar{\Xi}$.

	The formulation of a cost function $j$ allows for the framing of optimal experiment design as a problem of constrained optimization. In this context, the optimal experiment, denoted as $\Xi^*$, is:

	{\footnotesize \begin{equation} \Xi^* = \arg~\underset{\Xi \in \bar{\Xi}}{\text{opt}}~j\left(\Xi\right) \end{equation} }

	The cost function should describe the amount of information obtained from an experiment. For that purpose, it can be assumed that a function $\kappa$ can be related to the covariance matrix $A^{-1}$ obtained at arbitrary operating conditions:

	{\footnotesize \begin{equation} j(\Xi) = \kappa\left[ A^{-1}(\theta, \Xi) \right] \end{equation} }

	Recall that in the Bayesian estimation framework, the posterior covariance matrix of the parameter estimates is given by $\Sigma = A^{-1} = \left(J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1}\right)^{-1} $. $J$ is the Jacobian matrix of the model outputs with respect to the parameters, $\Sigma_Y$ is the covariance matrix of the measurement errors, and $\Sigma_\theta$ is the prior covariance matrix of the parameters.

	A general class of design of experiments (DOE) optimality criteria is given by:

	{\footnotesize 
		\begin{align} 
			\kappa_k\left( A^{-1}(\theta) \right) &= \left[ \frac{1}{n_\theta} \operatorname{trace}\left( Q A^{-1}(\theta, \Xi) Q^\top \right)^k \right]^{1/k} & \text{if} \det A^{-1} \neq 0, \nonumber \\ 
			\kappa_k\left( A^{-1}(\theta) \right) &= \infty & \text{if} \det A^{-1} = 0
		\end{align} }

	where $Q$ is a weighting matrix. The special case $k=1$ corresponds to the L-optimality cost function:

	{\footnotesize \begin{equation} j_L(\Xi) = \operatorname{trace} \left( Q A^{-1}(\theta, \Xi) Q^\top \right) \end{equation} }

	Choosing $Q = \mathbf{I}_{n\theta}$ corresponds to the A-optimality cost function. An A-optimal experiment minimizes the sum of the variances of the parameter estimates (i.e., the trace of the covariance matrix). When $Q$ is diagonal with $[Q]_{ii} = 1/\theta_i$, this corresponds to weighting the parameters inversely by their magnitude, which is associated with relative precision.

	Selecting $Q$ as a row vector results in C-optimality, which focuses on linear combinations of parameters. Setting $Q = \mathbf{I}_{n\theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalue of the covariance matrix $A^{-1}(\theta, \Xi)$, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.

	The most commonly used criterion is the D-optimality, which involves $k = 0$ and $Q = \mathbf{I}_{n\theta}$, requiring the minimization of $\det A^{-1}(\theta, \Xi)$, or equivalently, maximization of:

	{\footnotesize \begin{equation} j_D(\Xi) = \det A(\theta, \Xi) \end{equation} }

	Since $\det A(\theta, \Xi) = 1 / \det A^{-1}(\theta, \Xi)$, maximizing $\det A$ is equivalent to minimizing $\det A^{-1}$.

	The D-optimality criterion originates from the geometric interpretation of the determinant. A two-dimensional matrix with real number entries can represent two linear maps: one mapping the standard basis vectors to the rows and the other to the columns. In both cases, the images of the basis vectors form a parallelogram that represents the image of the unit square under the mapping. The absolute value of the determinant is the area of this parallelogram, reflecting the scale factor by which the matrix transforms areas. The signed value of the determinant indicates the oriented area of the parallelogram, which is negative when the angle from the first to the second defining vector is clockwise. In the multi-dimensional case, the matrix maps the n-cube to an n-dimensional parallelotope. The determinant provides the signed n-dimensional volume of this parallelotope, describing the volume scaling factor of the linear transformation produced by the matrix. Based on this geometric interpretation, a D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters. Figure \ref{fig:score_fun} illustrates the graphical representation of different optimality conditions.

	\begin{figure}[!h]
		\centering
		\resizebox{0.4\textwidth}{!}{%
			\begin{tikzpicture}
				% Ellipse parameters
				\def\ellipsecenter{(3,3)}
				\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
				\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
				\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow

				% Draw the rotated ellipse
				\draw[fill=gray!10, draw=black, rotate around={45:\ellipsecenter}] \ellipsecenter ellipse (3cm and 1cm);

				% Draw the dashed rectangle
				\draw[dashed] (0.75,0.75) rectangle (5.25,5.25);

				% Draw the arrows and label them with adjustable positions
				\draw [-latex] \ellipsecenter -- \ellipseA node[yshift=-4cm, xshift=2.5cm,rotate around={-45:\ellipsecenter}] {A-optimality};
				\draw [-latex] \ellipsecenter -- \ellipseB node[yshift=0cm, xshift=-3.9cm,rotate around={45:\ellipsecenter}] {E-optimality};
				\draw [-latex] \ellipseC -- (2,2) node[yshift=-1cm, xshift=2cm] {D-optimality};

				% Draw axes
				\draw[thick,->] (0,0) -- (6,0) node[below] {$\theta_1$};
				\draw[thick,->] (0,0) -- (0,6) node[left] {$\theta_2$};
			\end{tikzpicture}
		}%
		\caption{Graphical representation of score functions}
		\label{fig:score_fun}
	\end{figure}

	\subsubsection{Problem formulation}

	Details on the process model can be found in [article 1]. The model's empirical correlations are derived based on laboratory experiments conducted under various but constant operating conditions: $30^\circ\text{C} - 40^\circ\text{C}$, $100 - 200$ bar, and $3.33 \cdot 10^{-5} - 6.67 \cdot 10^{-5}$ kg/s. This study employs a model-based design of experiments technique to design an experiment with dynamically changing conditions to improve the precision of the correlation for $D_i$. The decision variables are adjusted every 10 minutes and are kept constant within each interval (piecewise constant controls). These controls have lower and upper bounds that match the validated range of the process model detailed in [article 1]. The sampling time is set to 5 minutes, and the total extraction time is 600 minutes. The standard deviation $\sigma^2$ was estimated to be 0.10.

	The analyzed correlations consist of two independent variables: Reynolds number and mass flow rate. The Reynolds number is a function of fluid thermodynamic properties and velocity, and the fluid density can be affected by temperature or pressure changes. In this work, the decision variables are the inlet temperature ($T^{\text{in}}$) and mass flow rate ($F$), while the pressure is assumed to remain constant. The initial state is considered isothermal, so $T^0 = T^{\text{in}}(t=0)$. The optimal design of experiment problem is solved for multiple values of pressure, namely 100, 125, 150, 175, and 200 bar.

	In a real system, the mass flow rate and inlet temperature cannot be changed instantaneously, as they depend on the dynamics of the pump and heat exchanger, respectively. To prevent bang-bang-like control between the lower and upper bounds of the decision variables, a penalty term is introduced. Similar to many control problems, such as the Linear Quadratic Regulator, a quadratic penalty term is added to the cost function. This penalty increases the cost function value when there are rapid changes in the decision variables. The matrix $R$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$. The problem formulation is given by Equation \ref{EQ:Formulation_2}.

	{\footnotesize 
		\begin{equation} 
			\begin{aligned} \Xi^* &= \arg \min_{ T^{\text{in}}(t), F(t) } \int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + u(t)^\top R u(t) \right] dt \\ 
				\text{subject to} \quad & \dot{x} = G(x, t, \theta; \Xi), \\ 
				& t_0 = 0 \text{min} \\ 
				& t_f = 600 \text{min} \\ 
				& T^{0} = T^{\text{in}}(t=0), \\ 
				& P(t) \in \left\{100, 125, 150, 175, 200\right\} \text{bar}, \\ 
				%& R = \begin{bmatrix} 10^{-1} & 0 \ 0 & 10^{-2} \end{bmatrix}, \\ 
				%& u(t) = \begin{bmatrix} \dfrac{dF(t)}{dt} \ \dfrac{dT^{\text{in}}(t)}{dt} \end{bmatrix}, \\
				& 30^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\ 
				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5} 
				\end{aligned} 
				\label{EQ:Formulation_2} 
			\end{equation} }

\end{document}

### 2024-10-30 Sections/Saturation.tex
30.10

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsubsection{Uneven solute's distribution in the solid phase} \label{CH: Gamma_Function}

	Following the idea of the Broken-and-Intact Cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}:

	{\footnotesize
		\begin{equation}
			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) \label{EQ: C_sat_function}
	\end{equation} }

	where  ${\color{black}\Upsilon}$ describes the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term:

	{\footnotesize
		\begin{equation}
			\label{Model_kinetic}
			r_e = -\cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
	\end{equation} }

	The $\gamma$ function limits the solute's availability in the solid phase. Similarly to the BIC model, the solute is assumed to be contained in the cells, some of which are open because the cell walls were broken by grinding, with the rest remaining intact. The diffusion of the solute from a particle's core takes more time than the diffusion of the solute close to the outer surface. The same idea can be represented by the decaying internal diffusion coefficient, where the decreasing term is a function of the solute concentration in the solid.

	An alternative interpretation of the decay function $\gamma$ involves considering the porous structure of the solid particles, where the pores are initially saturated with the solute. During extraction, the solute within these pores gradually dissolves into the surrounding fluid. Initially, the solute molecules near the pore openings dissolve and diffuse rapidly due to the short diffusion paths. As the extraction progresses, the dissolution front moves deeper into the pore structure, and solute from the inner regions of the pores begins to dissolve. The diffusion of solute molecules from the interior of the pores to the external fluid becomes progressively slower because the effective diffusion path length increases. This lengthening of the diffusion path enhances the mass transfer resistance, reducing the overall diffusion rate.

	In an extreme case, this model could be compared with the Shrinking Core Model presented by \citet{Goto1996}, where the particle radius decreases as the solute content in the solid phase diminishes. In the SC model, the reduction in particle size leads to significant changes in both the diffusion path length and the surface area available for mass transfer. The diminishing particle size increases the diffusion path within the remaining solid core and decreases the external surface area, both of which contribute to a slower extraction rate. By comparing this to the varying diffusion coefficient in our model, some conceptual similarities can be noticed.

	\subsubsection{Empirical correlations}

	The empirical correlations for $D_i$ and $\Upsilon$ were derived by \citet{Sliczniuk2024} and validated for temperatures between $30 - 40~^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s. Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables. The region marked with the white dashed line represents the confidence region, where the model has been tested. Both correlations should be equal of greater than zero, to avoid unphysical behaviour such as the reverse mass transfer. The multiple linear regression functions are combined with the rectifier function to ensure the non-negativity.

	\begin{figure}[!ht]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Di.png}
		\caption{Multiple linear regression $D_i^R = f(Re, F)$}
		\label{fig:Correlation_Di}
	\end{figure}

	\begin{figure}[!ht]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Gamma.png}
		\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
		\label{fig:Correlation_Gamma}
	\end{figure}

\end{document}

### 2024-10-30 SFE_DOE_Chamomile_modified/MD.m

@@ -1,0 +1,222 @@
+function [] = MD(P, N_exp, N_core)
+    %initParPool
+
+    %addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+    addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+    %addpath('casadi_folder')
+    import casadi.*
+
+    %%
+    Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+    Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+    N                       = 5;
+    
+    %% Create the solver
+    Iteration_max               = 200;                                         % Maximum number of iterations for optimzer
+    %Time_max                    = 3;                                           % Maximum time of optimization in [h]
+    
+    nlp_opts                    = struct;
+    nlp_opts.ipopt.max_iter     = Iteration_max;
+    %nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+    nlp_opts.ipopt.hessian_approximation ='limited-memory';
+    
+    %% Load paramters
+    m_total                 = 3.0;
+    
+    % Bed geometry
+    before                  = 0.04;                                             % Precentage of length before which is empty
+    bed                     = 0.92;                                              % Percentage of length occupied by fixed bed
+    
+    % Set time of the simulation
+    PreparationTime         = 0;
+    ExtractionTime          = 600;
+    timeStep                = 5;                                                % Minutes
+    OP_change_Time          = 10; 
+    Sample_Time             = 5;
+    
+    simulationTime          = PreparationTime + ExtractionTime;
+    
+    timeStep_in_sec         = timeStep * 60;                                    % Seconds
+    Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+    Time                    = [0 Time_in_sec/60];                               % Minutes
+    
+    N_Time                  = length(Time_in_sec);
+    
+    SAMPLE                  = Sample_Time:Sample_Time:ExtractionTime;
+    
[…]

### 2024-10-30 SFE_DOE_Chamomile_modified/main_MD_Chamomile.m

@@ -1,0 +1,452 @@
+startup;
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
+
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+import casadi.*
+
+excel_file = 'Chamomile_Di_Gamma_2.xls';
+%rng(69)
+
+%%
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('dataset_2.xlsx');
+N                       = 5;
+
+%% Create the solver
+Iteration_max               = 15;                                         % Maximum number of iterations for optimzer
+Time_max                    = 10;                                           % Maximum time of optimization in [h]
+
+nlp_opts                    = struct;
+nlp_opts.ipopt.max_iter     = Iteration_max;
+%nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+nlp_opts.ipopt.hessian_approximation ='limited-memory';
+
+%% Load paramters
+m_total                 = 3.0;
+
+% Bed geometry
+before                  = 0.04;                                             % Precentage of length before which is empty
+bed                     = 0.92;                                              % Percentage of length occupied by fixed bed
+
+% Set time of the simulation
+PreparationTime         = 0;
+ExtractionTime          = 600;
+timeStep                = 5;                                                % Minutes
+OP_change_Time          = 15; 
+%OP_change_Time_P        = 100; 
+Sample_Time             = 5;
+
+simulationTime          = PreparationTime + ExtractionTime;
+
+timeStep_in_sec         = timeStep * 60;                                    % Seconds
+Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+Time                    = [0 Time_in_sec/60];                               % Minutes
+
+N_Time                  = length(Time_in_sec);
+
[…]

### 2024-10-30 SFE_DOE_Chamomile_modified/modelSFE_Corr_sensitivity.m

@@ -1,0 +1,152 @@
+function Sdot = modelSFE_Corr_sensitivity(X, p, mask, dt)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% Load Paramters
+    T_u           =     p{1};
+    P_u           =     p{2};
+    F_u           =     p{3} * 1e-5;
+
+    parameters    =     p(4:end);
+
+    %nstages       =     parameters{1};
+    C0solid       =     parameters{2};     % Extractor initial concentration of extract
+    r             =     parameters{3};     % Extractor length (m)
+    epsi          =     parameters{4};     % Void bed fraction
+    dp            =     parameters{5};     % Diameter of the particle (m)
+    L             =     parameters{6};     % Length of the extractor (m)
+    rho_s         =     parameters{7};     %
+    mi            =     parameters{9};
+
+    %km            =     parameters{8} ;
+    %Di            =     parameters{44}* 1e-13;      
+    %Dx            =     parameters{45}* 1e-12;      
+    Dx            =     1e-15;      
+    %gamma         =     parameters{46};
+
+    nstages_index =     numel(mask);
+    x             =     X(1:3*nstages_index+3);
+    s             =     reshape(X(3*nstages_index+4:end), 3*nstages_index+3, 3);
+
+    %% Properties of the bed
+    A             =     pi*r^2 ;       % Cross-section of the extractor (m^2)
+    rp            =     dp / 2;
+    lp2           =     (rp / 3)^2;
+
+    %% States
+    FLUID         =     x(0*nstages_index+1:1*nstages_index);
+    SOLID         =     x(1*nstages_index+1:2*nstages_index);
+    ENTHALPY_RHO  =     x(2*nstages_index+1:3*nstages_index);
+    PRESSURE      =     x(3*nstages_index+1);
+
+    TEMP          =     Reconstruct_T_from_enthalpy(ENTHALPY_RHO, PRESSURE, parameters);
+      
+    %Properties of the fluid in the extractor
+    Z             =     Compressibility(TEMP, PRESSURE,    parameters);
+
[…]

### 2024-10-30 SFE_DOE_Chamomile_modified/test_sensitivity.m

@@ -1,0 +1,276 @@
+startup;
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
+
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+import casadi.*
+
+excel_file = 'Chamomile_Di_Gamma_2.xls';
+%rng(69)
+
+%%
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('dataset_2.xlsx');
+%Q_RBF = readmatrix('Q_RBF.txt');
+%Q_FP  = readmatrix('Q_FP.txt');
+
+%% Create the solver
+Iteration_max               = 0;                                         % Maximum number of iterations for optimzer
+%Time_max                    = 17;                                           % Maximum time of optimization in [h]
+
+nlp_opts                    = struct;
+%nlp_opts.ipopt.max_iter     = Iteration_max;
+nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+nlp_opts.ipopt.hessian_approximation ='limited-memory';
+
+%% Load paramters
+m_total                 = 3.0;
+
+% Bed geometry
+before                  = 0.04;                                             % Precentage of length before which is empty
+bed                     = 0.92;                                              % Percentage of length occupied by fixed bed
+
+% Set time of the simulation
+PreparationTime         = 0;
+ExtractionTime          = 600;
+timeStep                = 5;                                                % Minutes
+OP_change_Time          = 10; 
+Sample_Time             = 5;
+
+simulationTime          = PreparationTime + ExtractionTime;
+
+timeStep_in_sec         = timeStep * 60;                                    % Seconds
+Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+Time                    = [0 Time_in_sec/60];                               % Minutes
+
+N_Time                  = length(Time_in_sec);
+
[…]

### 2024-11-16 Sections/DOE.tex
16.11

@@
 		\centering
-		\resizebox{0.4\textwidth}{!}{%
+		\resizebox{0.8\columnwidth}{!}{%
 			\begin{tikzpicture}
@@
 		\begin{equation} 
-			\begin{aligned} \Xi^* &= \arg \min_{ T^{\text{in}}(t), F(t) } \int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + u(t)^\top R u(t) \right] dt \\ 
+			\begin{aligned} \Xi^* &= \arg \min_{ T^{\text{in}}(t), F(t) } \int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + \frac{du(t)}{dt}^\top R \frac{du(t)}{dt} \right] dt \\ 
 				\text{subject to} \quad & \dot{x} = G(x, t, \theta; \Xi), \\ 
@@
 				& P(t) \in \left\{100, 125, 150, 175, 200\right\} \text{bar}, \\ 
-				%& R = \begin{bmatrix} 10^{-1} & 0 \ 0 & 10^{-2} \end{bmatrix}, \\ 
-				%& u(t) = \begin{bmatrix} \dfrac{dF(t)}{dt} \ \dfrac{dT^{\text{in}}(t)}{dt} \end{bmatrix}, \\
 				& 30^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\ 
-				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5} 
+				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5} \\
+				& R = \begin{bmatrix} 0.1 & 0 \\ 0 & 0.01 \end{bmatrix} \\ 
+				& \frac{du(t)}{dt} = \begin{bmatrix} \dfrac{dF(t)}{dt} \\ \dfrac{dT^{\text{in}}(t)}{dt} \end{bmatrix}
 				\end{aligned} 

### 2024-11-16 Sections/Results_DOE.tex
16.11

@@
 	For each pressure case, the profiles with the lowest value of the objective function are further analysed.
-As shown in Figure \ref{fig:profiles_T}, all the inlet temperature profiles follow the same pattern.
-Initally, the system starts from the highest temperature (upper control bound) and gradually decreasing to lowest temperatures (lower control bound).
+As shown in Figure \ref{fig:profiles_T}, the dynamic behavior of the inlet temperature ($T^{in}$) for various cases in a supercritical CO2 extraction process.
+The initial temperature starts uniformly at $40~^\circ C$ for all cases but evolves differently depending on the operating conditions.
+These results underscore the sensitivity of supercritical CO$_2$ properties to control parameters such as temperature, particularly near the critical point.
+This observation aligns with the phenomenon that supercritical fluids exhibit properties like density and viscosity undergo strong non-linear changes around the critical point.
+At 200 bar the
 

### 2024-11-16 SFE_DOE_Chamomile_modified/CheckSimulation.m

@@ -1,0 +1,219 @@
+startup;
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
+
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+import casadi.*
+
+excel_file = 'Chamomile_Di_Gamma_2.xls';
+%rng(69)
+
+%%
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('dataset_2.xlsx');
+%Q_RBF = readmatrix('Q_RBF.txt');
+%Q_FP  = readmatrix('Q_FP.txt');
+
+%% Create the solver
+Iteration_max               = 0;                                         % Maximum number of iterations for optimzer
+%Time_max                    = 17;                                           % Maximum time of optimization in [h]
+
+nlp_opts                    = struct;
+%nlp_opts.ipopt.max_iter     = Iteration_max;
+%nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+nlp_opts.ipopt.hessian_approximation ='limited-memory';
+
+%% Load paramters
+m_total                 = 3.0;
+
+% Bed geometry
+before                  = 0.04;                                             % Precentage of length before which is empty
+bed                     = 0.92;                                              % Percentage of length occupied by fixed bed
+
+% Set time of the simulation
+PreparationTime         = 0;
+ExtractionTime          = 600;
+timeStep                = 5;                                                % Minutes
+OP_change_Time          = 10; 
+Sample_Time             = 5;
+
+simulationTime          = PreparationTime + ExtractionTime;
+
+timeStep_in_sec         = timeStep * 60;                                    % Seconds
+Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+Time                    = [0 Time_in_sec/60];                               % Minutes
+
+N_Time                  = length(Time_in_sec);
+
+SAMPLE                  = Sample_Time:Sample_Time:ExtractionTime;
+
+OP_change               = 0:OP_change_Time:ExtractionTime-OP_change_Time;
+
[…]

### 2024-11-16 SFE_DOE_Chamomile_modified/MD.m

@@ -12,11 +12,11 @@ function [] = MD(P, N_exp, N_core)
     N                       = 5;
     
     %% Create the solver
-    Iteration_max               = 200;                                         % Maximum number of iterations for optimzer
-    %Time_max                    = 3;                                           % Maximum time of optimization in [h]
+    %Iteration_max               = 200;                                         % Maximum number of iterations for optimzer
+    Time_max                    = 24;                                           % Maximum time of optimization in [h]
     
     nlp_opts                    = struct;
-    nlp_opts.ipopt.max_iter     = Iteration_max;
+    %nlp_opts.ipopt.max_iter     = Iteration_max;
     %nlp_opts.ipopt.max_cpu_time = Time_max*3600;
     nlp_opts.ipopt.hessian_approximation ='limited-memory';
     
@@ -211,7 +211,7 @@ function [] = MD(P, N_exp, N_core)
     COST_0  = full(GG(T0, F0 ));
     COST    = full(GG(HH_1, HH_2 ));
   
-    FY_FP   = Function('FY_FP',{T0homog, Flow},{XX_FP(end,:)});
+    FY_FP   = Function('FY_FP',{T0homog, Flow},{yy_FP});
     Y_FP_0  = full(FY_FP(T0, F0));
     Y_FP    = full(FY_FP(HH_1, HH_2));
 

### 2025-01-11 Article_Design_of_Experiment-Chamomile.tex
30.10
11.01

@@
 \subsection{Optimal design of experiment} \label{CH: DOE}
-\subfile{Sections/Optimal_design_of_experiment}
+\subfile{Sections/DOE}
 
@@
 \section{Conclusions} \label{CH: Conclusion}
-This paper introduces the D-optimal experimental design (D-OED) as a model-based method for finding an experimental procedure in chemical engineering problems.
-D-OED forms the objective function, which can be interpreted as minimising the volume of uncertainty ellipsoid.
-Compared to the classical formulation of D-OED, a penalty term was introduced to the cost function to prevent infeasibly rapid changes in operating conditions or bang-bang type control.
-The method is demonstrated through a case study on supercritical extraction.
-This work aims to design an experiment to improve the precision of the correlation for $D_i$.
-While the original experiments were conducted under constant operating conditions, this work looks for an experimental procedure with dynamically changing operating conditions.
-In such a case, the D-OED solution can also be used for model validation.
+This paper introduce the D-optimal experimental design (D-OED) as a model-based method for determining optimal experimental procedures in chemical engineering problems.
+D-OED optimizes an objective function, which can be geometrically interpreted as minimizing the volume of the uncertainty ellipsoid, thereby maximizing the precision of parameter estimates.
+Compared to the classical formulation of D-OED, this work introduces a penalty term to the cost function to prevent unrealistic rapid changes in operating conditions, ensuring practical feasibility in experimental implementation.
+The method is demonstrated through a case study on supercritical extraction, focusing on designing experiments to improve the precision of the correlation for the diffusivity coefficient $D_i$.
+While the original experiments were conducted under constant operating conditions, this study explores dynamically changing operating conditions, highlighting the potential of D-OED solutions for both parameter estimation and model validation.
 
-The analysis was repeated for multiple pressure values, and the obtained optimal profiles of inlet temperature and mass flow rate were similar across all cases.
-The resulting yield curves exhibit wavy patterns due to the relationship between the Hessian and the curvature of a multi-variable function.
-The analysis of the yield curves and scatter plots reveals that applying the same experimental strategy at different operating conditions results in varying amounts of information being collected.
-Consequently, it is concluded that the operating conditions should always be carefully chosen to conduct the most informative experiments.
-This is because the physical properties of CO$_2$ vary less at pressures far from the critical point, meaning that the same set of controls has less impact on the system at high pressures than at low pressures.
+The analysis was conducted for multiple pressure cases, and the optimal mass flow rate profiles were similar across all instances.
+The inlet temperature profiles show different patterns, but all of them start with high temperature and decrease in the second half of the batch.
+The resulting yield curves exhibit distinct wavy patterns, which can be explained through the relationship between the Hessian matrix and the Gaussian curvature of a multi-variable function.
+The determinant of the Fisher information matrix, central to the D-optimality criterion, is proportional to the Gaussian curvature of the parameter manifold.
+This curvature reflects the system's sensitivity to parameter changes and is maximized by the D-OED method.
+The observed wavy behavior of the yield curves is thus a manifestation of the high-curvature regions identified by the optimization, where the system's response to experimental conditions is most informative.
+
+Further analysis of the yield curves and scatter plots reveals that the informativeness of experiments varies significantly across different operating conditions.
+This variation depends on the physical properties of CO$_2$, which strongly change around the critical point.
+Consequently, it is concluded that operating conditions must be carefully selected to the specific regime of interest to maximize the information gained.
+This observation emphasizes the importance of aligning experimental strategies with the system's underlying physical properties and model structure.
 
@@
 %% Loading bibliography style file
+\clearpage
 \newpage
@@
 
+\clearpage
 \newpage

### 2025-01-11 Sections/Results_DOE.tex
11.01

--- 2024-07-09 Sections/Results_DOE.tex
@@
 
-	\label{CH: Results}
-
-	To identify the global solution of Equations \ref{EQ:Formulation_1}, the optimization problem is solved multiple times, each starting from a random initial solution.
-Figure \ref{fig:scatter_T} compares the initial and final values of the cost function across multiple optimization runs.
-The shaded area spans from the smallest to the third smallest final values of the objective function.
-The black curves on the left and below the scatter plot represent the distributions of the initial and final cost function values, respectively.
-From Figure \ref{fig:scatter_T}, it can be observed that multiple local solutions exist for Case 1.
-The solution with the lowest cost function value is considered the global solution.
+	To identify the global solution for Equations \ref{EQ:Formulation_2}, the optimization problem is solved multiple times, each run starting from a random initial solution sampled from a uniform distribution.
+Figure \ref{fig:scatter} compares the initial and final cost function values across multiple optimization runs for all pressure cases.
+The solution with the lowest cost function value is considered the global solution for each case.
 
@@
 		\centering
-		\includegraphics[width=\columnwidth]{Figures/Results/scatter_T.png}	
+		\includegraphics[width=\columnwidth]{Figures/Results/scatter.png}	
 		\caption{Initial vs final values of the cost function}
-		\label{fig:scatter_T}
+		\label{fig:scatter}
 	\end{figure}
 
-	The optimal profiles of inlet temperature and mass flow rate are presented in Figure \ref{fig:profile_T}.
-One of the independent parameters in the analysed correlation is the mass flow rate, which is directly modified several times during the experiment.
-The second independent parameter is the Reynolds number, which can be affected by changes in the thermodynamic properties of the fluid.
-The thermal properties of CO$_2$ between $30^\circ$C and $40^\circ$C, assuming a constant pressure of 150 bar, vary only slightly.
-For instance, the dynamic viscosity changes from 67 to $80 \times 10^{-6}$ Pa$\cdot$s.
-The obtained profile of the inlet temperature shows minimal variation, suggesting a limited influence of inlet temperature on the extraction yield.
-Given the narrow operational window for inlet temperature at constant pressure, the mass flow rate becomes the primary variable to control.
+	From Figure \ref{fig:scatter}, it is evident that multiple local solutions exist.
+By analyzing locations of the clusters in Figure \ref{fig:scatter}, it can be concluded that experiments conducted near the critical point provide more information regarding the correlation than those conducted farther from it.
+For each pressure case, the profiles with the lowest value of the objective function are further analysed.
+The closer the pressure is to the critical point, the larger the deviations in the physical properties of $CO_2$ caused by changes in the controls, leading to greater variation in the Reynolds number, and consequently to more informative experiments.
 
-	\begin{figure}[h!]
+	As presented in Figure \ref{fig:profiles_F}, all mass flow rate profiles initially stay at a minimum value, persisting for 100 to 150 minutes, depending on the pressure.
+Subsequently, a step-like increase in mass flow rate is observed, with the onset occurring earlier at higher pressures.
+Between 250 and 300 min, the mass flow rate stabilizes at value of the upper bound.
+
+	\begin{figure}[t!]
 		\centering
-		\includegraphics[width=\columnwidth]{Figures/Results/Profile_T_1.png}	
-		\caption{Optimal temperature and mass flow rate profiles}
-		\label{fig:profile_T}
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=\columnwidth]{Figures/Results/Profile_F.png}	
+			\caption{Optimal mass flow rate profiles}
+			\label{fig:profiles_F}
+		\end{subfigure}%
+		\par\bigskip % force a bit of vertical whitespace
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=\columnwidth]{Figures/Results/Profile_T.png}	
+			\caption{Optimal inlet temperature profile}
+			\label{fig:profiles_T}
+		\end{subfigure}
+		\par\bigskip % force a bit of vertical whitespace
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=\columnwidth]{Figures/Results/yield.png}	
+			\caption{Optimal yield profiles}
+			\label{fig:profiles_y}
+		\end{subfigure}
+		\caption{Results of the optimization problem}
 	\end{figure}
 
-	Similar to Case 1, Case 2 is solved multiple times starting from random initial solutions to identify the global solution.
-Figure \ref{fig:scatter_P} summarizes the changes in the objective function values across all optimization runs.
-It is evident that both the initial and final values of the cost function are significantly lower than any values obtained in Case 1.
-In Case 2, the wider operating range leads to more significant changes in the physical properties of CO$_2$ compared to Case 1.
-For example, the kinematic viscosity of CO$_2$ ranges from $48 \cdot 10^{-6}$ (at $40^\circ$C and 100 bar) to $90 \cdot 10^{-6}$ Pa$\cdot$s (at $30^\circ$C and 200 bar).
-The greater variability in pressure induces a more complex system response, including temperature variations, resulting in lower values of the objective function compared to Case 1.
+	Figure \ref{fig:profiles_T} shows the optimal profiles of the inlet temperature ($T^{in}$) for various pressure cases in the supercritical CO$_2$ extraction process.
+Initially, the $T^{in}$ remains constant at approximately $40~^\circ C$ for all pressures, indicating a stable starting condition for the system.
+The temperature decreases after about 300 min, but the exact time slightly varies depending on the pressure.
+This decline is rapid for lower pressures and gradual for higher pressures.
+The blue curve (100 bar) exhibits the sharpest temperature drop, while the green curve (200 bar) demonstrates a slower and more gradual decline.
+At lower pressures, the final temperature reaches the lower bound and remains steady until the end of the batch.
+In contrary, the higher pressure cases result in a less significant temperature reduction.
+Moreover, the system does not reach steady operating conditions, as the inlet temperature profile does not flatten by the end of the process.
 
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[width=\columnwidth]{Figures/Results/scatter_P.png}	
-		\caption{Initial vs final values of the cost function}
-		\label{fig:scatter_P}
-	\end{figure}
+	Figure \ref{fig:profiles_y} depicts the predicted yield curves.
+A closer examination of the yield and scatter plots reveals that the most informative experiments do not necessarily correspond to those with the highest yield.
+When the D-optimality criterion is applied, the aim is to maximize the determinant of the Fisher information matrix across the experimental design space.
+This approach identifies conditions that amplify variations in observed responses, particularly in regions with high sensitivity to parameter changes.
+As a result, the yield curve may display a "wavy" pattern, characterized by oscillations rather than a smooth, monotonic trend.
+These fluctuations arise from increased multiple critical points—local maxima, minima, or saddle points—on the response surface.
+By maximizing the sum of determinants of the Fisher information matrix, the experimental design prioritizes regions of high curvature, where the response changes sharply.
 
-	The optimal profiles of pressure and mass flow rate are presented on Figure \ref{fig:profile_P}.
-Similarly to case 1, only few changes in the mass flow rate are observed in the plot.
-In contrary to the inlet temperature, the pressure changes are frequently applied in the case 2.
+	Alternatively, the D-optimality problem can be understood through the concept of Gaussian curvature.
+In this view, the experimental design shapes the parameter space of a model into a manifold with local geometry defined by the Fisher information matrix.
+The D-optimality condition maximizes the determinant of this matrix, which geometrically corresponds to maximizing the product of the principal curvatures of the manifold at a given point.
+This determinant is directly proportional to the Gaussian curvature, linking experimental design to the geometry of the parameter space.
+The determinant of the Fisher information matrix can be interpreted as a measure of the "volume element" on the parameter manifold, with higher values indicating regions of greater local curvature.
+By maximizing this determinant, the parameter manifold is locally as curved as possible, which explains the wavy behavior of the yield curves.
 
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[width=\columnwidth]{Figures/Results/Profile_P_1.png}	
-		\caption{Optimal pressure and mass flow rate profiles}
-		\label{fig:profile_P}
-	\end{figure}
+	The results and observations discussed in this article are local and should be considered valid only for the model given by \citet{Sliczniuk2024}.
+Although general conclusions about the curvature of the yield curve are independent of a process model, a completely different set of control profiles should be expected if the same technique is applied to a different model.
+Such strong dependence on a model is one of the most significant limitations of this work.
+Moreover, the model predicts the dataset in the region, which has not been validated during previous experiments.
+One hand this leaves a room for model validation, on the other hand the obtained set of data points might differs from the predictions.
+In such a case, further improvement of the model is necessary.
 

### 2025-01-11 SFE_DOE_Chamomile_modified/MD.m

@@ -1,9 +1,9 @@
 function [] = MD(P, N_exp, N_core)
-    %initParPool
+    initParPool
 
     %addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-    addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
-    %addpath('casadi_folder')
+    %addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+    addpath('casadi_folder')
     import casadi.*
 
     %%
@@ -12,11 +12,11 @@ function [] = MD(P, N_exp, N_core)
     N                       = 5;
     
     %% Create the solver
-    %Iteration_max               = 200;                                         % Maximum number of iterations for optimzer
-    Time_max                    = 24;                                           % Maximum time of optimization in [h]
+    Iteration_max               = 300;                                         % Maximum number of iterations for optimzer
+    %Time_max                    = 3;                                           % Maximum time of optimization in [h]
     
     nlp_opts                    = struct;
-    %nlp_opts.ipopt.max_iter     = Iteration_max;
+    nlp_opts.ipopt.max_iter     = Iteration_max;
     %nlp_opts.ipopt.max_cpu_time = Time_max*3600;
     nlp_opts.ipopt.hessian_approximation ='limited-memory';
     
@@ -179,7 +179,7 @@ function [] = MD(P, N_exp, N_core)
     [xx_F]                 = simulateSystem(F_corr , [], x0_FP, Parameters_init_time );
     
     %%
-    sigma = 0.01;
+    sigma = 0.03;
     
     Q_FP_1 = readmatrix('Q_FP_1.txt');
     Q_FP_1 = Q_FP_1(1:3,1:3);
@@ -189,13 +189,17 @@ function [] = MD(P, N_exp, N_core)
     S_FP     = XX_FP(2:end,N_Sample) ;
     
     SS = S_FP * S_FP' ;
-    JJ = -log(myDet(SS./sigma + pinv( Q_FP_1 ) ));
[…]

### 2025-01-11 SFE_DOE_Chamomile_modified/MD_100.sh

@@ -1,0 +1,9 @@
+#!/bin/bash 
+#SBATCH --time=96:00:00
+#SBATCH --mem-per-cpu=2G
+#SBATCH --cpus-per-task=32
+#SBATCH --output=matlab_parallel_100_n.out
+
+module load matlab
+
+srun matlab -nodisplay -r 'MD(100, 32, 32)'

### 2025-01-11 SFE_DOE_Chamomile_modified/MD_125.sh

@@ -1,0 +1,9 @@
+#!/bin/bash 
+#SBATCH --time=96:00:00
+#SBATCH --mem-per-cpu=2G
+#SBATCH --cpus-per-task=32
+#SBATCH --output=matlab_parallel_125_n.out
+
+module load matlab
+
+srun matlab -nodisplay -r 'MD(125, 32, 32)'

### 2025-01-11 SFE_DOE_Chamomile_modified/MD_150.sh

@@ -1,0 +1,9 @@
+#!/bin/bash 
+#SBATCH --time=96:00:00
+#SBATCH --mem-per-cpu=2G
+#SBATCH --cpus-per-task=32
+#SBATCH --output=matlab_parallel_150_n.out
+
+module load matlab
+
+srun matlab -nodisplay -r 'MD(150, 32, 32)'

### 2025-01-11 SFE_DOE_Chamomile_modified/MD_175.sh

@@ -1,0 +1,9 @@
+#!/bin/bash 
+#SBATCH --time=96:00:00
+#SBATCH --mem-per-cpu=2G
+#SBATCH --cpus-per-task=32
+#SBATCH --output=matlab_parallel_175_n.out
+
+module load matlab
+
+srun matlab -nodisplay -r 'MD(175, 32, 32)'

### 2025-01-11 SFE_DOE_Chamomile_modified/MD_200.sh

@@ -1,0 +1,9 @@
+#!/bin/bash 
+#SBATCH --time=96:00:00
+#SBATCH --mem-per-cpu=2G
+#SBATCH --cpus-per-task=32
+#SBATCH --output=matlab_parallel_200_n.out
+
+module load matlab
+
+srun matlab -nodisplay -r 'MD(200, 32, 32)'

### 2025-01-11 SFE_DOE_Chamomile_modified/plot_correlations.m

@@ -35,9 +35,12 @@ hold off
 
 colormap turbo 
 c = colorbar;
+c.Label.String = '$D^R_i~[m^2/s]$';
+c.Label.Interpreter = 'latex';
+c.Label.FontSize = 12;
 set(c,'TickLabelInterpreter','latex');
 
-title('$D^R_i = \max(0, 0.190 -  8.188 \cdot Re + 0.620 \cdot F) \cdot 10^{-13} $')
+title('$D^R_i~[m^2/s] = \max(0, 0.190 -  8.188 \cdot Re + 0.620 \cdot F) \cdot 10^{-13} $')
 subtitle('$R^2 = 0.868$')
 xlabel('Re [-]')
 ylabel('F $\cdot 10^{-5}$ [kg/s]')
@@ -70,9 +73,12 @@ hold off
 
 colormap turbo 
 c = colorbar;
+c.Label.String = '$\Upsilon~[-]$';
+c.Label.Interpreter = 'latex';
+c.Label.FontSize = 12;
 set(c,'TickLabelInterpreter','latex');
 
-title('$\Upsilon = \max(0, 3.158 - 11.922 \cdot Re + 0.686 \cdot F) $')
+title('$\Upsilon~[-] = \max(0, 3.158 - 11.922 \cdot Re + 0.686 \cdot F) $')
 subtitle('$R^2 = 0.823$')
 xlabel('Re [-]')
 ylabel('F $\cdot 10^{-5}$ [kg/s]')

### 2025-01-11 SFE_DOE_Chamomile_modified/plot_results.m

@@ -64,7 +64,7 @@ for ii = 1:numel(PP)
 
     % Plots of controls
     selected_exp  = sort(FinaCost);
-    ind      = find( FinaCost == selected_exp(1) );
+    ind      = find( FinaCost == selected_exp(end) );
     
     %{\
     %subplot(3,1,1)
@@ -127,6 +127,7 @@ for ii = 1:numel(PP)
 %}
 
 end
+%{
 figure(1); legend({'100 bar','125 bar','150 bar','175 bar','200 bar'}, 'Location', 'southwest' ); legend('boxoff')
 exportgraphics(figure(1), ['Profile_T.png'], "Resolution",300); 
 
@@ -138,7 +139,7 @@ exportgraphics(figure(3), ['yield.png'], "Resolution",300);
 
 figure(4); legend({'100 bar','125 bar','150 bar','175 bar','200 bar'}, 'Location', 'northeast' ); legend('boxoff')
 exportgraphics(figure(4), ['diff_yield.png'], "Resolution",300); 
-
+%}
 %%
 %{\
 figure(5)

### 2025-05-20 Article_Design_of_Experiment-Chamomile.tex
20.05

@@
 	\item[\bfseries
-	\ifstrequal{#1}{A}{Latin symbols}{%
+	\ifstrequal{#1}{A}{}{%
 		\ifstrequal{#1}{B}{Greek symbols}{%
@@
 	]}
-
-\usepackage{csvsimple}
+\newcommand{\nomunit}[1]{%
+	\renewcommand{\nomentryend}{\hspace*{\fill}#1}}
 
@@
 This study investigates the process of chamomile oil extraction from flowers.
-A parameter-distributed model consisting of a set of partial differential equations is used to describe the governing mass transfer phenomena in a solid-fluid environment under supercritical conditions using carbon dioxide as a solvent.
+A parameter-distributed model consisting of a set of partial differential equations is used to describe the governing mass transfer phenomena in a{ \color{blue}cylindrical packed bed with solid chamomile particles} under supercritical conditions using carbon dioxide as a solvent.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-The empirical correlations used in the model are based on the set of laboratory experiments performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The empirical correlations used in the model are based on the set of laboratory experiments performed under multiple constant operating conditions: ${\color{blue}31} - 40~^\circ$C, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
 A model-based design of experiments with D-optimality criterion is applied to improve the precision of the correlation parameters by designing a new dynamic experiment.
@@
 %% Loading bibliography style file
-\clearpage
-\newpage
+%\clearpage
+%\newpage
 %\bibliographystyle{model1-num-names}
@@
 
-\nomenclature[A]{\(P\)}{Pressure}
-\nomenclature[A]{\(T\)}{Temperature}
-\nomenclature[A]{\(T^{in}\)}{Inlet temperature}
-\nomenclature[A]{\(T^{out}\)}{Outlet temperature}
-\nomenclature[A]{\(F\)}{Mass flow rate}
-\nomenclature[A]{\(u\)}{Superfical velocity}
-\nomenclature[A]{\(v\)}{Linear velocity}
-\nomenclature[A]{\(z\)}{Spatial direction}
-\nomenclature[A]{\(e\)}{Internal energy}
-\nomenclature[A]{\(e^y\)}{Output error}
-\nomenclature[A]{\(h\)}{Enthalpy}
-\nomenclature[A]{\(t\)}{Time}
-\nomenclature[A]{\(t_f\)}{Total extraction time}
-\nomenclature[A]{\(t_0\)}{Inital extraction time}
-\nomenclature[A]{\(A\)}{Total cross section of the bed}
-\nomenclature[A]{\(A_f\)}{Cross section of the bed accupied by the fluid}
-\nomenclature[A]{\(c_f\)}{Concentration of solute in fluid phase}
-\nomenclature[A]{\(c_{f0}\)}{Inital concentration of solute in fluid phase}
-\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface}
-\nomenclature[A]{\(c_s\)}{Concentration of solute in solid phase}
-\nomenclature[A]{\(c_{s0}\)}{Inital concentration of solute in solid phase}
-\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface}
-\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore}
-\nomenclature[A]{\(c_{pf}\)}{Concentration of solute in the pore opening}
-\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficeint}
-\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term}
-\nomenclature[A]{\(L\)}{Length of fixed bed}
-\nomenclature[A]{\(j\)}{Objective function}
-\nomenclature[A]{\(j_{ml}\)}{Maximum Likelihood}
-\nomenclature[A]{\(S\)}{Sensitivity equations}
-\nomenclature[A]{\(Q\)}{Weighting matrix}
-\nomenclature[A]{\(R\)}{Control cost matrix}
+\nomenclature[A]{\(P\)}{Pressure \nomunit{bar}}
+\nomenclature[A]{\(T\)}{Temperature \nomunit{K}}
+\nomenclature[A]{\(T_{in}\)}{Inlet temperature \nomunit{K}}
+\nomenclature[A]{\(T_{out}\)}{Outlet temperature \nomunit{K}}
+\nomenclature[A]{\(F\)}{Mass flow rate \nomunit{kg/s}}
+\nomenclature[A]{\(u\)}{Superficial velocity \nomunit{m/s}}
+\nomenclature[A]{\(v\)}{Linear velocity \nomunit{m/s}}
+\nomenclature[A]{\(z\)}{Spatial direction \nomunit{m}}
+\nomenclature[A]{\(e\)}{Internal energy \nomunit{J/kg}}
+%\nomenclature[A]{\(e^y\)}{Output error}
+\nomenclature[A]{\(h\)}{Enthalpy \nomunit{kJ/kg}}
+\nomenclature[A]{\(t\)}{Time \nomunit{s}}
+\nomenclature[A]{\(t_f\)}{Total extraction time \nomunit{s}}
+\nomenclature[A]{\(t_0\)}{Initial extraction time \nomunit{s}}
+\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{m$^2$}}
+\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{m$^2$}}
+\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{m$^2$/s}}
+\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/m$^3$/s}}
+\nomenclature[A]{\(L\)}{Length of the fixed bed \nomunit{m}}
+\nomenclature[A]{\(j\)}{Objective function \nomunit{-}}
+\nomenclature[A]{\(j_{ml}\)}{Maximum Likelihood \nomunit{-}}
+\nomenclature[A]{\(S\)}{Sensitivity equations \nomunit{-}}
+\nomenclature[A]{\(Q\)}{Weighting matrix \nomunit{-}}
+\nomenclature[A]{\(R\)}{Control cost matrix \nomunit{-}}
 %\nomenclature[A]{\(\textbf{G}\)}{Augumented system}
@@
 %\nomenclature[A]{\(\mathcal{L}\)}{Log-likelihood function}
-\nomenclature[A]{\(l\)}{Characterisitic diemsinon of particles}
-\nomenclature[A]{\(D_i\)}{Interanl diffusion coefficient}
-\nomenclature[A]{\(D_i^R\)}{Reference value of interanl diffusion coefficient}
-\nomenclature[A]{\(r\)}{Particle radius}
-\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient}
-\nomenclature[A]{\(k_m\)}{Mass partition coefficient}
-\nomenclature[A]{\(y\)}{Extraction yield}
-\nomenclature[A]{\(Y\)}{Yield measurment}
+\nomenclature[A]{\(l\)}{Characteristic dimension of particles \nomunit{m}}
+\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{m$^2$/s}}
+\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{m$^2$/s}}
+\nomenclature[A]{\(r\)}{Particle radius \nomunit{m}}
+\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient \nomunit{-}}
+\nomenclature[A]{\(k_m\)}{Mass partition coefficient \nomunit{-}}
+\nomenclature[A]{\(y\)}{Extraction yield \nomunit{g}}
+%\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
 \nomenclature[A]{\(x\)}{State vector}
@@
 
-\nomenclature[B]{\(\rho_f\)}{Fluid density}
-\nomenclature[B]{\(\Phi\)}{Bed porosity}
-\nomenclature[B]{\(\rho_s\)}{Bulk density of solid}
-\nomenclature[B]{\(\mu\)}{Sphericity coefficient}
-\nomenclature[B]{\(\pi\)}{Probability desnsity}
-\nomenclature[B]{\(\gamma\)}{Decaying function}
-\nomenclature[B]{\(\Upsilon\)}{Decay coefficient}
-\nomenclature[B]{\(\Theta\)}{Paramter space}
-\nomenclature[B]{\(\theta\)}{vector of unknown parameters}
-\nomenclature[B]{\(\epsilon\)}{Unobervable error}
-\nomenclature[B]{\(\sigma\)}{Standard deviation}
-\nomenclature[B]{\(\Sigma\)}{Covariance matrix}
-\nomenclature[B]{\(\xi\)}{Vector of experimental condtions}
-\nomenclature[B]{\(\Xi\)}{Matrix of experimental condtions}
+\nomenclature[B]{\(\rho_f\)}{Fluid density\nomunit{kg/m$^3$}}
+\nomenclature[B]{\(\Phi\)}{Bed porosity \nomunit{-}}
+\nomenclature[B]{\(\rho_s\)}{Bulk density of solid\nomunit{kg/m$^3$}}
+\nomenclature[B]{\(\mu\)}{Sphericity coefficient \nomunit{-}}
+\nomenclature[B]{\(\pi\)}{Probability desnsity \nomunit{-}}
+\nomenclature[B]{\(\gamma\)}{Decaying function \nomunit{-}}
+\nomenclature[B]{\(\Upsilon\)}{Decay coefficient \nomunit{-}}
+\nomenclature[B]{\(\Theta\)}{Paramter space \nomunit{-}}
+\nomenclature[B]{\(\theta\)}{vector of unknown parameters \nomunit{-}}
+\nomenclature[B]{\(\epsilon\)}{Unobervable error \nomunit{-}}
+\nomenclature[B]{\(\sigma\)}{Standard deviation \nomunit{-}}
+\nomenclature[B]{\(\Sigma\)}{Covariance matrix \nomunit{-}}
+\nomenclature[B]{\(\xi\)}{Vector of experimental condtions \nomunit{-}}
+\nomenclature[B]{\(\Xi\)}{Matrix of experimental condtions \nomunit{-}}
 

### 2025-05-20 Sections/DOE.tex
20.05

--- 2024-10-30 Sections/DOE.tex
@@
 
-	Building on the work of\citet{Walter2010} and \citet{Himmelblau1970}, Bayes' Theorem can be employed to define a general cost function:
+	Building on the work of \citet{Walter2010} and \citet{Himmelblau1970}, the Bayes' Theorem can be employed to define a general cost function:
 
@@
 
-	The aim of experimental design is to maximize the posterior probability of estimating $\theta$ ($p\left(\theta \mid Y, \Xi \right)$) given the prior distribution of $\theta$ ($p(\theta)$) obtained from previous experiments, and the likelihood of obtaining observations $Y$ given $\theta$ and experimental conditions $\Xi$.
+	The aim of experimental design is to maximize the posterior probability of estimating $\theta$ ($p\left(\theta \mid Y, \Xi \right)$) given the prior distribution of $\theta$ ($p(\theta)$) obtained from previous experiments, and the likelihood of obtaining observations $Y~\left(p\left(Y \mid \theta, \Xi\right)\right)$ given $\theta$ and experimental conditions $\Xi$.
 The new observations $Y$, under a set of experimental conditions $\Xi$, are assumed to be normally distributed around the model output $y$, with measurement error covariance $\Sigma_Y$.
 Similarly, $\theta$ is assumed to be normally distributed around the true parameter values $\hat{\theta}$, with covariance matrix $\Sigma_\theta$ estimated from previous experiments.
-The probabilities can be defined as
+These probabilities are:
 
@@
 		\begin{align} 
-			p\left(Y \mid \theta, \Xi \right) &= \frac{|\Sigma_Y|^{-1/2}}{\left(2\pi\right)^{n_Y/2}} \exp\left( -\frac{1}{2} \left(Y - y\right)^\top \Sigma_Y^{-1} \left(Y - y\right) \right), \\ 
-			p\left(\theta\right) &= \frac{|\Sigma_\theta|^{-1/2}}{\left(2\pi\right)^{n_\theta/2}} \exp\left( -\frac{1}{2} \left(\theta - \hat{\theta}\right)^\top \Sigma_\theta^{-1} \left(\theta - \hat{\theta}\right) \right),
+			p\left(Y \mid \theta, \Xi \right) &= \frac{|\Sigma_Y|^{-1/2}}{\left(2\pi\right)^{n_Y/2}} \exp\left( -\frac{1}{2} \left(Y - y\right)^\top \Sigma_Y^{-1} \left(Y - y\right) \right) \\
+			p\left(\theta\right) &= \frac{|\Sigma_\theta|^{-1/2}}{\left(2\pi\right)^{n_\theta/2}} \exp\left( -\frac{1}{2} \left(\theta - \hat{\theta}\right)^\top \Sigma_\theta^{-1} \left(\theta - \hat{\theta}\right) \right)
 		\end{align}
@@
 	By linearizing the model output around $\hat{\theta}$, the model output becomes: $y = y(\hat{\theta}) + J \Delta_\theta$, where $J = \frac{\partial y(\hat{\theta})}{\partial \theta}$ is the Jacobian matrix evaluated at $\hat{\theta}$, and $\Delta_\theta = \theta - \hat{\theta}$.
-To simplify the equation, we introduce the residual term $\Delta_y = Y - y(\hat{\theta})$.
+To simplify the equation, the residual term $\Delta_y = Y - y(\hat{\theta})$ is introduced.
 Substituting these into the expression for $\ln p\left(\theta \mid Y, \Xi \right)$:
@@
 	The Fisher Information $\mathcal{F}$ measures the amount of information that an observable random variable carries about an unknown parameter of the distribution that models the random variable.
-It is related to the negative expected value of the second derivative (or curvature) of the log-likelihood function with respect to the parameter, providing a measure of how "sensitive" the likelihood is to changes in the parameter value.
+It is related to the negative expected value of the second derivative of the log-likelihood function with respect to the parameter, providing a measure of how "sensitive" the likelihood is to changes in the parameter value.
 
@@
 	Since the likelihood is Gaussian and linearized, the second derivative of the log-likelihood with respect to $\theta$ simplifies to $J^\top \Sigma_Y^{-1} J$, and its negative expected value yields the same expression because the expectation of the Hessian is constant in this linear approximation.
-	\begin{comment}
 
-	Under the hypotheses that:
-
-	\begin{itemize}
-		\item The set of all data vectors $Y$ with $p(Y \mid \theta, \Xi) > 0$ does not depend on $\theta$.
-		\item The partial derivatives $\frac{\partial p(Y \mid \theta, \Xi)}{\partial \theta_i}$ for $i=1,2,...,n_\theta$ are absolutely integrable.
-		\item The expected value $\mathop{\mathbb{E}}_{Y \mid \theta, \Xi} \left[ \frac{\partial^2 \ln p \left( Y \mid \theta, \Xi \right)}{\partial \theta \partial \theta^\top} \right]$ exists and is invertible.
-	\end{itemize}
-
-	\end{comment}
 	The Cramér-Rao inequality provides that the covariance of any unbiased estimator $\hat{\theta}$ satisfies:
@@
 
-	In other words, the precision with which we can estimate $\theta$ is limited by the Fisher Information of the likelihood function.
+	The precision with which a parameter $\theta$ can be estimated is limited by the Fisher Information of the likelihood function.
 Based on the Cramér-Rao inequality, the Fisher Information matrix can be used to calculate the covariance matrices associated with maximum-likelihood estimates.
@@
 
-	A general class of design of experiments (DOE) optimality criteria is given by:
-
-	{\footnotesize 
-		\begin{align} 
-			\kappa_k\left( A^{-1}(\theta) \right) &= \left[ \frac{1}{n_\theta} \operatorname{trace}\left( Q A^{-1}(\theta, \Xi) Q^\top \right)^k \right]^{1/k} & \text{if} \det A^{-1} \neq 0, \nonumber \\ 
-			\kappa_k\left( A^{-1}(\theta) \right) &= \infty & \text{if} \det A^{-1} = 0
-		\end{align} }
-
-	where $Q$ is a weighting matrix. The special case $k=1$ corresponds to the L-optimality cost function:
-
-	{\footnotesize \begin{equation} j_L(\Xi) = \operatorname{trace} \left( Q A^{-1}(\theta, \Xi) Q^\top \right) \end{equation} }
-
-	Choosing $Q = \mathbf{I}_{n\theta}$ corresponds to the A-optimality cost function.
-An A-optimal experiment minimizes the sum of the variances of the parameter estimates (i.e., the trace of the covariance matrix).
-When $Q$ is diagonal with $[Q]_{ii} = 1/\theta_i$, this corresponds to weighting the parameters inversely by their magnitude, which is associated with relative precision.
-
-	Selecting $Q$ as a row vector results in C-optimality, which focuses on linear combinations of parameters.
-Setting $Q = \mathbf{I}_{n\theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalue of the covariance matrix $A^{-1}(\theta, \Xi)$, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.
-
-	The most commonly used criterion is the D-optimality, which involves $k = 0$ and $Q = \mathbf{I}_{n\theta}$, requiring the minimization of $\det A^{-1}(\theta, \Xi)$, or equivalently, maximization of:
-
-	{\footnotesize \begin{equation} j_D(\Xi) = \det A(\theta, \Xi) \end{equation} }
-
-	Since $\det A(\theta, \Xi) = 1 / \det A^{-1}(\theta, \Xi)$, maximizing $\det A$ is equivalent to minimizing $\det A^{-1}$.
-
-	The D-optimality criterion originates from the geometric interpretation of the determinant.
-A two-dimensional matrix with real number entries can represent two linear maps: one mapping the standard basis vectors to the rows and the other to the columns.
-In both cases, the images of the basis vectors form a parallelogram that represents the image of the unit square under the mapping.
-The absolute value of the determinant is the area of this parallelogram, reflecting the scale factor by which the matrix transforms areas.
-The signed value of the determinant indicates the oriented area of the parallelogram, which is negative when the angle from the first to the second defining vector is clockwise.
-In the multi-dimensional case, the matrix maps the n-cube to an n-dimensional parallelotope.
-The determinant provides the signed n-dimensional volume of this parallelotope, describing the volume scaling factor of the linear transformation produced by the matrix.
-Based on this geometric interpretation, a D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.
-Figure \ref{fig:score_fun} illustrates the graphical representation of different optimality conditions.
-
 	\begin{figure}[!h]
 		\centering
-		\resizebox{0.4\textwidth}{!}{%
+		\resizebox{0.9\columnwidth}{!}{%
 			\begin{tikzpicture}
@@
 
+	A general class of design of experiments (DOE) optimality criteria is given by Equation \ref{EQ:DOE_general}.
+Some of the DOE criterion have graphical interpretation as shown in Figure \ref{fig:score_fun}.
+
+	{\footnotesize 
+		\begin{align} \label{EQ:DOE_general}
+			\kappa_k\left( A^{-1}(\theta) \right) &= \left[ \frac{1}{n_\theta} \operatorname{trace}\left( Q A^{-1}(\theta, \Xi) Q^\top \right)^k \right]^{1/k} & \text{if} \det A^{-1} \neq 0, \nonumber \\ 
+			\kappa_k\left( A^{-1}(\theta) \right) &= \infty & \text{if} \det A^{-1} = 0
+		\end{align} }
+
+	where $Q$ is a weighting matrix. The special case $k=1$ corresponds to the L-optimality cost function:
+
+	{\footnotesize \begin{equation} j_L(\Xi) = \operatorname{trace} \left( Q A^{-1}(\theta, \Xi) Q^\top \right) \end{equation} }
+
+	Choosing $Q = \mathbf{I}_{n\theta}$ corresponds to the A-optimality cost function.
+An A-optimal experiment minimizes the sum of the variances of the parameter estimates (i.e., the trace of the covariance matrix).
+When $Q$ is diagonal with $[Q]_{ii} = 1/\theta_i$, this corresponds to weighting the parameters inversely by their magnitude, which is associated with relative precision.
+
+	Selecting $Q$ as a row vector results in C-optimality, which focuses on linear combinations of parameters.
+Setting $Q = \mathbf{I}_{n\theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalue of the covariance matrix $A^{-1}(\theta, \Xi)$, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.
+
+	The most commonly used criterion is the D-optimality, which involves $k = 0$ and $Q = \mathbf{I}_{n\theta}$, requiring the minimization of $\det A^{-1}(\theta, \Xi)$, or equivalently, maximization of:
+
+	{\footnotesize \begin{equation} j_D(\Xi) = \det A(\theta, \Xi) \end{equation} }
+
+	Since $\det A(\theta, \Xi) = 1 / \det A^{-1}(\theta, \Xi)$, maximizing $\det A$ is equivalent to minimizing $\det A^{-1}$.
+
+	The D-optimality (D-OED) criterion originates from the geometric interpretation of the determinant.
+A two-dimensional matrix with real number entries can represent two linear maps: one mapping the standard basis vectors to the rows and the other to the columns.
+In both cases, the images of the basis vectors form a parallelogram that represents the image of the unit square under the mapping.
+The absolute value of the determinant is the area of this parallelogram, reflecting the scale factor by which the matrix transforms areas.
+The signed value of the determinant indicates the area of the parallelogram, which is negative when the angle from the first to the second defining vector is clockwise.
+In the multi-dimensional case, the matrix maps the n-cube to an n-dimensional parallelotope.
+The determinant provides the signed n-dimensional volume of this parallelotope, describing the volume scaling factor of the linear transformation produced by the matrix.
+Based on this geometrical interpretation, a D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.
+
 	\subsubsection{Problem formulation}
 
-	Details on the process model can be found in [article 1].
-The model's empirical correlations are derived based on laboratory experiments conducted under various but constant operating conditions: $30^\circ\text{C} - 40^\circ\text{C}$, $100 - 200$ bar, and $3.33 \cdot 10^{-5} - 6.67 \cdot 10^{-5}$ kg/s.
-This study employs a model-based design of experiments technique to design an experiment with dynamically changing conditions to improve the precision of the correlation for $D_i$.
+	Details on the process model can be found in \citet{Sliczniuk2024}.
+The model's empirical correlations are derived based on laboratory experiments conducted under various but constant operating conditions: $31 - 40~^\circ\text{C}$, $100 - 200$ bar, and $3.33 \cdot 10^{-5} - 6.67 \cdot 10^{-5}$ kg/s.
+This study employs the process model obtained previously to design a set of supplementary experiments with dynamically changing conditions to improve the precision of the correlation for $D_i$.
+The analyzed correlations consist of three independent variables: mass flow rate, pressure and inlet temperature.
+
+	In this work, the decision variables are the inlet temperature ($T^{\text{in}}$) and mass flow rate ($F$), while the pressure is assumed to remain constant during a batch.
+The optimal design of experiment problem is solved for multiple values of pressure: 100, 125, 150, 175, and 200 bar.
+The initial state is considered isothermal, so $T^0(z) = T^{\text{in}}(t=0)$.
+
 	The decision variables are adjusted every 10 minutes and are kept constant within each interval (piecewise constant controls).
-These controls have lower and upper bounds that match the validated range of the process model detailed in [article 1].
-The sampling time is set to 5 minutes, and the total extraction time is 600 minutes.
-The standard deviation $\sigma^2$ was estimated to be 0.10.
+These controls have lower and upper bounds that match the validated range of the process model detailed by \citet{Sliczniuk2024}.
+The sampling time is assumed to be 5 minutes, and the total extraction time is 600 minutes.
+The standard deviation $\sigma^2$ was estimated to be 0.03.
 
-	The analyzed correlations consist of two independent variables: Reynolds number and mass flow rate.
-The Reynolds number is a function of fluid thermodynamic properties and velocity, and the fluid density can be affected by temperature or pressure changes.
-In this work, the decision variables are the inlet temperature ($T^{\text{in}}$) and mass flow rate ($F$), while the pressure is assumed to remain constant.
-The initial state is considered isothermal, so $T^0 = T^{\text{in}}(t=0)$.
-The optimal design of experiment problem is solved for multiple values of pressure, namely 100, 125, 150, 175, and 200 bar.
-
-	In a real system, the mass flow rate and inlet temperature cannot be changed instantaneously, as they depend on the dynamics of the pump and heat exchanger, respectively.
-To prevent bang-bang-like control between the lower and upper bounds of the decision variables, a penalty term is introduced.
-Similar to many control problems, such as the Linear Quadratic Regulator, a quadratic penalty term is added to the cost function.
+	In a real system, the mass flow rate and inlet temperature cannot be changed instantaneously to any arbitrary value, as they depend on the dynamics of the pump and heat exchanger, respectively.
+To prevent bang-bang type of control, a penalty term is introduced.
+Inspired by control problems, such as the Linear Quadratic Regulator, a quadratic penalty term is added to the cost function.
 This penalty increases the cost function value when there are rapid changes in the decision variables.
-The matrix $R$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$.
+The matrix $\bar{R}$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$.
 The problem formulation is given by Equation \ref{EQ:Formulation_2}.
@@
 		\begin{equation}
-			\begin{aligned} \Xi^* &= \arg \min_{ T^{\text{in}}(t), F(t) } \int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + u(t)^\top R u(t) \right] dt \\ 
-				\text{subject to} \quad & \dot{x} = G(x, t, \theta; \Xi), \\ 
-				& t_0 = 0 \text{min} \\ 
-				& t_f = 600 \text{min} \\ 
-				& T^{0} = T^{\text{in}}(t=0), \\ 
-				& P(t) \in \left\{100, 125, 150, 175, 200\right\} \text{bar}, \\ 
-				%& R = \begin{bmatrix} 10^{-1} & 0 \ 0 & 10^{-2} \end{bmatrix}, \\ 
-				%& u(t) = \begin{bmatrix} \dfrac{dF(t)}{dt} \ \dfrac{dT^{\text{in}}(t)}{dt} \end{bmatrix}, \\
-				& 30^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\ 
-				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5} 
+			\begin{aligned}
+				\Xi^* &= \arg \min_{T^{\text{in}}(t), F(t)} 
+				\int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + 
+				\frac{du(t)^\top}{dt} \, \bar{R} \, \frac{du(t)}{dt} \right] dt, \\
+				\text{subject to:} \quad 
+				& \dot{x} = G(x, t, \theta; \Xi), \\
+				& t_0 = 0 \, \text{min}, \quad t_f = 600 \, \text{min}, \\
+				& T^0 = T^{\text{in}}(t=0), \\
+				& P(t) \in \{100, 125, 150, 175, 200\} \, \text{bar}, \\
+				& 31^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\
+				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5}, \\
+				& \bar{R} = 
+				\begin{bmatrix} 
+					0.1 & 0 \\ 
+					0 & 0.01 
+				\end{bmatrix}, \\
+				& \frac{du(t)}{dt} = 
+				\begin{bmatrix} 
+					\dfrac{dF(t)}{dt} \\ 
+					\dfrac{dT^{\text{in}}(t)}{dt} 
+				\end{bmatrix}.
 			\end{aligned}

### 2025-05-20 Sections/Literature_Review.tex
20.05

@@
 	\citet{Ramandi2011} conducted a study to identify the variables with the greatest influence on the extraction yield of fatty acids from \textit{Borago officinalis L.} flowers using Supercritical Fluid Extraction (SFE).
-A Full Factorial Design was employed as a screening method, resulting in a design matrix of 32 runs ($2^5$) carried out randomly to minimize the impact of extraneous or nuisance variables.
+A Full Factorial Design was employed as a screening method, resulting in a design matrix of 32 runs ($2^5$) carried out randomly to minimize the impact of external factors.
 The low and high values for the factors were selected based on previous research.
-After determining the most significant variables, a Central Composite Design was applied to three factors—temperature, pressure, and modifier volume—to optimize the SFE conditions.
+After determining the most significant variables, a Central Composite Design was applied to three factors—temperature, pressure, and volume of methanol co-solvent to optimize the SFE conditions.
 This allowed for the modeling of the response surface by fitting a second-order polynomial.
@@
 	After an initial dataset has been collected and fitted to a mathematical model, the model undergoes further analysis.
-Additional experiments may be designed and conducted to differentiate between competing models that passed the preliminary tests.
+Additional experiments may be needed to differentiate between competing models that passed the preliminary tests.
 Once inadequate models are rejected, the remaining model may undergo another round of experiment design to enhance the precision of its parameters.

### 2025-05-20 Sections/Model.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\section{Materials and methods} \label{CH: Materials and methods}

	\subsection{Governing equations} \label{CH:Governing_equations_chapter}
	Following the work of \citet{Anderson1995}, the governing equations for a quasi-one-dimensional flow were derived. A quasi-one-dimensional flow refers to a fluid flow scenario assuming that the flow properties are uniformly distributed across any cross-section. This simplification is typically applied when the flow channel's cross-sectional area changes, such as through irregular shapes or partial filling of an extractor. According to this assumption, velocity and other flow properties change solely in the flow direction.

	As discussed by \citet{Anderson2023}, all flows are compressible, but some of them can be treated as incompressible since the velocities are low. This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The assumption allows for removing acoustic waves and large perturbations in density and/or temperature. In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant along the $z-$ direction.

	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}:

	{\footnotesize
		\begin{align}
			\label{EQ: CompressibleEuler_1}
			\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
			\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)   
			\label{EQ: CompressibleEuler_3}
		\end{align}  
	}

	where $\rho_f$ is the density of the fluid, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spatial direction.

	\subsection{Extraction model} \label{CH: Extraction_model}
	\subsubsection{Continuity equation} \label{CH: Continuity}

	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating the function $A_f = A\phi$. This modification distinguishes constant and varying terms, where the varying term accounts for changes in the cross-sectional area available for the fluid. Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:

	{\footnotesize
		\begin{equation} \label{EQ: Continuity_differential}
			\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial z} = 0
		\end{equation}
	}
	where $A$ is the total cross-section of the extractor and $\phi$ describes porosity along the extractor.

	Assuming that {\color{blue}the porosity} and mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial (\rho_f v A \phi )}{\partial z} dz = F \rightarrow F=\rho_f v A\phi
		\end{equation}
	}

	To simplify the system dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$ and $\rho_f$:

	{\footnotesize
		\begin{equation} \label{EQ:Velocity_1}
			v = \cfrac{F}{\rho_f A\phi} 
		\end{equation}
	}

	Similarly, superficial velocity may be introduced:

	{\footnotesize
		\begin{equation} \label{EQ:Velocity_2}
			u = v \phi = \cfrac{F}{\rho_f A }
		\end{equation}
	}

	The fluid density $\rho_f$ can be obtained from the Peng-Robinson equation of state if the temperature and thermodynamic pressure are known along $z$. Variation in fluid density may occur due to pressure or inlet temperature changes. In a non-isothermal case, in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} $\rho_f$ is considered the average fluid density along the extraction column.

	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}

	Equation \ref{Model_fluid} describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to those of the solvent itself. It is also assumed that the thermodynamic pressure remains constant throughout the device. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall. This leads to a uniform velocity profile across any cross-section perpendicular to the axial direction. Thus, the mass balance equation includes convection, diffusion and kinetic terms representing the fluid phase behaviour:

	{\footnotesize
		\begin{equation}
			\label{Model_fluid}
			\frac{\partial c_f}{\partial t}
			+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z}
			= \frac{1-\phi}{\phi} r_e
			+ \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right)
		\end{equation}
	}

	where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the axial dispersion coefficient.

	\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}

	As given by Equation \ref{Model_solid}, the solid phase is considered stationary, without convection and diffusion terms in the mass balance equation. Therefore, the only significant term in this equation is the kinetic term of Equation \ref{Model_kinetic_basic}, which connects the solid and fluid phases. For simplicity, the extract is represented by a single pseudo-component:

	{\footnotesize
		\begin{equation} 
			\label{Model_solid}
			%		{\scriptsize\begin{equation}
					\cfrac{\partial c_s}{\partial t} = \underbrace{ -  r_e }_{\text{Kinetics}}
			\end{equation} }

			\subsubsection{Kinetic term} \label{CH: Kinetic}

			As the solvent flows through the fixed bed, CO$_2$ molecules diffuse into the pores, adsorb on the inner surface and form a film due to solvent-solid matrix interactions. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore and the film into the bulk. Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$, and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$ for the solid and fluid phases, respectively. The concentration of the solutes in the fluid phase in the centre of the pore is denoted as $c_p$. As the solute diffuses through the pore, its concentration changes, reaching $c_{pf}$ at the opening. Then, the solute diffuses through the film around the particle and reaches bulk concentration $c_f$. The two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be determined from the relationship between the solute concentration in one phase and its equilibrium concentration.

			\begin{figure}[h!]
				\centering
				\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=0.85\columnwidth]{Figures/SFE_PFD.drawio.png}	
				\caption{Mass transfer mechanism.}
				\label{fig: SFE_Mechanism}
			\end{figure}

			\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between the concentration of the solute in the bulk, $c_f$, and in the centre of the pore, $c_p^*$. The concentration $c_p^*$ is in equilibrium with $c_s$ according to the equilibrium relationship. The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$. In contrast, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$. As given by Equation \ref{Model_kinetic_basic}, the concentration $c_p^*$ is determined by the equilibrium relationship with $c_f$:

			{\footnotesize
				\begin{equation} \label{Model_kinetic_basic}
					r_e = \cfrac{D_i}{\mu l^2 }\left(c_s - c_p^* \right)
			\end{equation} }

			where $\mu$ is sphericity, $l$ a characteristic dimension of particles that can be defined as $l = r/3$, $r$ is the mean particle radius, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is the concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).

			According to \citet{Bulley1984}, a linear equilibrium relationship (Equation \ref{Linear_equilibirum}) can be used to find the equilibrium concentration of the solute in the fluid phase $c_f^*$ based on the concentration of the solute in the solid phase $c_s$:

			{\footnotesize
				\begin{align} \label{Linear_equilibirum}
					c_f^* &= k_p c_s
			\end{align} }

			The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase. \citet{Spiro2007} proposed to define the mass partition coefficient $k_m$ and the solid density $\rho_s$ as

			{\footnotesize
				\begin{align}
					k_m = \cfrac{k_p \rho_s}{\rho_f}
			\end{align} }

			According to \citet{Reverchon1996}, the kinetic term becomes

			{\footnotesize
				\begin{equation}
					\label{Model_kinetic_no_sat}
					r_e = \cfrac{D_i}{ \mu l^2 } \left(c_s - \cfrac{\rho_s c_f}{k_m \rho_f} \right)
			\end{equation} }

			\subfile{Saturation}

			\subsubsection{Heat balance} \label{CH: heat_balance}

			The heat balance equation describe the evolution of the enthalpy in the system and it is given by Equation \ref{EQ:Enthalpy_equation}

			{\footnotesize
				\begin{equation} \label{EQ:Enthalpy_equation}
					\cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f {\color{black}h} A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
				\end{equation}
			}

			%The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure.

			If the value of enthalpy $h$ is known from the time evolution of the energy equation, and pressure $P$ is known from measurement, then the temperature $T$ can be reconstructed based on the departure function. The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure. As presented by \citet{Gmehling2019}, for the Peng-Robinson equation of state, the enthalpy departure function is defined by Equation \ref{EQ:Enthalpy_PR}.

			{\scriptsize
				\begin{equation}
					{\color{black}h}-{\color{black}h}^{id}={\color{black}R}T \left[{\color{black}T_r}({\color{black}Z}-1) -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T\right) } } \ln \left(\cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}}\right)\right]
					\label{EQ:Enthalpy_PR}
				\end{equation}				
			}

			where $\alpha$ is defined as $\left( 1+\kappa \left( 1 - \sqrt{T_r} \right) \right)^2$, $T_r$ is the reduced temperature, $P_r$ is the reduced pressure, $Z$ is the compressibility factor, $\kappa$ is a quadratic function of the acentric factor and $B$ is calculated as $0.07780\frac{P_r}{T_r}$.

			Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which is assumed to be $T_{ref}=298.15$ K and $P_{ref}=1.01325$ bar.

			A root-finder can be used to find a value of temperature, which minimizes the difference between the value of enthalpy coming from the heat balance and the departure functions. The root fining procedure to repeated at every time step to find a temperature profile along spatial direction $z$.

			{\footnotesize
				\begin{equation}
					\min_T \left( \underbrace{h\left(t,x\right)}_{\text{Heat balance}} - \underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}} \right)^2
					\label{EQ:Enthalpy_root}
				\end{equation}
			}

			\subsubsection{Pressure term} \label{CH: Pressure}

			{\color{blue}As explained in Section \ref{CH:Governing_equations_chapter}, the pressure in the low-velocity region remains nearly constant due to the small pressure wave propagation occurring at the speed of sound. Under such conditions, the term $\partial P/\partial t$ can be approximated by a forward difference equation, describing the pressure change over a small time step $\Delta t$. The pressure $P$ in the system is treated as a state variable, while the incoming pressure at the new time-step $P_{in}$ is treated as a control:}

			{\footnotesize
				\begin{equation}
					\frac{\partial {\color{black}P}}{\partial t} \approx \frac{{\color{black}P_{in}} - {\color{black}P} }{\Delta t}
			\end{equation}}

			{\color{blue}Such a simplified equation allows for instantaneous pressure. In a real system, the pressure dynamics would depend on the behaviour of the pump and the back-pressure regulator, which introduce additional inertia and resistance to pressure changes, leading to pressure gradual build-up.}

			\subsubsection{Extraction yield} \label{CH: Yield}

			The process yield is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}. The measurement equation evaluates the solute's mass at the extraction unit outlet and sums it up. The integral form of the measurement (Equation \ref{Model_measurment_1}) can be transformed into the differential form (Equation \ref{Model_measurment_2}) and augmented with the process model.

			{\footnotesize
				\begin{align} 
					\label{Model_measurment_1}
					y &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
					\cfrac{dy}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
					\label{Model_measurment_2}
			\end{align}	}

			\subsubsection{Initial and boundary conditions} 
			It is assumed that the solvent is free of solute at the beginning of the process $c_{f0}=0$, that all the solid particles have the same initial solute content $c_{s0}$, and that the system is isothermal, hence the initial state is $h_0$. The fluid at the inlet is considered not to contain any solute. The initial and boundary conditions are defined as follows:

			{\footnotesize
				\begin{align*}
					&c_f(t = 0, z) = 0  && c_s(t = 0, z) = c_{s0} && h(t = 0, z) = h_0 \\
					&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
					&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0 \quad P(0) = P_0 \\
			\end{align*} }

			\subsubsection{Discretization methods}

				\begin{figure}[!h]
				\centering
				{\footnotesize
					\begin{align*}
						\dot{x} &= \cfrac{d x}{d t} = 
						\begin{bmatrix}
							\cfrac{d c_{f,1}}{d t} 	  \\
							\vdots					  \\
							\cfrac{d c_{f,N_z}}{d t} \\
							\\ \hline \\
							\cfrac{d c_{s,1}}{d t} 	  \\
							\vdots					  \\
							\cfrac{d c_{s,N_z}}{d t} \\
							\\ \hline \\
							\cfrac{d h_1}{d t} 	  \\
							\vdots 					  \\
							\cfrac{d h_{N_z}}{d t} \\
							\\ \hline \\
							\cfrac{d P}{d t} \\
							\\ \hline \\
							\cfrac{d y}{d t}
						\end{bmatrix}
						=
						\underbrace{\begin{bmatrix}
								G_1 \left( c_f,c_s,h; \Theta \right)\\ 
								\vdots\\ 
								G_{N_z} \left( c_f,c_s,h; \Theta \right)\\ 
								\\ \hline \\ \\
								G_{N_z+1} \left( c_f,c_s,h; \Theta \right)\\ 
								\vdots\\
								G_{2N_z} \left( c_f,c_s,h; \Theta \right)\\ 
								\\ \\ \hline \\ 
								G_{2N_z+1} \left( c_f,c_s,h; \Theta \right) \\
								\vdots\\
								G_{3N_z} \left( c_f,c_s,h; \Theta \right) \\ 
								\\ \\ \hline \\
								G_{3N_z+1} \left( c_f,c_s,h; \Theta \right) \\
								\\ \\ \hline \\
								G_{3N_z+2} \left( c_f,c_s,h; \Theta \right) 
						\end{bmatrix}}_{G \left( x; \Theta \right)} 
				\end{align*} }
				\caption{Discretized state-space}
				\label{fig:discretization}
			\end{figure}

			The method of lines is used to transform the process model equations into a set of ODEs denoted by $G(x;\Theta)$. For a derivative to be conservative, it must form a telescoping series. In other words, only the boundary terms should remain after adding all terms coming from the discretization over a grid, and the artificial interior points should be cancelled out. Discretization is applied to the conservative form of the model to ensure mass conservation. The backward finite difference is used to approximate the first-order derivative, while the central difference scheme approximates the second-order derivative $z$ direction. The length of the fixed bed is divided into $N_z$, i.e. equally distributed points in the $z$ direction. The state-space model after discretization is denoted by $x$ and defined as follows the Figure \ref{fig:discretization}, where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.

		\end{document}

### 2025-05-20 Sections/Results_DOE.tex
20.05

@@
 		\centering
-		\includegraphics[width=\columnwidth]{Figures/Results/scatter.png}	
+		\includegraphics[width=0.90\columnwidth]{Figures/Results/scatter.png}	
 		\caption{Initial vs final values of the cost function}
@@
 			\centering
-			\includegraphics[width=\columnwidth]{Figures/Results/Profile_F.png}	
+			\includegraphics[width=0.90\columnwidth]{Figures/Results/Profile_F.png}	
 			\caption{Optimal mass flow rate profiles}
@@
 			\centering
-			\includegraphics[width=\columnwidth]{Figures/Results/Profile_T.png}	
+			\includegraphics[width=0.90\columnwidth]{Figures/Results/Profile_T.png}	
 			\caption{Optimal inlet temperature profile}
@@
 			\centering
-			\includegraphics[width=\columnwidth]{Figures/Results/yield.png}	
+			\includegraphics[width=0.90\columnwidth]{Figures/Results/yield.png}	
 			\caption{Optimal yield profiles}
@@
 The blue curve (100 bar) exhibits the sharpest temperature drop, while the green curve (200 bar) demonstrates a slower and more gradual decline.
-At lower pressures, the final temperature reaches the lower bound and remains steady until the end of the batch.
+At lower pressures, the final temperature reaches the critical temperature and remains steady until the end of the batch.
 In contrary, the higher pressure cases result in a less significant temperature reduction.
@@
 Moreover, the model predicts the dataset in the region, which has not been validated during previous experiments.
-One hand this leaves a room for model validation, on the other hand the obtained set of data points might differs from the predictions.
-In such a case, further improvement of the model is necessary.
+On one hand this leaves a room for model validation, on the other hand the obtained set of data points might differs from the predictions.
 

### 2025-05-20 Sections/Saturation.tex
20.05

@@
 		\begin{equation}
-			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) \label{EQ: C_sat_function}
+			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( - \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) \label{EQ: C_sat_function}
 	\end{equation} }
@@
 			\label{Model_kinetic}
-			r_e = -\cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
+			r_e = \cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
 	\end{equation} }
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Di.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Di_1.png}
 		\caption{Multiple linear regression $D_i^R = f(Re, F)$}
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Gamma.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Gamma_1.png}
 		\caption{Multiple linear regression $\Upsilon = f(Re, F)$}

### 2025-05-20 Sections/introduction_imp.tex
20.05

@@
 
-	The supercritical carbon dioxide is commonly used for impregnation as described by \citet{Weidner2018}, \citet{Machado2022} or \citet{Fathi2022}.
-Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
-The main advantage of using supercritical CO$_2$ is that after depressurization, it desorbs from the surface and evaporates, leaving a solvent-free product.
-On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.
-
-	Another application of supercritical CO$_2$ is nanoparticles formation as investigated by \citet{Padrela2018}, \citet{Franco2021}, \citet{SaadatiArdestani2020} or \citet{Sodeifian2022}.
-Supercritical carbon-dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating operating conditions.
-Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nanosized particles or crystals, such as reduced use of toxic solvents.
-Moreover, the CO$_2$ is completely removed from the final product by simple depressurization.
-
 	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993} or \citet{Sovova1994}.
 Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
-Distillation, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
+Distillation involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
 This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction.
@@
 
+	The applications of supercritical carbon dioxide are not limited only to an extraction process but can also be used for impregnation, as described by \citet{Weidner2018} or \citet{Machado2022}.
+Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
+The main advantage of using supercritical CO$_2$ is that, after depressurization, it desorbs from the surface and evaporates, leaving a solvent-free product.
+On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.
+	The study of \citet{Ameri2020} investigates the loading of lansoprazole into polymers using supercritical carbon dioxide and examines how various parameters, such as temperature, pressure, and time, affect the drug loading efficiency.
+The results indicate that increasing any of these parameters enhances drug loading, with temperature having the most significant impact.
+\citet{Fathi2022} explored the use of supercritical carbon dioxide to enhance the bioavailability of ketoconazole by impregnating it into water-soluble polymers, specifically polyvinylpyrrolidone and hydroxypropyl methylcellulose.
+Utilizing a Box-Behnken design, the researchers optimized the impregnation process by varying pressure, temperature, and time, achieving increase in drug loadings ranging.
+
+	Another application of supercritical CO$_2$ is nanoparticle formation, as investigated by \citet{Padrela2018}, \citet{Franco2021} or \citet{Sodeifian2022}.
+Supercritical carbon-dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating the operating conditions.
+Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nanosized particles or crystals, such as reduced use of toxic solvents.
+Moreover, the CO$_2$ is removed from the final product by simple depressurization.
+	\citet{Sodeifian2018} investigated the solubility of Letrozole, a poorly water-soluble anticancer drug, in supercritical carbon dioxide with and without menthol as a solid co-solvent.
+The addition of menthol increased Letrozole's solubility by 7.1 times compared to supercritical CO$_2$ alone.
+Using the rapid expansion of supercritical solutions with solid co-solvent method, the average particle size of Letrozole was reduced to the nanoscale.
+Temperature was found to have the most significant impact on nanoparticle size reduction, while pressure had the least effect.
+	The study of \citet{SaadatiArdestani2020} explored the preparation of phthalocyanine green nano pigment using supercritical carbon dioxide as an antisolvent.
+The researchers employed the gas antisolvent technique to achieve nano-sized particles of the pigment.
+	\citet{Sodeifian2019} analysed the production of amiodarone hydrochloride nanoparticles using an ultrasonic-assisted rapid expansion of supercritical solution into a liquid solvent method.
+By optimizing parameters such as pressure, temperature, and polymeric stabilizer concentration, the researchers achieved significant particle size reduction.
+Characterization techniques confirmed the successful formation of nanoparticles with improved properties.
+
 	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process.
 Chamomile is a medicinal herb widely cultivated in southern and eastern Europe — in countries such as Germany, Hungary, France and Russia.
-It can be found outside Europe, for instance in Brazil as discussed by \citet{Singh2011}.
+It can also be found outside Europe, for instance in Brazil, as discussed by \citet{Singh2011}.
 This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets.
@@
 In comparison, chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
+{\color{blue}\citet{Milovanovic2023} extracted oils from Roman chamomile seeds in a two-stage process.
+First supercritical carbon dioxide at pressures up to 450 bar and temperatures up to 60 $^\circ$C was used for the first extraction.
+Then, the authors re-extracted using supercritical CO$_2$ with the addition of ethanol.
+By optimization in operating pressure, temperature, production cost, fraction of milled seeds, and co-solvent addition, the amount of separated chamomile oil increased from 2.4 to 18.6\% and the content of unsaturated fatty acids up to 88.7\%}.
 
 	The literature offers various mathematical models to describe the extraction of valuable compounds from biomass.
-Selecting a process model is case-to-case dependent and requires analysis of each model's specific assumptions about mass transfer and thermodynamic equilibrium.
+Selecting a process model is case-dependent and requires analysis of each model's specific assumptions about mass transfer and thermodynamic equilibrium.
 
-	\citet{Goto1996} presented the Shrinking Core (SC) model, which describes a process of irreversible desorption that is followed by diffusion through the pores of a porous solid.
-When the mass transfer rate of the solute in the non-extracted inner region is significantly slower than in the outer region, where most of the solute has already been extracted, or when the solute concentration exceeds its solubility in the solvent, a distinct boundary may form between the inner and outer regions.
+	Depending on the needs one of two approaches can be considered while developing a mathematical model for the extraction process.
+A model, which is based on a multiple regression can be used if the relation between inputs and outputs is the only of interests.
+\citet{Sodeifian2017a} investigated an influence of pressure, temperature and particle size on the extraction efficiency of oil from dracocephalum kotschyi boiss seed.
+The second order polynomial model was applied to obtain the corresponding response surface and to identify the optimum operating conditions.
+The study of \citet{Sodeifian2017b} investigates the of essential oil from Eryngium billardieri, focusing on optimizing extraction conditions and developing a mathematical model based on the second order polynomial to predict the process yield.
+The researchers employed a simulated annealing algorithm to optimize parameters such as pressure, temperature, and extraction time, aiming to maximize oil efficiency.
+
+	Alternatively, a first principle model can be derived and applied to cover not only the input-output relations, but the phenomena occurring in the system.
+This approach allows for more detailed representation the system behaviour, but requires deeper understanding of the underlying physics and more rigorous experiments.
+
+	\citet{Goto1996} presented the shrinking core (SC) model, which describes a process of irreversible desorption that is followed by diffusion through the pores of a porous solid.
+When the mass transfer rate of the solute in the non-extracted inner region is significantly slower than in the outer region, where most of the solute has already been extracted or when the solute concentration exceeds its solubility in the solvent, a distinct boundary may form between the inner and outer regions.
 As extraction progresses, the core of the inner region shrinks.
@@
 
-	\citet{Sovova1994} proposed The Broken-and-Intact Cell (BIC) model, which assumes that a portion of the solute, initially stored within plant structures and protected by cell walls, is released during the mechanical breakdown of the material.
+	\citet{Sovova1994} proposed the broken-and-intact cell (BIC) model, which assumes that a portion of the solute, initially stored within plant structures and protected by cell walls, is released during the mechanical breakdown of the material.
 The solute located in the region of broken cells near the particle surface is directly exposed to the solvent, while the core of the particle contains intact cells with undamaged walls.
@@
 
-	The Supercritical Fluid Extraction (SFE) process can be be treated similarly to heat transfer, considering solid particles like hot balls cooling down in a uniform environment.
-\citet{Bartle1990} introduced the hot ball diffusion (HBD) model, where spherical particles with uniformly distributed solute diffuse similarly to heat diffusion.
-Unlike the BIC model, where solute is readily available on the particle surface, the HBD model is suited for systems with small quantities of extractable materials and is not limited by solubility.
+	The supercritical fluid extraction (SFE) process can be treated similarly to heat transfer, considering solid particles as hot balls cooling down in a uniform environment.
+\citet{Bartle1990} introduced the hot ball diffusion (HBD) model, where spherical particles with a uniformly distributed solute diffuse similarly to heat diffusion.
+Unlike the BIC model, where the solute is readily available on the particle surface, the HBD model is suited for systems with small quantities of extractable materials and is not limited by solubility.
 The model is particularly relevant when internal diffusion controls mass transfer, allowing results from single particles to be extended to the entire bed under uniform conditions.
-\citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes for natural materials.
+\citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes.
 
@@
 The fraction of oil freely available on the particle surface should not be significant in the case of SFE from leaves.
-Consequently, SFE of essential oil from leaves should be mainly controlled by the internal mass-transfer resistance.
+Consequently, SFE of essential oil from leaves should be mainly controlled by  internal mass-transfer resistance.
 Therefore, the external mass-transfer coefficient was neglected in the development of the model of \citet{Reverchon1996}.
-The mass balances were developed in the additional hypotheses that the axial dispersion can be neglected and that the solvent density and flow rate are constant along the bed.
+The mass balances were developed with the additional hypotheses that axial dispersion can be neglected and that the solvent density and flow rate are constant along the bed.
 
 	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process.
-This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel.
+This model aims at control-oriented simplicity, assuming semi-continuous operation within a cylindrical vessel.
 The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
-Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T^{in}$) are adjustable and measurable, while the outlet temperature ($T^{out}$) and the amount of product at the outlet can only be monitored.
+Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
 Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.

### 2025-05-20 SFE_DOE_Chamomile_modified/plot_results.m

@@ -34,6 +34,7 @@ N_exp                   = 32;
 COLORS                  = ['b','r','k','m','g'];
 COST_I   = []; COST_F   = []; GROUP    = []; Yield      = [];
 PP                      = [100, 125, 150, 175, 200];
+%PP                      = [150, 175];
 
 figure(3)
 tiledlayout(numel(PP),2)
@@ -58,13 +59,13 @@ for ii = 1:numel(PP)
 
     Y_FP     = readlines(['FP_',num2str(PRES),'.txt']);
     YY_FP_0  = reshape(str2num(Y_FP(1,:)),[],N_exp);
-    YY_FP    = reshape(str2num(Y_FP(2,:)),[],N_exp);
+    YY_FP    = reshape(str2num(Y_FP(2,:)),[],N_exp); YY_FP(end,:)
 
     Time     = linspace(0,600,size(TempCont,1)+1);
 
     % Plots of controls
     selected_exp  = sort(FinaCost);
-    ind      = find( FinaCost == selected_exp(end) );
+    ind      = find( FinaCost == selected_exp(1) );
     
     %{\
     %subplot(3,1,1)
@@ -99,7 +100,7 @@ for ii = 1:numel(PP)
     %nexttile
     hold on
     %plot(Time, YY_RBF(:,ii), 'LineWidth',3, 'Color', 'r', 'LineStyle',':');
-    plot(Time, YY_FP( :,ii), 'LineWidth',3, 'Color', COLORS(ii), 'LineStyle','-');
+    plot(Time, YY_FP( :,ind), 'LineWidth',3, 'Color', COLORS(ii), 'LineStyle','-');
     %plot(Time, YY_RBF_0(:,ii), 'LineWidth',3, 'Color', 'b', 'LineStyle',':');
     %plot(Time, YY_FP_0( :,ii), 'LineWidth',3, 'Color', 'b', 'LineStyle','-');
     hold off
@@ -113,7 +114,7 @@ for ii = 1:numel(PP)
     %subplot(5,1,ii)
     %nexttile
     hold on
-    plot(Time(1:end-1), diff(YY_FP(:,ii)), 'LineWidth',3, 'Color', COLORS(ii),'LineStyle','-');
+    plot(Time(1:end-1), diff(YY_FP(:,ind)), 'LineWidth',3, 'Color', COLORS(ii),'LineStyle','-');
[…]

### 2025-05-21 Article_Design_of_Experiment-Chamomile.tex
21.05

@@
 This study investigates the process of chamomile oil extraction from flowers.
-A parameter-distributed model consisting of a set of partial differential equations is used to describe the governing mass transfer phenomena in a{ \color{blue}cylindrical packed bed with solid chamomile particles} under supercritical conditions using carbon dioxide as a solvent.
+A parameter-distributed model consisting of a set of partial differential equations is used to describe the governing mass transfer phenomena in a cylindrical packed bed with solid chamomile particles under supercritical conditions using carbon dioxide as a solvent.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-The empirical correlations used in the model are based on the set of laboratory experiments performed under multiple constant operating conditions: ${\color{blue}31} - 40~^\circ$C, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The empirical correlations used in the model are based on the set of laboratory experiments performed under multiple constant operating conditions: $30 - 40~^\circ$C, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
 A model-based design of experiments with D-optimality criterion is applied to improve the precision of the correlation parameters by designing a new dynamic experiment.
@@
 \nomenclature[A]{\(Q\)}{Weighting matrix \nomunit{-}}
-\nomenclature[A]{\(R\)}{Control cost matrix \nomunit{-}}
+\nomenclature[A]{\(\mathcal{R}\)}{Control cost matrix \nomunit{-}}
 %\nomenclature[A]{\(\textbf{G}\)}{Augumented system}

### 2025-05-21 Sections/DOE.tex
21.05

@@
 		\begin{flalign*}
-			\ln p\left(Y \mid \theta, \Xi \right) &\propto -\frac{1}{2} \left( \underbrace{r^\top \Sigma_Y^{-1} r}_{C} - 2 \underbrace{ J^\top \Sigma_Y^{-1} \Delta_y }_{B} \Delta_\theta + \Delta_\theta^\top \underbrace{\left( J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1} \right)}_{A} \Delta_\theta \right) && \\
-			&=-\frac{1}{2} \left( \Delta_\theta^\top A \Delta_\theta - 2 B^\top \Delta_\theta + C \right) &&
+			\ln p\left(Y \mid \theta, \Xi \right) &\propto -\frac{1}{2} \left( \underbrace{r^\top \Sigma_Y^{-1} r}_{\mathcal{C}} - 2 \underbrace{ J^\top \Sigma_Y^{-1} \Delta_y }_{\mathcal{B}} \Delta_\theta + \Delta_\theta^\top \underbrace{\left( J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1} \right)}_{\mathcal{A}} \Delta_\theta \right) && \\
+			&=-\frac{1}{2} \left( \Delta_\theta^\top \mathcal{A} \Delta_\theta - 2 \mathcal{B}^\top \Delta_\theta + \mathcal{C} \right) &&
 		\end{flalign*}
@@
 
-	By completing the square, we introduce $\theta^* = \hat{\theta} + A^{-1} B$, and the cost function becomes:
+	By completing the square, we introduce $\theta^* = \hat{\theta} + \mathcal{A}^{-1} \mathcal{B}$, and the cost function becomes:
 
@@
 		\begin{equation} 
-			\ln p\left(\theta \mid Y, \Xi \right) \propto -\frac{1}{2} \left( \left( \theta - \theta^* \right)^\top A \left( \theta - \theta^* \right) + C - B^\top A^{-1} B \right) 
+			\ln p\left(\theta \mid Y, \Xi \right) \propto -\frac{1}{2} \left( \left( \theta - \theta^* \right)^\top \mathcal{A} \left( \theta - \theta^* \right) + \mathcal{C} - \mathcal{B}^\top \mathcal{A}^{-1} \mathcal{B} \right)
 		\end{equation} }
@@
 	It can be observed that the quadratic term represents the spread of the posterior multivariate distribution around the mean $\theta^*$.
-The constant term $C - B^\top A^{-1} B$ is independent of $\theta$ and does not affect the shape of the posterior distribution but is still important for normalization.
+The constant term $\mathcal{C} - \mathcal{B}^\top \mathcal{A}^{-1} \mathcal{B}$ is independent of $\theta$ and does not affect the shape of the posterior distribution but is still important for normalization.
 This constant term is absorbed into the normalizing constant of the posterior distribution.
@@
 
-	{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) \propto \exp \left( -\frac{1}{2} \left( \theta - \theta^* \right)^\top A \left( \theta - \theta^* \right) \right) \end{equation} }
+	{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) \propto \exp \left( -\frac{1}{2} \left( \theta - \theta^* \right)^\top \mathcal{A} \left( \theta - \theta^* \right) \right) \end{equation} }
 
-	This is the expression of a multivariate normal distribution with mean $\theta^*$ and covariance matrix $A^{-1}$:
+	This is the expression of a multivariate normal distribution with mean $\theta^*$ and covariance matrix $\mathcal{A}^{-1}$:
 
-	{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) = \mathcal{N}\left( \theta^*, A^{-1} \right) \end{equation} }
+	{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) = \mathcal{N}\left( \theta^*, \mathcal{A}^{-1} \right) \end{equation} }
 
-	As the goal of optimal experimental design is to improve the precision of parameters, the main focus is on the matrix $A$, which consists of two terms.
+	As the goal of optimal experimental design is to improve the precision of parameters, the main focus is on the matrix $\mathcal{A}$, which consists of two terms.
 The first corresponds to the information gained from new observations based on the model and measurement error ($J^\top \Sigma_Y^{-1} J$), while the second is the prior information ($\Sigma_\theta^{-1}$).
@@
 	The cost function should describe the amount of information obtained from an experiment.
-For that purpose, it can be assumed that a function $\kappa$ can be related to the covariance matrix $A^{-1}$ obtained at arbitrary operating conditions:
+For that purpose, it can be assumed that a function $\kappa$ can be related to the covariance matrix $\mathcal{A}^{-1}$ obtained at arbitrary operating conditions:
 
-	{\footnotesize \begin{equation} j(\Xi) = \kappa\left[ A^{-1}(\theta, \Xi) \right] \end{equation} }
+	{\footnotesize \begin{equation} j(\Xi) = \kappa\left[ \mathcal{A}^{-1}(\theta, \Xi) \right] \end{equation} }
 
-	Recall that in the Bayesian estimation framework, the posterior covariance matrix of the parameter estimates is given by $\Sigma = A^{-1} = \left(J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1}\right)^{-1} $.
+	Recall that in the Bayesian estimation framework, the posterior covariance matrix of the parameter estimates is given by $\Sigma = \mathcal{A}^{-1} = \left(J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1}\right)^{-1} $.
 $J$ is the Jacobian matrix of the model outputs with respect to the parameters, $\Sigma_Y$ is the covariance matrix of the measurement errors, and $\Sigma_\theta$ is the prior covariance matrix of the parameters.
@@
 		\begin{align} \label{EQ:DOE_general}
-			\kappa_k\left( A^{-1}(\theta) \right) &= \left[ \frac{1}{n_\theta} \operatorname{trace}\left( Q A^{-1}(\theta, \Xi) Q^\top \right)^k \right]^{1/k} & \text{if} \det A^{-1} \neq 0, \nonumber \\ 
-			\kappa_k\left( A^{-1}(\theta) \right) &= \infty & \text{if} \det A^{-1} = 0
+			\kappa_k\left( \mathcal{A}^{-1}(\theta) \right) &= \left[ \frac{1}{n_\theta} \operatorname{trace}\left( Q \mathcal{A}^{-1}(\theta, \Xi) Q^\top \right)^k \right]^{1/k} & \text{if} \det \mathcal{A}^{-1} \neq 0, \nonumber \\
+			\kappa_k\left( \mathcal{A}^{-1}(\theta) \right) &= \infty & \text{if} \det \mathcal{A}^{-1} = 0
 		\end{align} }
@@
 
-	{\footnotesize \begin{equation} j_L(\Xi) = \operatorname{trace} \left( Q A^{-1}(\theta, \Xi) Q^\top \right) \end{equation} }
+	{\footnotesize \begin{equation} j_L(\Xi) = \operatorname{trace} \left( Q \mathcal{A}^{-1}(\theta, \Xi) Q^\top \right) \end{equation} }
 
@@
 	Selecting $Q$ as a row vector results in C-optimality, which focuses on linear combinations of parameters.
-Setting $Q = \mathbf{I}_{n\theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalue of the covariance matrix $A^{-1}(\theta, \Xi)$, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.
+Setting $Q = \mathbf{I}_{n\theta}$ and $k = \infty$ leads to E-optimality, where the design maximizes the smallest eigenvalue of the covariance matrix $\mathcal{A}^{-1}(\theta, \Xi)$, thereby minimizing the length of the largest axis of the asymptotic confidence ellipsoids.
 
-	The most commonly used criterion is the D-optimality, which involves $k = 0$ and $Q = \mathbf{I}_{n\theta}$, requiring the minimization of $\det A^{-1}(\theta, \Xi)$, or equivalently, maximization of:
+	The most commonly used criterion is the D-optimality, which involves $k = 0$ and $Q = \mathbf{I}_{n\theta}$, requiring the minimization of $\det \mathcal{A}^{-1}(\theta, \Xi)$, or equivalently, maximization of:
 
-	{\footnotesize \begin{equation} j_D(\Xi) = \det A(\theta, \Xi) \end{equation} }
+	{\footnotesize \begin{equation} j_D(\Xi) = \det \mathcal{A}(\theta, \Xi) \end{equation} }
 
-	Since $\det A(\theta, \Xi) = 1 / \det A^{-1}(\theta, \Xi)$, maximizing $\det A$ is equivalent to minimizing $\det A^{-1}$.
+	Since $\det A(\theta, \Xi) = 1 / \det \mathcal{A}^{-1}(\theta, \Xi)$, maximizing $\det \mathcal{A}$ is equivalent to minimizing $\det \mathcal{A}^{-1}$.
 
@@
 	Details on the process model can be found in \citet{Sliczniuk2024}.
-The model's empirical correlations are derived based on laboratory experiments conducted under various but constant operating conditions: $31 - 40~^\circ\text{C}$, $100 - 200$ bar, and $3.33 \cdot 10^{-5} - 6.67 \cdot 10^{-5}$ kg/s.
+The model's empirical correlations are derived based on laboratory experiments conducted under various but constant operating conditions: $30 - 40~^\circ\text{C}$, $100 - 200$ bar, and $3.33 \cdot 10^{-5} - 6.67 \cdot 10^{-5}$ kg/s.
 This study employs the process model obtained previously to design a set of supplementary experiments with dynamically changing conditions to improve the precision of the correlation for $D_i$.
@@
 This penalty increases the cost function value when there are rapid changes in the decision variables.
-The matrix $\bar{R}$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$.
+The matrix $\mathcal{R}$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$.
 The problem formulation is given by Equation \ref{EQ:Formulation_2}.
@@
 				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5}, \\
-				& \bar{R} = 
+				& \mathcal{R} = 
 				\begin{bmatrix} 

### 2025-05-21 Sections/Model.tex
21.05

@@
 
-			{\color{blue}As explained in Section \ref{CH:Governing_equations_chapter}, the pressure in the low-velocity region remains nearly constant due to the small pressure wave propagation occurring at the speed of sound.
+			As explained in Section \ref{CH:Governing_equations_chapter}, the pressure in the low-velocity region remains nearly constant due to the small pressure wave propagation occurring at the speed of sound.
 Under such conditions, the term $\partial P/\partial t$ can be approximated by a forward difference equation, describing the pressure change over a small time step $\Delta t$.
-The pressure $P$ in the system is treated as a state variable, while the incoming pressure at the new time-step $P_{in}$ is treated as a control:}
+The pressure $P$ in the system is treated as a state variable, while the incoming pressure at the new time-step $P_{in}$ is treated as a control:
 
@@
 
-			{\color{blue}Such a simplified equation allows for instantaneous pressure.
-In a real system, the pressure dynamics would depend on the behaviour of the pump and the back-pressure regulator, which introduce additional inertia and resistance to pressure changes, leading to pressure gradual build-up.}
+			Such a simplified equation allows for instantaneous pressure.
+In a real system, the pressure dynamics would depend on the behaviour of the pump and the back-pressure regulator, which introduce additional inertia and resistance to pressure changes, leading to pressure gradual build-up.
 

### 2025-05-28 Article_Design_of_Experiment-Chamomile.tex
29.05

@@
 % ===================================================
-\title[mode=title]{Optimal design of experiment}                      
-\shorttitle{ODOE}
+\title[mode=title]{Optimal model-based design of experiments for parameter precision: Supercritical Extraction case}                      
+\shorttitle{OMB DOE: SFE}
 
@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-The empirical correlations used in the model are based on the set of laboratory experiments performed under multiple constant operating conditions: $30 - 40~^\circ$C, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-A model-based design of experiments with D-optimality criterion is applied to improve the precision of the correlation parameters by designing a new dynamic experiment.
-The mass flow rate and inlet temperature are used as decision variables to maximize the Fisher Information embedded in the yield curve with respect to the empirical correlations.
+The empirical correlations used in the model are based on a set of laboratory experiments performed under multiple constant operating conditions: $30 - 40~^\circ$C, $100 - 200$ bar and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+A model-based design of experiments with the D-optimality criterion is applied to improve the precision of the correlation parameters by designing a new dynamic experiment.
+The mass flow rate and inlet temperature are used as decision variables to maximise the Fisher information embedded in the yield curve with respect to the empirical correlations.
 
@@
 \begin{keywords}
-Supercritical extraction \sep Optimal design of experiment \sep Mathematical modelling
+	Supercritical extraction \sep Optimal design of experiments \sep Mathematical modelling
 \end{keywords}
@@
 
-\subfile{Sections/introduction_imp}
+%\subfile{Sections/introduction_imp}
+Supercritical CO2 extraction is a green extraction method that uses carbon dioxide in a supercritical state (above its critical point of 31.1 $^\circ$C and 73.8 bar) to extract compounds from materials.
+This is one of the most popular applications of supercritical fluids, which was described by many researchers, for example \citet{Sodeifian2017}, \citet{Reverchon1993} and \citet{Sovova1994}.
+Traditional methods, such as distillation and organic solvent extraction, are commonly employed although they have drawbacks.
+Distillation involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
+This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction.
+Supercritical CO$_2$ is attractive due to its distinctive properties: it is inflammable, non-toxic and non-corrosive.
+Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
 
-\subfile{Sections/Literature_Review}
+Applications for supercritical carbon dioxide are not limited to extraction processes; they can also be used for impregnation, as described by \citet{Weidner2018} and \citet{Machado2022}.
+Impregnation is defined as modification of the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, for example, the surface hydrophobisation.
+The main advantage of using supercritical CO$_2$ is that, after depressurisation, it desorbs from the surface and evaporates, leaving a solvent-free product.
+However, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs surface hydrophobisation.
+The study of \citet{Ameri2020} investigates the loading of lansoprazole into polymers using supercritical carbon dioxide and examines how various parameters, such as temperature, pressure and time, affect the drug loading efficiency.
+The results indicate that increasing any of these parameters enhances drug loading, with temperature having the most significant impact.
+\citet{Fathi2022} explored the use of supercritical carbon dioxide to enhance the bioavailability of ketoconazole by impregnation into water-soluble polymers, specifically polyvinylpyrrolidone and hydroxypropyl methylcellulose.
+Utilising a Box-Behnken design, the researchers optimised the impregnation process by varying pressure, temperature and time, achieving an increased drug loading range.
+
+Another application of supercritical CO$_2$ is nanoparticle formation, as investigated by \citet{Padrela2018}, \citet{Franco2021} and \citet{Sodeifian2022}.
+Supercritical $CO_2$-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating the operating conditions.
+Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nano-sized particles or crystals, such as reduced use of toxic solvents.
+Moreover, the CO$_2$ can be removed from the final product by simple depressurisation.
+\citet{Sodeifian2018} investigated the solubility of Letrozole, a poorly water-soluble anticancer drug, in supercritical carbon dioxide with and without menthol as a solid co-solvent.
+The addition of menthol increased the solubility of Letrozole by 7.1 times compared to supercritical CO$_2$ alone.
+Using the rapid expansion of supercritical solutions with the solid co-solvent method, the average particle size of Letrozole was reduced to the nanoscale.
+Temperature was found to have the most significant impact on nanoparticle size reduction, while pressure had the least effect.
+The study of \citet{SaadatiArdestani2020} explored the preparation of phthalocyanine green nano pigment using supercritical carbon dioxide as an anti-solvent.
+The researchers employed the gas anti-solvent technique to achieve nano-sized pigment particles.
+\citet{Sodeifian2019} analysed the production of amiodarone hydrochloride nanoparticles using ultrasonic-assisted rapid expansion of the supercritical solution in a liquid solvent method.
+The researchers achieved significant particle size reduction by optimising parameters such as pressure, temperature and polymeric stabiliser concentration.
+Characterisation techniques confirmed the successful formation of nanoparticles with improved properties.
+
+The present study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques in addition to the modelling of this process.
+Chamomile is a medicinal herb widely cultivated in southern and eastern Europe - in countries such as Germany, Hungary, France and Russia.
+It can also be found outside Europe, for instance in Brazil, as discussed by \citet{Singh2011}.
+Chamomile is distinguished by its hollow, bright gold cones that house disc or tubular florets surrounded by about fifteen white ray or ligulate florets.
+The plant has been utilised for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy.
+Chamomile extracts are widely used to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia and other sleep-related conditions, according to \citet{Srivastava2009}.
+\citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg.
+The highest yields of essential oil, between 6.1 mL/kg and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine.
+In comparison, chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
+\citet{Milovanovic2023} extracted oils from Roman chamomile seeds in a two-stage process.
+First, supercritical carbon dioxide at pressures of up to 450 bar and temperatures up to 60 $^\circ$C was used for the first extraction.
+Then, the oil was re-extracted using supercritical CO$_2$ with the addition of ethanol.
+Through optimisation of the operating pressure, temperature, production cost, fraction of milled seeds and addition of co-solvent, the amount of separated chamomile oil increased from 2.4 to 18.6\% and the content of unsaturated fatty acids up to 88.7\%.
+
+The literature offers various mathematical models to describe the extraction of valuable compounds from biomass.
+Selecting a process model is case-dependent and requires analysis of each model's specific assumptions about mass transfer and thermodynamic equilibrium.
+
+Depending on the case, two approaches can be considered when developing a mathematical model for the extraction process.
+A model based on multiple regression can be used if the relation between inputs and outputs is the only one of interest.
+\citet{Sodeifian2017a} investigated the influence of pressure, temperature and particle size on the extraction efficiency of oil from \textit{Dracocephalum kotschyi Boiss} seed.
+A second-order polynomial model was applied to obtain the corresponding response surface and to identify the optimum operating conditions.
+The study of \citet{Sodeifian2017b} investigates the extraction of essential oil from Eryngium billardieri, focusing on optimising the extraction conditions and developing a mathematical model based on the second-order polynomial to predict the process yield.
+The researchers employed a simulated annealing algorithm to optimise parameters such as pressure, temperature and extraction time, aiming to maximise oil extraction efficiency.
+
+Alternatively, a first-principle model can be derived and applied to cover not only the input-output relations, but also the phenomena occurring in the system.
+This approach allows for a more detailed representation of the system behaviour, but requires deeper understanding of the underlying physics and more rigorous experiments.
+
+\citet{Goto1996} presented the shrinking core (SC) model, which describes a process of irreversible desorption followed by diffusion through the pores of a porous solid.
+When the mass transfer rate of the solute in the non-extracted inner region is significantly slower than in the outer region, where most of the solute has already been extracted or when the solute concentration exceeds its solubility in the solvent, a distinct boundary may form between the inner and outer regions.
+As extraction progresses, the core of the inner region shrinks.
+The model envisions supercritical CO$_2$ extraction as a sharp, inward-moving front, with a completely non-extracted core ahead of the front and a fully extracted shell behind it.
+
+\citet{Sovova1994} proposed the broken-and-intact cell (BIC) model, which assumes that a portion of the solute, initially stored within plant structures and protected by cell walls, is released during the mechanical breakdown of the material.
+The solute located in the region of broken cells near the particle surface is directly exposed to the solvent, while the core of the particle contains intact cells with undamaged walls.
+This model describes three extraction phases: a fast extraction phase for accessible oil, a transient phase and a slow phase controlled by diffusion.
+The model has been successfully applied to the extraction of grape oil (\citet{Sovova1994b}) and caraway oil (\citet{Sovova1994a}).
+
+The supercritical fluid extraction (SFE) process can be treated similarly to heat transfer, considering solid particles as spheres cooling down in a uniform environment.
+\citet{Bartle1990} introduced the hot ball diffusion (HBD) model, where spherical particles with a uniformly distributed solute diffuse similarly to heat diffusion.
+Unlike the BIC model, where the solute is readily available on the particle surface, the HBD model is suitable for systems with small quantities of extractable materials and is not limited by solubility.
+The model is particularly relevant when mass transfer is controlled by internal diffusion, allowing results from single particles to be extended to the entire bed under uniform conditions.
+\citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes.
+
+\citet{Reverchon1996} proposed a model for the extraction of essential oils that are mainly located inside vegetable cells in organelles called vacuoles.
+Only a small fraction of essential oil might be near the particle surface due to the breaking up of cells during grinding or in epidermal hairs located on the leaf surface.
+The fraction of oil freely available on the particle surface should not be significant in the case of SFE from leaves.
+Consequently, SFE of essential oil from leaves should be controlled mainly by internal mass-transfer resistance.
+Therefore, the external mass-transfer coefficient was neglected in the development of Reverchon's model (\citet{Reverchon1996}).
+The mass balances were developed with the additional hypotheses that axial dispersion can be neglected and that the solvent density and flow rate are constant along the bed.
+
+This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process.
+The model aims at control-oriented simplicity, assuming semi-continuous operation within a cylindrical vessel.
+The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
+Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
+Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\columnwidth]{Figures/PFD.drawio.pdf}
+	\caption{Process flow diagram.}
+	\label{fig: SFE_drawing}
+\end{figure}
+
+%\subfile{Sections/Literature_Review}
+Design of experiments (DoE) is a structured approach that examines how various elements influence a particular result.
+By evaluating multiple factors at once, DoE allows the uncovering of the impacts of each element and their combinations to be discovered, yielding a comprehensive comprehension of the entire system.
+DoE begins with the determination of the experiment's objectives and selection of the factors for the study process.
+DoE aims to obtain the maximum information from an experimental apparatus modelled by devising experiments that will yield the most informative data in a statistical sense for use in parameter estimation and model validation.
+
+The first conceptualisation of DoE was introduced by \citet{Fisher1935}, who described the fundamental problem of experimental design as deciding which pattern of factor combinations would best reveal the properties of the response that is influenced by the factors.
+This type of DoE views an experiment as simply connecting inputs with outputs and is therefore called a "black-box experiment design".
+It aims to select the combinations of factor values that provide the most information on the input-output relationship in the presence of variation.
+The main class of statistical design techniques of this type of DoE are the so-called factorial methods.
+These methods are created to measure the additive effects on the response for each input factor and investigate the effects of interactions between factors.
+Factorial methods are not suitable for situations where constraints exist on the output or internal states.
+They are better suited for dynamic experiments where inputs and outputs have complex time profiles.
+However, this group of methods is still widely used due to their simplicity.
+
+\citet{Ramandi2011} conducted a study to identify the variables with the greatest influence on the extraction yield of fatty acids from \textit{Borago officinalis L.} flowers using supercritical fluid extraction (SFE).
+A full factorial design was employed as the screening method, resulting in a design matrix of 32 runs ($2^5$) carried out randomly to minimise the impact of external factors.
+The low and high values for the factors were selected based on previous research.
+After determining the most significant variables, a central composite design was applied to three factors, i.e.
+temperature, pressure and the volume of the methanol co-solvent, to optimise the SFE conditions.
+This allowed for the modelling of the response surface by fitting a second-order polynomial.
+
+Similarly, \citet{Caldera2012} conducted a study to optimise the SFE variables, specifically the extraction pressure, extraction temperature and static extraction time, for the maximum extraction of carnosol and carnosic acid from Venezuelan rosemary (\textit{Rosmarinus officinalis L.}) leaves.
+A $2^3$ full factorial design was initially used to examine these three variables.
+Based on the statistically significant variables, a Box-Behnken design was employed to create a matrix of 15 experiments, which was used to further optimise the SFE process for maximum carnosol and carnosic acid extraction using response surface methodology.
+
+As opposed to the "black-box" statistical experiment design methods, another form of optimal design has been developed, taking explicit advantage of some knowledge of the structure underlying the system, which is represented by a mathematical model, particularly in the form of differential and algebraic equations.
+The model-based experiment design approach is characterised by the following:
+
+\begin{enumerate}
+	\item explicit use of model equations and current parameters to predict the "information content" of the subsequent experiment
+	\item application of an optimisation framework for solving the resulting numerical problem
+\end{enumerate}
+
+After an initial data set has been collected and fitted to a mathematical model, the model undergoes further analysis.
+Additional experiments may be needed to differentiate between competing models that pass the preliminary tests.
+Once inadequate models have been rejected, the remaining model may undergo another round of experiment design to enhance the precision of its parameters.
+This paper focuses on the final step of the validation procedure, known as model-based design of experiments (m-DoE), aimed at improving parameter precision.
+To the best of the authors' knowledge, m-DoE has not been applied to any case of supercritical extraction, so the following literature review provides examples of applications in crystallisation and pharmacology processes.
+
+\citet{Chung2000} applied model-based experimental design to a batch crystallisation process with a cooling jacket.
+A dynamic programming formulation minimises the volume of the confidence hyper-ellipsoid for the estimated nucleation and growth parameters over the supersaturation profile and the seed characteristics, namely, crystal mass, mean size and width of seed distribution.
+As a result, the accuracy of the parameter estimates can be improved by identifying the optimal temperature profile.
+
+\citet{Duarte2019} investigated compartment models incorporating Michaelis-Menten elimination kinetics for pharmacological applications.
+The authors designed both static and dynamic experiments for 2- and 3-compartment models using D-optimality criteria.
+The dynamic experiments for both models involved the determination of the initial concentration in the first compartment and the optimisation of the mass flow rate profile of the drug entering this compartment.
 
@@
 
-\subfile{Sections/Model}
+%\subfile{Sections/Model}
+\section{Materials and methods} \label{CH: Materials and methods}
 
-\subsection{Optimal design of experiment} \label{CH: DOE}
-\subfile{Sections/DOE}
+\subsection{Governing equations} \label{CH:Governing_equations_chapter}
+The governing equations for a quasi-one-dimensional flow were derived by following the work of \citet{Anderson1995}.
+A quasi-one-dimensional flow refers to a fluid flow scenario which assumes that the flow properties are uniformly distributed across any cross-section.
+This simplification is typically applied when the cross-sectional area of the flow channel changes, such as through irregular shapes or partial filling of an extractor.
+According to this assumption, velocity and other flow properties change solely in the flow direction.
+
+As discussed by \citet{Anderson2023}, all flows are compressible, but some can be treated as incompressible since the velocities are low.
+This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strictly incompressible) or varying density flow.
+The assumption allows for removal of acoustic waves and large perturbations in density and/or temperature.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant along $z-$ direction.
+
+The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}:
+
+{\footnotesize
+	\begin{align}
+		\label{EQ: CompressibleEuler_1}
+		\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
+		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
+		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+		\label{EQ: CompressibleEuler_3}
+	\end{align}  
+}
+
+where $\rho_f$ is the density of the fluid, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time, and $z$ is the spatial direction.
+
+\subsection{Extraction model} \label{CH: Extraction_model}
+\subsubsection{Continuity equation} \label{CH: Continuity}
+
+The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating the function $A_f = A\phi$.
+This modification differentiates constant and varying terms, where the varying term accounts for changes in the cross-sectional area available for the fluid.
+Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:
+
+{\footnotesize
+	\begin{equation} \label{EQ: Continuity_differential}
+		\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial z} = 0
+	\end{equation}
+}
+where $A$ is the total cross-section of the extractor and $\phi$ describes the porosity along the extractor.
+
+Assuming that the porosity and mass flow rate are constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as
+
+{\footnotesize
+	\begin{equation}
+		\int \frac{\partial (\rho_f v A \phi )}{\partial z} dz = F \rightarrow F=\rho_f v A\phi
+	\end{equation}
+}
+
+To simplify the system dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows the velocity profile that satisfies mass continuity based on $F$, $\phi$ and $\rho_f$ to be found:
+
+{\footnotesize
+	\begin{equation} \label{EQ:Velocity_1}
+		v = \cfrac{F}{\rho_f A\phi} 
+	\end{equation}
+}
+
+Similarly, superficial velocity may be introduced:
+
+{\footnotesize
+	\begin{equation} \label{EQ:Velocity_2}
+		u = v \phi = \cfrac{F}{\rho_f A }
+	\end{equation}
+}
+
+The fluid density $\rho_f$ can be obtained from the Peng-Robinson equation of state if the temperature and thermodynamic pressure are known along $z$.
+Variation in fluid density may occur due to pressure or inlet temperature changes.
+In a non-isothermal case, in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} $\rho_f$ is considered to be the average fluid density along the extraction column.
+
+\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
+
+Equation \ref{Model_fluid} describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption.
+Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to those of the solvent itself.
+It is also assumed that the thermodynamic pressure remains constant throughout the device.
+The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall.
+This leads to a uniform velocity profile across any cross-section perpendicular to the axial direction.
+Thus, the mass balance equation includes convection, diffusion and kinetic terms representing the fluid phase behaviour:
+
+{\footnotesize
+	\begin{equation}
+		\label{Model_fluid}
+		\frac{\partial c_f}{\partial t}
+		+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z}
+		= \frac{1-\phi}{\phi} r_e
+		+ \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right)
+	\end{equation}
+}
+
+where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the axial dispersion coefficient.
+
+\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
+
+As given by Equation \ref{Model_solid}, the solid phase is considered to be stationary, without convection and diffusion terms in the mass balance equation.
+Therefore, the only significant term in this equation is the kinetic term of Equation \ref{Model_kinetic_basic}, which connects the solid and fluid phases.
+For simplicity, the extract is represented by a single pseudo-component:
+
+{\footnotesize
+	\begin{equation} 
+		\label{Model_solid}
+		%		{\scriptsize\begin{equation}
+				\cfrac{\partial c_s}{\partial t} = \underbrace{ -  r_e }_{\text{Kinetics}}
+		\end{equation} }
+
+		\subsubsection{Kinetic term} \label{CH: Kinetic}
+
+		As the solvent flows through the fixed bed, CO$_2$ molecules diffuse into the pores, adsorb on the inner surface and form a film due to solvent-solid matrix interactions.
+The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore and the film into the bulk.
+Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$, and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$ for the solid and fluid phases, respectively.
+The concentration of the solutes in the fluid phase in the centre of the pore is denoted as $c_p$.
+As the solute diffuses through the pore, its concentration changes, reaching $c_{pf}$ at the opening.
+Then, the solute diffuses through the film around the particle and reaches bulk concentration $c_f$.
+The two-film theory describes the solid-fluid interface inside the pore.
+The overall mass transfer coefficient can be determined from the relationship between the solute concentration in one phase and its equilibrium concentration.
+
+		\begin{figure}[h!]
+			\centering
+			\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=0.85\columnwidth]{Figures/SFE_PFD.drawio.png}	
+			\caption{Mass transfer mechanism.}
+			\label{fig: SFE_Mechanism}
+		\end{figure}
+
+		\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between the concentration of the solute in the bulk, $c_f$, and in the centre of the pore, $c_p^*$.
+According to the equilibrium relationship, the concentration $c_p^*$ is in equilibrium with $c_s$.
+The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$.
+In contrast, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
+As given by Equation \ref{Model_kinetic_basic}, the concentration $c_p^*$ is determined by the equilibrium relationship with $c_f$:
+
+		{\footnotesize
+			\begin{equation} \label{Model_kinetic_basic}
+				r_e = \cfrac{D_i}{\mu l^2 }\left(c_s - c_p^* \right)
+		\end{equation} }
+
+		where $\mu$ is sphericity, $l$ a characteristic dimension of particles that can be defined as $l = r/3$, $r$ is the mean particle radius, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is the concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
+
+		According to \citet{Bulley1984}, a linear equilibrium relationship (Equation \ref{Linear_equilibirum}) can be used to find the equilibrium concentration of the solute in the fluid phase $c_f^*$ based on the concentration of the solute in the solid phase $c_s$:
+
+		{\footnotesize
+			\begin{align} \label{Linear_equilibirum}
+				c_f^* &= k_p c_s
+		\end{align} }
+
+		The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
+\citet{Spiro2007} proposed a definition of the mass partition coefficient $k_m$ and the solid density $\rho_s$ as
+
+		{\footnotesize
+			\begin{align}
+				k_m = \cfrac{k_p \rho_s}{\rho_f}
+		\end{align} }
+
+		According to \citet{Reverchon1996}, the kinetic term becomes
+
+		{\footnotesize
+			\begin{equation}
+				\label{Model_kinetic_no_sat}
+				r_e = \cfrac{D_i}{ \mu l^2 } \left(c_s - \cfrac{\rho_s c_f}{k_m \rho_f} \right)
+		\end{equation} }
+
+		%\subfile{Saturation}
+		\subsubsection{Uneven solute distribution in the solid phase} \label{CH: Gamma_Function}
+
+		Following the idea of the broken-and-intact cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}:
+
+		{\footnotesize
+			\begin{equation}
+				D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( - \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) \label{EQ: C_sat_function}
+		\end{equation} }
+
+		where  ${\color{black}\Upsilon}$ describes the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term:
+
+		{\footnotesize
+			\begin{equation}
+				\label{Model_kinetic}
+				r_e = \cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
+		\end{equation} }
+
+		The $\gamma$ function limits the solute's availability in the solid phase.
+Similarly to the BIC model, the solute is assumed to be contained inside the cells, some of which are open because the cell walls have been broken by grinding, with the rest remaining intact.
+The diffusion of solute from a particle's core takes more time than the diffusion of solute close to the outer surface.
+The same idea can be represented by the decaying internal diffusion coefficient, where the decreasing term is a function of the solute concentration in the solid.
+
+		An alternative interpretation of the decay function $\gamma$ involves taking into account the porous structure of the solid particles, where the pores are initially saturated with the solute.
+During extraction, the solute within these pores gradually dissolves into the surrounding fluid.
+Initially, the solute molecules near the pore openings dissolve and diffuse rapidly due to the short diffusion paths.
+As extraction progresses, the dissolution front moves deeper into the pore structure and solute from the inner regions of the pores begins to dissolve.
+The diffusion of solute molecules from the interior of the pores to the external fluid becomes progressively slower because the effective diffusion path length increases.
+This lengthening of the diffusion path enhances mass transfer resistance, reducing the overall diffusion rate.
+
+		In an extreme case, this model could be compared with the shrinking core (SC) model presented by \citet{Goto1996}, where the particle radius is reduced as the solute content in the solid phase decreases.
+In the SC model, the reduction in particle size leads to significant changes in both the diffusion path length and the surface area available for mass transfer.
+The diminishing particle size increases the diffusion path within the remaining solid core and decreases the external surface area, both of which contribute to a slower extraction rate.
+When comparing this to the varying diffusion coefficient in our model, some conceptual similarities can be noticed.
+
+		\subsubsection{Empirical correlations}
+
+		The empirical correlations for $D_i$ and $\Upsilon$ were derived by \citet{Sliczniuk2024} and validated for temperatures of $30 - 40~^\circ C$, pressures of $100 - 200$ bar and mass flow rates of $3.33-6.67 \cdot 10^{-5}$ kg/s.
+Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to parameter estimation solutions and selected independent variables.
+The region marked with the white dashed line represents the confidence region where the model has been tested.
+Both correlations should be equal or greater than zero to avoid unphysical behaviour such as reverse mass transfer.
+The multiple linear regression functions are combined with the rectifier function to ensure non-negativity.
+
+		\begin{figure}[!ht]
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Di_1.png}
+			\caption{Multiple linear regression $D_i^R = f(Re, F)$.}
+			\label{fig:Correlation_Di}
+		\end{figure}
+
+		\begin{figure}[!ht]
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Gamma_1.png}
+			\caption{Multiple linear regression $\Upsilon = f(Re, F)$.}
+			\label{fig:Correlation_Gamma}
+		\end{figure}
+
+		\subsubsection{Heat balance} \label{CH: heat_balance}
+
+		The heat balance equation describes the evolution of enthalpy in the system, given by Equation \ref{EQ:Enthalpy_equation}:
+
+		{\footnotesize
+			\begin{equation} \label{EQ:Enthalpy_equation}
+				\cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f {\color{black}h}  v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+			\end{equation}
+		}
+
+		If the value of enthalpy $h$ is known from the time evolution of the energy equation and pressure $P$ is known from measurement, then the temperature $T$ can be reconstructed based on the departure function.
+The departure function is a mathematical function that characterises the deviation of a thermodynamic property (enthalpy, entropy or internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+As presented by \citet{Gmehling2019}, the enthalpy departure function for the Peng-Robinson equation of state is defined by Equation \ref{EQ:Enthalpy_PR}:
+
+		{\scriptsize
+			\begin{equation}
+				{\color{black}h}-{\color{black}h}^{id}={\color{black}R}T \left[{\color{black}T_r}({\color{black}Z}-1) -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T\right) } } \ln \left(\cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}}\right)\right]
+				\label{EQ:Enthalpy_PR}
+			\end{equation}				
+		}
+
+		where $\alpha$ is defined as $\left( 1+\kappa \left( 1 - \sqrt{T_r} \right) \right)^2$, $T_r$ is the reduced temperature, $P_r$ is the reduced pressure, $Z$ is the compressibility factor, $\kappa$ is a quadratic function of the acentric factor and $B$ is calculated as $0.07780\frac{P_r}{T_r}$.
+
+		Equation \ref{EQ:Enthalpy_PR} requires a reference state, which is assumed to be $T_{ref}=298.15$ K and $P_{ref}=1.01325$ bar.
+
+		A root finder can be used to find a temperature value that minimises the difference between the value of enthalpy coming from the heat balance and the departure functions.
+The root-finding procedure is repeated at every time step to find a temperature profile along the spatial direction $z$.
+
+		{\footnotesize
+			\begin{equation}
+				\min_T \left( \underbrace{h\left(t,x\right)}_{\text{Heat balance}} - \underbrace{h\left(T,P,o_f\left(T,P\right)\right)}_{\text{Departure function}} \right)^2
+				\label{EQ:Enthalpy_root}
+			\end{equation}
+		}
+
+		\subsubsection{Pressure term} \label{CH: Pressure}
+
+		As explained in Section \ref{CH:Governing_equations_chapter}, the pressure in the low-velocity region remains nearly constant due to the small pressure wave propagation occurring at the speed of sound.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by a forward difference equation, describing the pressure change over a small time step $\Delta t$.
+The pressure $P$ in the system is treated as a state variable, while the incoming pressure at the new time step $P_{in}$ is treated as a control:
+
+		{\footnotesize
+			\begin{equation}
+				\frac{\partial {\color{black}P}}{\partial t} \approx \frac{{\color{black}P_{in}} - {\color{black}P} }{\Delta t}
+		\end{equation}}
+
+		Such a simplified equation allows for instantaneous pressure.
+In a real system, the pressure dynamics would depend on the behaviour of the pump and the back-pressure regulator, which introduce additional inertia and resistance to pressure changes, leading to gradual pressure build-up.
+
+		\subsubsection{Extraction yield} \label{CH: Yield}
+
+		The process yield is calculated according to Equation \ref{Model_measurment_1}, as presented by \citet{Sovova1994a}.
+The measurement equation evaluates the solute's mass at the extraction unit outlet and sums it up.
+The integral form of the measurement (Equation \ref{Model_measurment_1}) can be transformed into the differential form (Equation \ref{Model_measurment_2}) and augmented with the process model.
+
+		{\footnotesize
+			\begin{align} 
+				\label{Model_measurment_1}
+				y &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
+				\cfrac{dy}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
+				\label{Model_measurment_2}
+		\end{align}	}
+
+		\subsubsection{Initial and boundary conditions} 
+		It is assumed that the solvent is free of solute at the beginning of the process $c_{f0}=0$, that all the solid particles have the same initial solute content $c_{s0}$ and that the system is isothermal, hence the initial state is $h_0$.
+The fluid at the inlet is considered not to contain any solute.
+The initial and boundary conditions are defined as follows:
+
+		{\footnotesize
+			\begin{align*}
+				&c_f(t = 0, z) = 0  && c_s(t = 0, z) = c_{s0} && h(t = 0, z) = h_0 \\
+				&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
+				&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0 \quad P(0) = P_0 \\
+		\end{align*} }
+
+		\subsubsection{Discretisation methods}
+
+		\begin{figure}[!h]
+			\centering
+			{\footnotesize
+				\begin{align*}
+					\dot{x} &= \cfrac{d x}{d t} = 
+					\begin{bmatrix}
+						\cfrac{d c_{f,1}}{d t} 	  \\
+						\vdots					  \\
+						\cfrac{d c_{f,N_z}}{d t} \\
+						\\ \hline \\
+						\cfrac{d c_{s,1}}{d t} 	  \\
+						\vdots					  \\
+						\cfrac{d c_{s,N_z}}{d t} \\
+						\\ \hline \\
+						\cfrac{d h_1}{d t} 	  \\
+						\vdots 					  \\
+						\cfrac{d h_{N_z}}{d t} \\
+						\\ \hline \\
+						\cfrac{d P}{d t} \\
+						\\ \hline \\
+						\cfrac{d y}{d t}
+					\end{bmatrix}
+					=
+					\underbrace{\begin{bmatrix}
+							G_1 \left( c_f,c_s,h; \Theta \right)\\ 
+							\vdots\\ 
+							G_{N_z} \left( c_f,c_s,h; \Theta \right)\\ 
+							\\ \hline \\ \\
+							G_{N_z+1} \left( c_f,c_s,h; \Theta \right)\\ 
+							\vdots\\
+							G_{2N_z} \left( c_f,c_s,h; \Theta \right)\\ 
+							\\ \\ \hline \\ 
+							G_{2N_z+1} \left( c_f,c_s,h; \Theta \right) \\
+							\vdots\\
+							G_{3N_z} \left( c_f,c_s,h; \Theta \right) \\ 
+							\\ \\ \hline \\
+							G_{3N_z+1} \left( c_f,c_s,h; \Theta \right) \\
+							\\ \\ \hline \\
+							G_{3N_z+2} \left( c_f,c_s,h; \Theta \right) 
+					\end{bmatrix}}_{G \left( x; \Theta \right)} 
+			\end{align*} }
+			\caption{Discretised state space.}
+			\label{fig:discretization}
+		\end{figure}
+
+		The method of lines is used to transform the process model equations into a set of ODEs denoted by $G(x;\Theta)$.
+For a derivative to be conservative, it must form a telescoping series.
+In other words, only the boundary terms should remain after adding all terms coming from the discretisation over a grid, and the artificial interior points should be cancelled out.
+Discretisation is applied to the conservative form of the model to ensure mass conservation.
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme approximates the second-order derivative $z$ direction.
+The length of the fixed bed is divided into $N_z$, i.e.
+equally distributed points in the $z$ direction.
+The state-space model after discretisation is denoted by $x$ and defined as shown in Figure \ref{fig:discretization}, where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.
+
+		\subsection{Optimal design of experiments} \label{CH: DOE}
+		\subsubsection{Bayesian estimation}
+
+		After selecting a process model and estimating its parameters based on initial experiments, additional experiments may be planned to further refine the estimates of the model coefficients.
+An optimal experimental design enables parameters to be estimated without bias and with minimum variance.
+A model-based approach to experimental design allows for the consideration of system complexity and constraints, such as practical infeasibility due to safety concerns.
+
+		Building on the work of \citet{Walter2010} and \citet{Himmelblau1970}, the Bayes theorem can be employed to define a general cost function:
+
+		{\footnotesize
+			\begin{equation}
+				\max p\left(\theta \mid Y, \Xi \right) = \frac{p\left(Y \mid \theta, \Xi\right) p\left(\theta\right)}{\int p\left(Y \mid \theta, \Xi\right) p\left(\theta\right) d\theta} \propto p\left(Y \mid \theta, \Xi\right) p\left(\theta\right)
+			\end{equation}
+		}
+
+		The aim of experimental design is to maximise the posterior probability of estimating $\theta$ ($p\left(\theta \mid Y, \Xi \right)$) given the prior distribution of $\theta$ ($p(\theta)$) obtained from previous experiments, and the likelihood of obtaining observations $Y~\left(p\left(Y \mid \theta, \Xi\right)\right)$ given $\theta$ and experimental conditions $\Xi$.
+The new observations $Y$, under a set of experimental conditions $\Xi$, are assumed to be normally distributed around the model output $y$, with measurement error covariance $\Sigma_Y$.
+Similarly, $\theta$ is assumed to be normally distributed around the true parameter values $\hat{\theta}$, with covariance matrix $\Sigma_\theta$ estimated from previous experiments.
+These probabilities are:
+
+		{\footnotesize
+			\begin{align} 
+				p\left(Y \mid \theta, \Xi \right) &= \frac{|\Sigma_Y|^{-1/2}}{\left(2\pi\right)^{n_Y/2}} \exp\left( -\frac{1}{2} \left(Y - y \right)^\top \Sigma_Y^{-1} \left(Y - y\right) \right) \\
+				p\left(\theta\right) &= \frac{|\Sigma_\theta|^{-1/2}}{\left(2\pi\right)^{n_\theta/2}} \exp\left( -\frac{1}{2} \left(\theta - \hat{\theta}\right)^\top \Sigma_\theta^{-1} \left(\theta - \hat{\theta}\right) \right)
+			\end{align}
+		}
+
+		where $n_Y$ is the number of observations and $n_\theta$ is the number of parameters to be estimated. Substituting these expressions into the cost function gives:
+
+		{\footnotesize 
+			\begin{equation} 
+				\ln p\left(\theta \mid Y, \Xi \right) \propto -\frac{1}{2} \left[ \left(Y - y\right)^\top \Sigma_Y^{-1} \left(Y - y\right) + \left(\theta - \hat{\theta}\right)^\top \Sigma_\theta^{-1} \left(\theta - \hat{\theta}\right) \right]
+		\end{equation} }
+
+		When linearising the model output around $\hat{\theta}$, the model output becomes $y = y(\hat{\theta}) + J \Delta_\theta$, where $J = \frac{\partial y(\hat{\theta})}{\partial \theta}$ is the Jacobian matrix evaluated at $\hat{\theta}$, and $\Delta_\theta = \theta - \hat{\theta}$.
+To simplify the equation, the residual term $\Delta_y = Y - y(\hat{\theta})$ is introduced.
+Substituting these into the expression for $\ln p\left(\theta \mid Y, \Xi \right)$ gives:
+
+		{\footnotesize 
+			\begin{flalign*} 
+				\ln p\left(\theta \mid Y, \Xi \right) &\propto -\frac{1}{2} \left[ \left(\Delta_y - J \Delta_\theta \right)^\top \Sigma_Y^{-1} \left(\Delta_y - J \Delta_\theta \right) + \Delta_\theta^\top \Sigma_\theta^{-1} \Delta_\theta \right] && \\
+				&= -\frac{1}{2} \left[ \Delta_y^\top \Sigma_Y^{-1} \Delta_y - 2 \Delta_y^\top \Sigma_Y^{-1} J \Delta_\theta + \Delta_\theta^\top \left( J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1} \right) \Delta_\theta \right] &&
+		\end{flalign*} }
+
+		This equation can be reformulated by expanding the quadratic terms:
+
+		{\footnotesize
+			\begin{flalign*}
+				\ln p\left(Y \mid \theta, \Xi \right) &\propto -\frac{1}{2} \left( \underbrace{r^\top \Sigma_Y^{-1} r}_{\mathcal{C}} - 2 \underbrace{ J^\top \Sigma_Y^{-1} \Delta_y }_{\mathcal{B}} \Delta_\theta + \Delta_\theta^\top \underbrace{\left( J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1} \right)}_{\mathcal{A}} \Delta_\theta \right) && \\
+				&=-\frac{1}{2} \left( \Delta_\theta^\top \mathcal{A} \Delta_\theta - 2 \mathcal{B}^\top \Delta_\theta + \mathcal{C} \right) &&
+			\end{flalign*}
+		}
+
+		By completing the square, we introduce $\theta^* = \hat{\theta} + \mathcal{A}^{-1} \mathcal{B}$, and the cost function becomes:
+
+		{\footnotesize 
+			\begin{equation} 
+				\ln p\left(\theta \mid Y, \Xi \right) \propto -\frac{1}{2} \left( \left( \theta - \theta^* \right)^\top \mathcal{A} \left( \theta - \theta^* \right) + \mathcal{C} - \mathcal{B}^\top \mathcal{A}^{-1} \mathcal{B} \right)
+		\end{equation} }
+
+		It can be observed that the quadratic term represents the spread of the posterior multivariate distribution around the mean $\theta^*$.
+The constant term $\mathcal{C} - \mathcal{B}^\top \mathcal{A}^{-1} \mathcal{B}$ is independent of $\theta$ and does not affect the shape of the posterior distribution but is still important for normalisation.
+This constant term is absorbed into the normalising constant of the posterior distribution.
+It does not affect the estimation of $\theta$ or the shape of the posterior distribution and thus can be neglected when focusing on parameter estimation or experimental design.
+Therefore, the posterior distribution of $\theta$ given $Y$ and $\Xi$ is:
+
+		{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) \propto \exp \left( -\frac{1}{2} \left( \theta - \theta^* \right)^\top \mathcal{A} \left( \theta - \theta^* \right) \right) \end{equation} }
+
+		This is the expression of a multivariate normal distribution with mean $\theta^*$ and covariance matrix $\mathcal{A}^{-1}$:
+
+		{\footnotesize \begin{equation} p\left(\theta \mid Y, \Xi \right) = \mathcal{N}\left( \theta^*, \mathcal{A}^{-1} \right) \end{equation} }
+
+		As the goal of optimal experimental design is to improve the precision of parameters, the main focus is on the matrix $\mathcal{A}$, which consists of two terms.
+The first corresponds to the information gained from new observations based on the model and measurement error ($J^\top \Sigma_Y^{-1} J$), while the second is the prior information ($\Sigma_\theta^{-1}$).
+
+		\subsubsection{Fisher Information}
+
+		The Fisher information $\mathcal{F}$ measures the amount of information that an observable random variable carries about an unknown parameter of the distribution that models the random variable.
+It is related to the negative expected value of the second derivative of the log-likelihood function with respect to the parameter, providing a measure of how "sensitive" the likelihood is to changes in the parameter value.
+
+		{\footnotesize \begin{equation} \mathcal{F}(\theta, \Xi) = -\mathop{\mathbb{E}}_{Y \mid \theta, \Xi} \left[ \frac{\partial^2 \ln p \left( Y \mid \theta, \Xi \right)}{\partial \theta \partial \theta^\top} \right] \end{equation} }
+
+		Under regularity conditions, the Fisher information can also be expressed as:
+
+		{\footnotesize \begin{equation} \mathcal{F}(\theta, \Xi) = \mathop{\mathbb{E}}_{Y \mid \theta, \Xi} \left[ \left( \frac{\partial \ln p\left( Y \mid \theta, \Xi \right)}{\partial \theta} \right) \left( \frac{\partial \ln p\left( Y \mid \theta, \Xi \right)}{\partial \theta} \right)^\top \right] \end{equation} }
+
+		By inserting the expression for $p\left( Y \mid \theta, \Xi \right)$ and performing similar manipulations as in the previous section, the Fisher information becomes:
+
+		{\footnotesize \begin{equation} \mathcal{F}(\theta, \Xi) = J^\top \Sigma_Y^{-1} J \end{equation} }
+
+		Since the likelihood is Gaussian and linearised, the second derivative of the log-likelihood with respect to $\theta$ simplifies to $J^\top \Sigma_Y^{-1} J$, and its negative expected value yields the same expression because the expectation of the Hessian is constant in this linear approximation.
+
+		The Cramer-Rao inequality requires that the covariance of any unbiased estimator $\hat{\theta}$ satisfies:
+
+		{\footnotesize \begin{equation} \operatorname{Cov}(\hat{\theta}) \geq \mathcal{F}^{-1}(\theta) \end{equation} }
+
+		The precision with which a parameter $\theta$ can be estimated is limited by the Fisher information of the likelihood function.
+Based on the Cramer-Rao inequality, the Fisher information matrix can be used to calculate the covariance matrices associated with maximum-likelihood estimates.
+
+		\subsubsection{Optimal experimental design}
+
+		The optimal design of experiments is a statistical concept that refers to the process of planning an experiment that allows parameters to be estimated without bias and with minimum variance.
+Optimal design ensures that the experiment can provide the most informative data possible.
+This often involves balancing the study of the main effects and interactions between factors.
+Moreover, by efficiently planning experiments, optimal design aims to reduce the overall resources required, such as time, materials and manpower.
+
+		The methodology for collecting data to estimate the parameters of a specific model is influenced by a series of qualitative decisions made throughout the experimental and modelling process, such as model structure, sensor locations or equipment choices.
+Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, etc.).
+Experiment design aims to determine the experimental conditions adapted to the final purpose of the modelling.
+
+		Considering that each scalar observation in a study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ represents the specific experimental conditions (such as sampling time, operating conditions, etc.) under which the $i$-th observation is gathered.
+When collecting $n_t$ such observations, the assembly of these $\xi_i$ vectors forms the matrix $\Xi = (\xi_1, \xi_2, \dots, \xi_{n_t})$, which combines all the experimental conditions that need optimisation.
+To align the design of the experiment with practical realities, it is important to take into account various constraints, such as the total duration of the experiments, the maximum temperature of the inlet stream or the minimum interval between sampling events.
+The set of all possible combinations for $\Xi$ that adhere to these constraints is denoted as $\bar{\Xi}$.
+
+		The formulation of a cost function $j$ allows the framing of optimal experiment design as a constrained optimisation problem. In this context, the optimal experiment, denoted as $\Xi^*$, is:
+
+		{\footnotesize \begin{equation} \Xi^* = \arg~\underset{\Xi \in \bar{\Xi}}{\text{opt}}~j\left(\Xi\right) \end{equation} }
+
+		The cost function should describe the amount of information obtained from an experiment.
+For that purpose, it can be assumed that function $\varkappa$ can be related to the covariance matrix $\mathcal{A}^{-1}$ obtained under arbitrary operating conditions:
+
+		{\footnotesize \begin{equation} j(\Xi) = \varkappa\left[ \mathcal{A}^{-1}(\theta, \Xi) \right] \end{equation} }
+
+		Taking into account that, in the Bayesian estimation framework, the posterior covariance matrix of the parameter estimates is given by $\Sigma = \mathcal{A}^{-1} = \left(J^\top \Sigma_Y^{-1} J + \Sigma_\theta^{-1}\right)^{-1} $.
+$J$ is the Jacobian matrix of the model outputs with respect to the parameters, $\Sigma_Y$ is the covariance matrix of the measurement errors and $\Sigma_\theta$ is the prior covariance matrix of the parameters.
+
+		\begin{figure}[!h]
+			\centering
+			\resizebox{0.9\columnwidth}{!}{%
+				\begin{tikzpicture}
+					% Ellipse parameters
+					\def\ellipsecenter{(3,3)}
+					\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
+					\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
+					\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow
+
+					% Draw the rotated ellipse
+					\draw[fill=gray!10, draw=black, rotate around={45:\ellipsecenter}] \ellipsecenter ellipse (3cm and 1cm);
+
+					% Draw the dashed rectangle
+					\draw[dashed] (0.75,0.75) rectangle (5.25,5.25);
+
+					% Draw the arrows and label them with adjustable positions
+					\draw [-latex] \ellipsecenter -- \ellipseA node[yshift=-4cm, xshift=2.5cm,rotate around={-45:\ellipsecenter}] {A-optimality};
+					\draw [-latex] \ellipsecenter -- \ellipseB node[yshift=0cm, xshift=-3.9cm,rotate around={45:\ellipsecenter}] {E-optimality};
+					\draw [-latex] \ellipseC -- (2,2) node[yshift=-1cm, xshift=2cm] {D-optimality};
+
+					% Draw axes
+					\draw[thick,->] (0,0) -- (6,0) node[below] {$\theta_1$};
+					\draw[thick,->] (0,0) -- (0,6) node[left] {$\theta_2$};
+				\end{tikzpicture}
+			}%
+			\caption{Graphical representation of score functions.}
+			\label{fig:score_fun}
+		\end{figure}
+
+		Equation \ref{EQ:DOE_general} shows the general type of DOE optimality criteria. Some of the DOE criteria have a graphical interpretation, as shown in Figure \ref{fig:score_fun}.
+
+		{\footnotesize 
+			\begin{align} \label{EQ:DOE_general}
+				\varkappa_k\left( \mathcal{A}^{-1}(\theta) \right) &= \left[ \frac{1}{n_\theta} \operatorname{trace}\left( Q \mathcal{A}^{-1}(\theta, \Xi) Q^\top \right)^k \right]^{1/k} & \text{if} \det \mathcal{A}^{-1} \neq 0 \nonumber \\
+				\varkappa_k\left( \mathcal{A}^{-1}(\theta) \right) &= \infty & \text{if} \det \mathcal{A}^{-1} = 0
+		\end{align} }
+
+		where $Q$ is the weighting matrix. The special case $k=1$ corresponds to the L-optimality cost function:
+
+		{\footnotesize \begin{equation} j_L(\Xi) = \operatorname{trace} \left( Q \mathcal{A}^{-1}(\theta, \Xi) Q^\top \right) \end{equation} }
+
+		Selection of $Q = \mathbf{I}_{n\theta}$ corresponds to the A-optimality cost function.
+An A-optimal experiment minimises the sum of the variances of the parameter estimates (i.e.
+the trace of the covariance matrix).
+When $Q$ is diagonal with $[Q]_{ii} = 1/\theta_i$, this corresponds to weighting the parameters inversely by their magnitude, which is associated with relative precision.
+
+		Selecting $Q$ as a row vector results in C-optimality, which focuses on linear combinations of parameters.
+Setting $Q = \mathbf{I}_{n\theta}$ and $k = \infty$ leads to E-optimality, where the design maximises the smallest eigenvalue of the covariance matrix $\mathcal{A}^{-1}(\theta, \Xi)$, thereby minimising the length of the largest axis of the asymptotic confidence ellipsoids.
+
+		The most commonly used criterion is D-optimality, which involves $k = 0$ and $Q = \mathbf{I}_{n\theta}$, requiring the minimisation of $\det \mathcal{A}^{-1}(\theta, \Xi)$, or correspondingly, the maximisation of:
+
+		{\footnotesize \begin{equation} j_D(\Xi) = \det \mathcal{A}(\theta, \Xi) \end{equation} }
+
+		Since $\det A(\theta, \Xi) = 1 / \det \mathcal{A}^{-1}(\theta, \Xi)$, maximising $\det \mathcal{A}$ is equivalent to minimising $\det \mathcal{A}^{-1}$.
+
+		The D-optimality (D-OED) criterion originates from the geometric interpretation of the determinant.
+A two-dimensional matrix with real number entries can represent two linear maps: one mapping the standard basis vectors to the rows and the other to the columns.
+In both cases, the images of the basis vectors form a parallelogram that represents the image of the unit square under the mapping.
+The absolute value of the determinant is the area of this parallelogram, reflecting the scale factor by which the matrix transforms areas.
+The signed value of the determinant indicates the area of the parallelogram, which is negative when the angle from the first to the second defining vector is clockwise.
+In a multi-dimensional case, the matrix maps the n-cube to an n-dimensional parallelotope.
+The determinant provides the signed n-dimensional volume of this parallelotope, describing the volume scaling factor of the linear transformation produced by the matrix.
+Based on this geometrical interpretation, a D-optimal experiment minimises the volume of the asymptotic confidence ellipsoids for the parameters.
+
+		\subsubsection{Problem formulation}
+
+		Details on the process model can be found in \citet{Sliczniuk2024}.
+The model's empirical correlations were derived based on laboratory experiments conducted under various but constant operating conditions: $30 - 40~^\circ\text{C}$, $100 - 200$ bar and $3.33 \cdot 10^{-5} - 6.67 \cdot 10^{-5}$ kg/s.
+This study employs the process model obtained previously to design a set of supplementary experiments with dynamically changing conditions to improve the precision of the correlation for $D_i$.
+The analysed correlations consist of three independent variables: mass flow rate, pressure and inlet temperature.
+
+		In this work, the decision variables are the inlet temperature ($T^{\text{in}}$) and mass flow rate ($F$), while the pressure is assumed to remain constant during each batch.
+The optimal design of experiments problem is solved for multiple values of pressure: 100, 125, 150, 175 and 200 bar.
+The initial state is considered isothermal, so $T^0(z) = T^{\text{in}}(t=0)$.
+
+		The decision variables are adjusted every 10 minutes and are kept constant within each interval (piecewise constant controls).
+These controls have lower and upper bounds that match the validated range of the process model detailed by \citet{Sliczniuk2024}.
+The sampling time is assumed to be 5 minutes, and the total extraction time 600 minutes.
+The standard deviation $\sigma^2$ is estimated to be 0.03.
+
+		In a real system, the mass flow rate and inlet temperature cannot be changed instantaneously to any arbitrary value, as they depend on the dynamics of the pump and heat exchanger, respectively.
+To prevent the bang-bang type of control, a penalty term is introduced.
+Inspired by control problems such as the linear quadratic regulator, a quadratic penalty term is added to the cost function.
+This penalty increases the cost function value when there are rapid changes in the decision variables.
+The matrix $\mathcal{R}$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$.
+The problem formulation is given by Equation \ref{EQ:Formulation_2}:
+
+		{\footnotesize 
+			\begin{equation}
+				\begin{aligned}
+					\Xi^* &= \arg \min_{T^{\text{in}}(t), F(t)} 
+					\int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + 
+					\frac{du(t)^\top}{dt} \, \bar{R} \, \frac{du(t)}{dt} \right] dt, \\
+					\text{subject to:} \quad 
+					& \dot{x} = G(x, t, \theta; \Xi), \\
+					& t_0 = 0 \, \text{min}, \quad t_f = 600 \, \text{min}, \\
+					& T^0 = T^{\text{in}}(t=0), \\
+					& P(t) \in \{100, 125, 150, 175, 200\} \, \text{bar}, \\
+					& 31^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\
+					& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5}, \\
+					& \mathcal{R} = 
+					\begin{bmatrix} 
+						0.1 & 0 \\ 
+						0 & 0.01 
+					\end{bmatrix}, \\
+					& \frac{du(t)}{dt} = 
+					\begin{bmatrix} 
+						\dfrac{dF(t)}{dt} \\ 
+						\dfrac{dT^{\text{in}}(t)}{dt} 
+					\end{bmatrix}.
+				\end{aligned}
+				\label{EQ:Formulation_2}
+		\end{equation} }
 
@@
 		\section{Results}
-\subfile{Sections/Results_DOE}
+		To identify a global solution for Equation \ref{EQ:Formulation_2}, the optimisation problem is solved multiple times, each run starting from a random initial solution sampled from a uniform distribution.
+Figure \ref{fig:scatter} compares the initial and final cost function values across multiple optimisation runs for all pressure cases.
+The solution with the lowest cost function value is considered the global solution for each case.
 
-\section{Conclusions} \label{CH: Conclusion}
-This paper introduce the D-optimal experimental design (D-OED) as a model-based method for determining optimal experimental procedures in chemical engineering problems.
-D-OED optimizes an objective function, which can be geometrically interpreted as minimizing the volume of the uncertainty ellipsoid, thereby maximizing the precision of parameter estimates.
+		\begin{figure}[h!]
+			\centering
+			\includegraphics[width=0.90\columnwidth]{Figures/Results/scatter.png}	
+			\caption{Initial vs final values of the cost function.}
+			\label{fig:scatter}
+		\end{figure}
+
+		By analysing the locations of the clusters in Figure \ref{fig:scatter}, it can be concluded that experiments conducted near the critical point provide more information regarding the correlation than those conducted farther from it.
+For each pressure case, the solutions with the lowest value of the objective function are analysed further.
+The closer the pressure to the critical point, the larger the deviations in the physical properties of $CO_2$ caused by changes in the controls, leading to greater variation in the Reynolds number, and consequently to more informative experiments.
+
+		As presented in Figure \ref{fig:profiles_F}, all mass flow rate profiles initially stay at a minimum value, persisting for 100 to 150 minutes, depending on the pressure.
+Subsequently, a step-like increase in mass flow rate is observed, with the onset occurring earlier at higher pressures.
+Between 250 min and 300 min, the mass flow rate stabilises at the value of the upper bound.
+
+		\begin{figure}[t!]
+			\centering
+			\begin{subfigure}[t]{\columnwidth}
+				\centering
+				\includegraphics[width=0.90\columnwidth]{Figures/Results/Profile_F.png}	
+				\caption{Optimal mass flow rate profiles}
+				\label{fig:profiles_F}
+			\end{subfigure}%
+			\par\bigskip % force a bit of vertical whitespace
+			\begin{subfigure}[t]{\columnwidth}
+				\centering
+				\includegraphics[width=0.90\columnwidth]{Figures/Results/Profile_T.png}	
+				\caption{Optimal inlet temperature profile}
+				\label{fig:profiles_T}
+			\end{subfigure}
+			\par\bigskip % force a bit of vertical whitespace
+			\begin{subfigure}[t]{\columnwidth}
+				\centering
+				\includegraphics[width=0.90\columnwidth]{Figures/Results/yield.png}	
+				\caption{Optimal yield profiles}
+				\label{fig:profiles_y}
+			\end{subfigure}
+			\caption{Results of the optimisation problem.}
+		\end{figure}
+
+		Figure \ref{fig:profiles_T} shows the optimal profiles of the inlet temperature ($T^{in}$) for various pressure cases in the supercritical CO$_2$ extraction process.
+Initially, the $T^{in}$ remains constant at approximately $40~^\circ C$ for all pressures, indicating a stable starting condition for the system.
+The temperature decreases after about 300 min, but the exact time varies slightly depending on the pressure.
+This decline is rapid for lower pressures and gradual for higher pressures.
+The blue curve (100 bar) exhibits the sharpest temperature drop, while the green curve (200 bar) demonstrates a slower and more gradual decline.
+At lower pressures, the final temperature reaches the critical temperature and remains steady until the end of the batch.
+In contrast, the higher pressure cases result in a less significant temperature reduction.
+Moreover, the system does not reach steady operating conditions, as the inlet temperature profile does not flatten by the end of the process.
+
+		Figure \ref{fig:profiles_y} depicts the predicted yield curves.
+A closer examination of the yield and scatter plots reveals that the most informative experiments do not necessarily correspond to those with the highest yield.
+When the D-optimality criterion is applied, the aim is to maximise the determinant of the Fisher information matrix across the experimental design space.
+This approach identifies conditions that amplify variations in observed responses, particularly in regions with high sensitivity to parameter changes.
+As a result, the yield curve may display a "wavy" pattern, characterised by oscillations rather than a smooth, monotonic trend.
+These fluctuations arise from increased multiple critical points - local maxima, minima or saddle points - on the response surface.
+By maximising the sum of determinants of the Fisher information matrix, the experimental design prioritises regions of high curvature, where the response changes sharply.
+
+		Alternatively, the D-optimality problem can be understood through the concept of Gaussian curvature.
+In this view, the experimental design shapes the parameter space of a model into a manifold with local geometry defined by the Fisher information matrix.
+The D-optimality condition maximises the determinant of this matrix, which geometrically corresponds to maximising the product of the principal curvatures of the manifold at a given point.
+This determinant is directly proportional to the Gaussian curvature, linking experimental design to the geometry of the parameter space.
+The determinant of the Fisher information matrix can be interpreted as a measure of the "volume element" on the parameter manifold, with higher values indicating regions of greater local curvature.
+By maximising this determinant, the parameter manifold is locally as curved as possible, which explains the wavy behaviour of the yield curves.
+
+		The results and observations discussed in this article are local and should be considered valid only for the model presented in \citet{Sliczniuk2024}.
+Although general conclusions about the curvature of the yield curve are independent of the process model, a completely different set of control profiles should be expected if the same technique is applied to a different model.
+Such strong dependence on the model is one of the most significant limitations of this work.
+Moreover, the model predicts the data set in a region which has not been validated during previous experiments.
+On the one hand, this leaves room for model validation, while on the other hand, the obtained set of data points might differ from the predictions.
+
+		\section{Conclusion } \label{CH: Conclusion}
+		This paper introduces D-optimal experimental design (D-OED) as a model-based method for determining optimal	experimental procedures in chemical engineering problems.
+D-OED optimises an objective function, which can be geometrically	interpreted as minimising the volume of the uncertainty ellipsoid, thereby maximising the precision of parameter estimates.
 Compared to the classical formulation of D-OED, this work introduces a penalty term to the cost function to prevent unrealistic rapid changes in operating conditions, ensuring practical feasibility in experimental	implementation.
@@
 
-The analysis was conducted for multiple pressure cases, and the optimal mass flow rate profiles were similar across all instances.
-The inlet temperature profiles show different patterns, but all of them start with high temperature and decrease in the second half of the batch.
+		The analysis was conducted for multiple pressure cases and the optimal mass flow rate profiles were similar across all instances.
+The inlet temperature profiles show different patterns, but all start with high temperature that decreases in	the second half of the batch.
 The resulting yield curves exhibit distinct wavy patterns, which can be explained through	the relationship between the Hessian matrix and the Gaussian curvature of a multi-variable function.
 The determinant of the Fisher information matrix, central to the D-optimality criterion, is proportional to the Gaussian curvature of the parameter manifold.
-This curvature reflects the system's sensitivity to parameter changes and is maximized by the D-OED method.
-The observed wavy behavior of the yield curves is thus a manifestation of the high-curvature regions identified by the optimization, where the system's response to experimental conditions is most informative.
+This curvature reflects the system’s sensitivity to parameter changes and is maximised by the D-OED method.
+The observed wavy behaviour of the yield curves is thus a manifestation of the high-curvature regions identified by the optimisation, where the system’s response to experimental conditions is most informative.
 
 		Further analysis of the yield curves and scatter plots reveals that the informativeness of experiments varies significantly across different operating conditions.
-This variation depends on the physical properties of CO$_2$, which strongly change around the critical point.
-Consequently, it is concluded that operating conditions must be carefully selected to the specific regime of interest to maximize the information gained.
-This observation emphasizes the importance of aligning experimental strategies with the system's underlying physical properties and model structure.
+This variation depends on the physical properties of CO$_2$, which change	significantly around the critical point.
+Consequently, it is concluded that operating conditions must be carefully selected for the specific regime of interest to maximise the information gained.
+This observation emphasises the importance of aligning experimental strategies with the system’s underlying physical properties and model structure.
 
@@
 
-\clearpage
-\newpage
+%\clearpage
+%\newpage
 
+\nomenclature[A]{\(A\)}{Information matrix}
+\nomenclature[A]{\(B\)}{Weighted score vector}
+\nomenclature[A]{\(C\)}{Weighted sum of squared deviations}
+\nomenclature[A]{\(\mathcal{F}\)}{Fisher information}
+\nomenclature[A]{\(\mathcal{R}\)}{Control cost matrix}
+\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{m²}}
+\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{m²}}
+\nomenclature[A]{\(B\)}{Pressure dependent parameter of P-R EoS \nomunit{m²}}
+\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/m³}}
+\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m³}}
+\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/m³}}
+\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/m³}}
+\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m³}}
+\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/m³}}
+\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/m³}}
+\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/m³}}
+\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{m²/s}}
+\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{m²/s}}
+\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{m²/s}}
+\nomenclature[A]{\(e\)}{Internal energy \nomunit{J/kg}}
+\nomenclature[A]{\(F\)}{Mass flow rate \nomunit{kg/s}}
+\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
+\nomenclature[A]{\(h\)}{Enthalpy \nomunit{kJ/kg}}
+\nomenclature[A]{\(J\)}{Jacobian}
+\nomenclature[A]{\(j\)}{Objective function}
+\nomenclature[A]{\(k_m\)}{Mass partition coefficient}
+\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient}
+\nomenclature[A]{\(L\)}{Length of the fixed bed \nomunit{m}}
+\nomenclature[A]{\(l\)}{Characteristic dimension of particles \nomunit{m}}
+\nomenclature[A]{\(n_\theta\)}{Number of analyzed parameters}
+\nomenclature[A]{\(n_y\)}{Number of measurements}
+\nomenclature[A]{\(N_z\)}{Number of discretized points in z-direction}
 \nomenclature[A]{\(P\)}{Pressure \nomunit{bar}}
+\nomenclature[A]{\(p\)}{Probability distribution model}
+\nomenclature[A]{\(P_r\)}{Reduced pressure}
+\nomenclature[A]{\(Q\)}{Weighting matrix}
+\nomenclature[A]{\(r\)}{Particle radius \nomunit{m}}
+\nomenclature[A]{\(Re\)}{Reynolds number}
+\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/m³/s}}
 \nomenclature[A]{\(T\)}{Temperature \nomunit{K}}
+\nomenclature[A]{\(t\)}{Time \nomunit{s}}
+\nomenclature[A]{\(t_0\)}{Initial extraction time \nomunit{s}}
+\nomenclature[A]{\(t_f\)}{Total extraction time \nomunit{s}}
+\nomenclature[A]{\(T_r\)}{Reduced temperature}
 \nomenclature[A]{\(T_{in}\)}{Inlet temperature \nomunit{K}}
 \nomenclature[A]{\(T_{out}\)}{Outlet temperature \nomunit{K}}
-\nomenclature[A]{\(F\)}{Mass flow rate \nomunit{kg/s}}
 \nomenclature[A]{\(u\)}{Superficial velocity \nomunit{m/s}}
 \nomenclature[A]{\(v\)}{Linear velocity \nomunit{m/s}}
+\nomenclature[A]{\(x\)}{State vector}
+\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
+\nomenclature[A]{\(y\)}{Predicted extraction yield \nomunit{g}}
+\nomenclature[A]{\(Z\)}{Compressibility factor}
 \nomenclature[A]{\(z\)}{Spatial direction \nomunit{m}}
-\nomenclature[A]{\(e\)}{Internal energy \nomunit{J/kg}}
-%\nomenclature[A]{\(e^y\)}{Output error}
-\nomenclature[A]{\(h\)}{Enthalpy \nomunit{kJ/kg}}
-\nomenclature[A]{\(t\)}{Time \nomunit{s}}
-\nomenclature[A]{\(t_f\)}{Total extraction time \nomunit{s}}
-\nomenclature[A]{\(t_0\)}{Initial extraction time \nomunit{s}}
-\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{m$^2$}}
-\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{m$^2$}}
-\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/m$^3$}}
-\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{m$^2$/s}}
-\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/m$^3$/s}}
-\nomenclature[A]{\(L\)}{Length of the fixed bed \nomunit{m}}
-\nomenclature[A]{\(j\)}{Objective function \nomunit{-}}
-\nomenclature[A]{\(j_{ml}\)}{Maximum Likelihood \nomunit{-}}
-\nomenclature[A]{\(S\)}{Sensitivity equations \nomunit{-}}
-\nomenclature[A]{\(Q\)}{Weighting matrix \nomunit{-}}
-\nomenclature[A]{\(\mathcal{R}\)}{Control cost matrix \nomunit{-}}
-%\nomenclature[A]{\(\textbf{G}\)}{Augumented system}
-%\nomenclature[A]{\(\dot{S}\)}{Time derivative of sensitivity equations}
-%\nomenclature[A]{\(\bar{S}\)}{Sensitivity matrix}
-%\nomenclature[A]{\(\bar{J}_x\)}{Jacobian matrix with respect to the state space}
-%\nomenclature[A]{\(\bar{J}_\Theta\)}{Jacobian matrix with respect to the paramters}
-%\nomenclature[A]{\(\mathcal{L}\)}{Log-likelihood function}
-\nomenclature[A]{\(l\)}{Characteristic dimension of particles \nomunit{m}}
-\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{m$^2$/s}}
-\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{m$^2$/s}}
-\nomenclature[A]{\(r\)}{Particle radius \nomunit{m}}
-\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient \nomunit{-}}
-\nomenclature[A]{\(k_m\)}{Mass partition coefficient \nomunit{-}}
-\nomenclature[A]{\(y\)}{Extraction yield \nomunit{g}}
-%\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
-\nomenclature[A]{\(x\)}{State vector}
-\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
-\nomenclature[A]{\(p\)}{Probaility disribution model}
-\nomenclature[A]{\(R_e\)}{Reynolds number}
-\nomenclature[A]{\(\mathcal{F}\)}{Fisher information}
 
-\nomenclature[B]{\(\rho_f\)}{Fluid density\nomunit{kg/m$^3$}}
-\nomenclature[B]{\(\Phi\)}{Bed porosity \nomunit{-}}
-\nomenclature[B]{\(\rho_s\)}{Bulk density of solid\nomunit{kg/m$^3$}}
-\nomenclature[B]{\(\mu\)}{Sphericity coefficient \nomunit{-}}
-\nomenclature[B]{\(\pi\)}{Probability desnsity \nomunit{-}}
-\nomenclature[B]{\(\gamma\)}{Decaying function \nomunit{-}}
-\nomenclature[B]{\(\Upsilon\)}{Decay coefficient \nomunit{-}}
-\nomenclature[B]{\(\Theta\)}{Paramter space \nomunit{-}}
-\nomenclature[B]{\(\theta\)}{vector of unknown parameters \nomunit{-}}
-\nomenclature[B]{\(\epsilon\)}{Unobervable error \nomunit{-}}
-\nomenclature[B]{\(\sigma\)}{Standard deviation \nomunit{-}}
-\nomenclature[B]{\(\Sigma\)}{Covariance matrix \nomunit{-}}
-\nomenclature[B]{\(\xi\)}{Vector of experimental condtions \nomunit{-}}
-\nomenclature[B]{\(\Xi\)}{Matrix of experimental condtions \nomunit{-}}
+% Greek symbols
+\nomenclature[B]{\(\alpha\)}{Temperature-dependent function in the P-R EoS}
+\nomenclature[B]{\(\Delta_\theta\)}{Residual term of the parameters}
+\nomenclature[B]{\(\Delta_y\)}{Residual term of the measurement error \nomunit{g}}
+\nomenclature[B]{\(\epsilon\)}{Unobservable error}
+\nomenclature[B]{\(\gamma\)}{Decaying function}
+\nomenclature[B]{\(\kappa\)}{Quadratic function of the acentric factor}
+\nomenclature[B]{\(\mu\)}{Sphericity coefficient}
+\nomenclature[B]{\(\phi\)}{Bed porosity}
+\nomenclature[B]{\(\pi\)}{Probability density}
+\nomenclature[B]{\(\rho_f\)}{Fluid density \nomunit{kg/m³}}
+\nomenclature[B]{\(\rho_s\)}{Bulk density of solid \nomunit{kg/m³}}
+\nomenclature[B]{\(\Sigma\)}{Covariance matrix}
+\nomenclature[B]{\(\sigma\)}{Standard deviation}
+\nomenclature[B]{\(\Sigma_\theta\)}{Parameter uncertainty matrix}
+\nomenclature[B]{\(\Sigma_Y\)}{Measurement covariance matrix}
+\nomenclature[B]{\(\Theta\)}{Parameter space}
+\nomenclature[B]{\(\theta\)}{Vector of analysed parameters}
+\nomenclature[B]{\(\Upsilon\)}{Decay coefficient}
+\nomenclature[B]{\(\varkappa\)}{An arbitrary function of \(\mathcal{A}\)}
+\nomenclature[B]{\(\Xi\)}{Matrix of experimental conditions}
+\nomenclature[B]{\(\xi\)}{Vector of experimental conditions}
 
+% Abbreviations
 \nomenclature[C]{BIC}{Broke-and-Intact Cell model}
-%\nomenclature[C]{MLE}{Maximum Likelihood Estimation}
+\nomenclature[C]{DoE}{Design of Experiment}
+\nomenclature[C]{HBD}{Hot Ball Diffusion}
+\nomenclature[C]{m-DoE}{Model-based Design of Experiment}
+\nomenclature[C]{P-R EoS}{Peng-Robinson Equation of State}
+\nomenclature[C]{SC}{Shrinking Core}
 \nomenclature[C]{SFE}{Supercritical Fluid Extraction}
-\nomenclature[C]{DoE}{Design of Experiment}
-\nomenclature[C]{m-DoE}{Model-based Design of Experiment}
-\nomenclature[C]{HBD}{Hot Ball Diffusion}
-\nomenclature[C]{SC}{Shrinking Core}
-
 \printnomenclature

### 2025-09-14 Article_Design_of_Experiment-Chamomile.tex
14.09

@@
 \usepackage{graphicx,float}
+\restylefloat{table}
 \usepackage{adjustbox}
@@
 	\item[\bfseries
-	\ifstrequal{#1}{A}{}{%
-		\ifstrequal{#1}{B}{Greek symbols}{%
-			\ifstrequal{#1}{C}{Abberivations}{
-	}}}%
+	\ifstrequal{#1}{A}{Latin symbols}{%
+		\ifstrequal{#1}{B}{Non-lation symbols}{%
+			\ifstrequal{#1}{C}{Greek symbols}{%
+				\ifstrequal{#1}{D}{Abberivations}{
+	}}}}%
 	]}
@@
 \usepackage[final]{pdfpages}
+
+\usepackage{multirow}
 
@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-The empirical correlations used in the model are based on a set of laboratory experiments performed under multiple constant operating conditions: $30 - 40~^\circ$C, $100 - 200$ bar and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The empirical correlations used in the model are based on laboratory experiments performed under multiple constant operating conditions: $30 - 40~^\circ$C, $100 - 200$ bar and $3.33-6.67 \cdot 10^{-5}$ kg/s.
 A model-based design of experiments with the D-optimality criterion is applied to improve the precision of the correlation parameters by designing a new dynamic experiment.
@@
 
-The present study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques in addition to the modelling of this process.
+Although the processes discussed are based on different phenomena, the outcome of these technologies strongly depends on the solubility in supercritical CO$_2$.
+The solubility of the solid in the solvent can be important for determining the partition coefficient for a potential impregnation and whether a cosolvent should be used in a supercritical extraction of a compound.
+Moreover, a good solute solubility not only accelerates the initial stages of the extraction but also reduces the time of the extraction process.
+Multiple researchers, such as \citet{Bagheri2025}, \citet{Tabebordbar2024}, \citet{SheikhiKouhsar2024} or \citet{Bagheri2022}, have conducted extensive research to measure the solubility of different solutes in the supercritical CO$_2$ and on the development of mathematical models.
+Several methods, including density-based correlations and equation of state, are used for correlations of solute solubility in the supercritical CO$_2$.
+The semi-empirical models are often used due to their ease of use and the absence of the need for physicochemical properties like sublimation pressure and critical features, which cannot be directly measured experimentally.
+
+The present study investigates the extraction of essential oil from chamomile flowers (\textit{Matricaria chamomilla L.}) via supercritical fluid extraction techniques in addition to the modelling of this process.
 Chamomile is a medicinal herb widely cultivated in southern and eastern Europe - in countries such as Germany, Hungary, France and Russia.
@@
 
+This study is, to the authors knowledge, the first application of m-DoE with a D-optimality criterion to SFE, contrasted with prior SFE studies that relied on static factorial/RSM designs.
+Calculations are performed on the full dynamic model to compute exact trajectory-wise Jacobians that drive both the sensitivity study and the information measure.
+On the experimental-design side, the traditional approach of D-criterion formulate a practically implementable DoE with piecewise-constant inputs and a quadratic move-penalty.
+The m-DoE is solved for various values of pressure (which is assumed to be cosntant during each batch) to assess the non-trivial impact of operating conditions on the model output.
+
 % ===================================================
@@
 
-where $\rho_f$ is the density of the fluid, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time, and $z$ is the spatial direction.
+where $\rho_f$ is the fluid density, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $T$ is the temperature, $t$ is time, and $z$ is the spatial direction.
+
+Equation \ref{EQ: CompressibleEuler_1}-\ref{EQ: CompressibleEuler_3} are the quasi-one-dimensional conservation laws for a variable-area duct representing a packed bed under the quasi-1D and low-Mach assumptions.
+Equation (\ref{EQ: CompressibleEuler_1}) (continuity) enforces conservation of mass is convected axially with velocity.
+Equation (\ref{EQ: CompressibleEuler_2}) (axial momentum) balances the momentum of the fluid parcel with the pressure gradient.
+The viscous wall/porous drag and body forces are neglected in the control-oriented model because pressure is imposed and nearly uniform in the low-velocity regime.
+Equation (\ref{EQ: CompressibleEuler_3}) (energy) transports internal energy by advection, includes pressure work, and accounts for axial heat conduction via the effective conductivity.
+The details on treatment of the governing equations are presented in Section \ref{CH: Extraction_model}.
 
@@
 
+		The residuals between the predicted and observed values were used to compute an unbiased estimate of the error variance.
+This variance, combined with the inverse of the design matrix's Gram matrix, yielded the covariance matrix of the coefficient estimates.
+The standard deviations (standard errors) of the coefficients were then obtained as the square roots of the diagonal elements of this covariance matrix.
+The variance-covariance is presented in Table \ref{tab:Uncertainty}.
+
+		\begin{table}[h!]
+			\centering
+			\resizebox{0.75\columnwidth}{!}{%
+				$
+				\begin{gathered}
+					\begin{array}{c|ccc}
+						& \sigma(D_i^R(0)) & \sigma(Re) & \sigma(F) \\
+						\hline
+						\sigma(D_i^R(0)) & 0.0817  &  0.0065 &  -0.0139 \\
+						\sigma(Re)       & 0.0065  &  1.6908 &  -0.0825 \\
+						\sigma(F)        & -0.0139 & -0.0825 &  0.0065 \\
+					\end{array}
+					\\[1.5em]
+					\begin{array}{c|ccc}
+						& \sigma(\Upsilon(0)) & \sigma(Re) & \sigma(F) \\
+						\hline
+						\sigma(\Upsilon(0)) & 0.1727  &  0.0138 &  -0.0294 \\
+						\sigma(Re)          & 0.0138  &  3.5732 &  -0.1744 \\
+						\sigma(F)           & -0.0294 & -0.1744 &  0.0137 \\
+					\end{array}
+				\end{gathered}
+				$
+			}
+			\caption{Variance–covariance matrices for $D_i^R$ (top) and $\Upsilon$ (bottom)}
+			\label{tab:Uncertainty}
+		\end{table}
+
 		\subsubsection{Heat balance} \label{CH: heat_balance}
@@
 			\begin{equation}
-				\min_T \left( \underbrace{h\left(t,x\right)}_{\text{Heat balance}} - \underbrace{h\left(T,P,o_f\left(T,P\right)\right)}_{\text{Departure function}} \right)^2
+				\min_T \left( \underbrace{h\left(t,x\right)}_{\text{Heat balance}} - \underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}} \right)^2
 				\label{EQ:Enthalpy_root}
@@
 The sampling time is assumed to be 5 minutes, and the total extraction time 600 minutes.
-The standard deviation $\sigma^2$ is estimated to be 0.03.
 
@@
 
-		\section{Conclusion } \label{CH: Conclusion}
+		\section{Conclusion} \label{CH: Conclusion}
 		This paper introduces D-optimal experimental design (D-OED) as a model-based method for determining optimal	experimental procedures in chemical engineering problems.
@@
 
-%\clearpage
+\clearpage
 %\newpage
 
-\nomenclature[A]{\(A\)}{Information matrix}
-\nomenclature[A]{\(B\)}{Weighted score vector}
-\nomenclature[A]{\(C\)}{Weighted sum of squared deviations}
-\nomenclature[A]{\(\mathcal{F}\)}{Fisher information}
-\nomenclature[A]{\(\mathcal{R}\)}{Control cost matrix}
-\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{m²}}
-\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{m²}}
-\nomenclature[A]{\(B\)}{Pressure dependent parameter of P-R EoS \nomunit{m²}}
-\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/m³}}
-\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m³}}
-\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/m³}}
-\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/m³}}
-\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m³}}
-\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/m³}}
-\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/m³}}
-\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/m³}}
-\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{m²/s}}
-\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{m²/s}}
-\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{m²/s}}
+\nomenclature[A]{\(A\)}{Information matrix \nomunit{[-]}}
+\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{$m^2$}}
+\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{$m^2$}}
+\nomenclature[A]{\(B\)}{Pressure dependent parameter of P-R EoS \nomunit{$m^2$}}
+\nomenclature[A]{\(B\)}{Weighted score vector \nomunit{[-]}}
+\nomenclature[A]{\(C\)}{Weighted sum of squared deviations \nomunit{[-]}}
+\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/$m^3$}}
+\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{$m^2$/s}}
+\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{$m^2$/s}}
+\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{$m^2$/s}}
 \nomenclature[A]{\(e\)}{Internal energy \nomunit{J/kg}}
 \nomenclature[A]{\(F\)}{Mass flow rate \nomunit{kg/s}}
-\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
+\nomenclature[A]{\(G\)}{Vector of discretized differential equations \nomunit{[-]}}
 \nomenclature[A]{\(h\)}{Enthalpy \nomunit{kJ/kg}}
-\nomenclature[A]{\(J\)}{Jacobian}
-\nomenclature[A]{\(j\)}{Objective function}
-\nomenclature[A]{\(k_m\)}{Mass partition coefficient}
-\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient}
+\nomenclature[A]{\(J\)}{Jacobian \nomunit{[-]}}
+\nomenclature[A]{\(j\)}{Objective function \nomunit{[-]}}
+\nomenclature[A]{\(k_m\)}{Mass partition coefficient \nomunit{[-]}}
+\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient \nomunit{[-]}}
 \nomenclature[A]{\(L\)}{Length of the fixed bed \nomunit{m}}
 \nomenclature[A]{\(l\)}{Characteristic dimension of particles \nomunit{m}}
-\nomenclature[A]{\(n_\theta\)}{Number of analyzed parameters}
-\nomenclature[A]{\(n_y\)}{Number of measurements}
-\nomenclature[A]{\(N_z\)}{Number of discretized points in z-direction}
+\nomenclature[A]{\(n_\theta\)}{Number of analyzed parameters \nomunit{[-]}}
+\nomenclature[A]{\(n_y\)}{Number of measurements \nomunit{[-]}}
+\nomenclature[A]{\(N_z\)}{Number of discretized points in z-direction \nomunit{[-]}}
 \nomenclature[A]{\(P\)}{Pressure \nomunit{bar}}
-\nomenclature[A]{\(p\)}{Probability distribution model}
-\nomenclature[A]{\(P_r\)}{Reduced pressure}
-\nomenclature[A]{\(Q\)}{Weighting matrix}
+\nomenclature[A]{\(P_r\)}{Reduced pressure \nomunit{[-]}}
+\nomenclature[A]{\(p\)}{Probability distribution model \nomunit{[-]}}
+\nomenclature[A]{\(Q\)}{Weighting matrix \nomunit{[-]}}
+\nomenclature[A]{\(Re\)}{Reynolds number \nomunit{[-]}}
 \nomenclature[A]{\(r\)}{Particle radius \nomunit{m}}
-\nomenclature[A]{\(Re\)}{Reynolds number}
-\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/m³/s}}
+\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/$m^3$/s}}
 \nomenclature[A]{\(T\)}{Temperature \nomunit{K}}
+\nomenclature[A]{\(T_{in}\)}{Inlet temperature \nomunit{K}}
+\nomenclature[A]{\(T_{out}\)}{Outlet temperature \nomunit{K}}
+\nomenclature[A]{\(T_r\)}{Reduced temperature \nomunit{[-]}}
 \nomenclature[A]{\(t\)}{Time \nomunit{s}}
@@
 \nomenclature[A]{\(t_f\)}{Total extraction time \nomunit{s}}
-\nomenclature[A]{\(T_r\)}{Reduced temperature}
-\nomenclature[A]{\(T_{in}\)}{Inlet temperature \nomunit{K}}
-\nomenclature[A]{\(T_{out}\)}{Outlet temperature \nomunit{K}}
 \nomenclature[A]{\(u\)}{Superficial velocity \nomunit{m/s}}
 \nomenclature[A]{\(v\)}{Linear velocity \nomunit{m/s}}
-\nomenclature[A]{\(x\)}{State vector}
+\nomenclature[A]{\(x\)}{State vector \nomunit{[-]}}
 \nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
 \nomenclature[A]{\(y\)}{Predicted extraction yield \nomunit{g}}
-\nomenclature[A]{\(Z\)}{Compressibility factor}
+\nomenclature[A]{\(Z\)}{Compressibility factor \nomunit{[-]}}
 \nomenclature[A]{\(z\)}{Spatial direction \nomunit{m}}
 
+% Non-latin symbols
+\nomenclature[B]{\(\mathcal{F}\)}{Fisher information \nomunit{[-]}}
+\nomenclature[B]{\(\mathcal{R}\)}{Control cost matrix \nomunit{[-]}}
+
 % Greek symbols
-\nomenclature[B]{\(\alpha\)}{Temperature-dependent function in the P-R EoS}
-\nomenclature[B]{\(\Delta_\theta\)}{Residual term of the parameters}
-\nomenclature[B]{\(\Delta_y\)}{Residual term of the measurement error \nomunit{g}}
-\nomenclature[B]{\(\epsilon\)}{Unobservable error}
-\nomenclature[B]{\(\gamma\)}{Decaying function}
-\nomenclature[B]{\(\kappa\)}{Quadratic function of the acentric factor}
-\nomenclature[B]{\(\mu\)}{Sphericity coefficient}
-\nomenclature[B]{\(\phi\)}{Bed porosity}
-\nomenclature[B]{\(\pi\)}{Probability density}
-\nomenclature[B]{\(\rho_f\)}{Fluid density \nomunit{kg/m³}}
-\nomenclature[B]{\(\rho_s\)}{Bulk density of solid \nomunit{kg/m³}}
-\nomenclature[B]{\(\Sigma\)}{Covariance matrix}
-\nomenclature[B]{\(\sigma\)}{Standard deviation}
-\nomenclature[B]{\(\Sigma_\theta\)}{Parameter uncertainty matrix}
-\nomenclature[B]{\(\Sigma_Y\)}{Measurement covariance matrix}
-\nomenclature[B]{\(\Theta\)}{Parameter space}
-\nomenclature[B]{\(\theta\)}{Vector of analysed parameters}
-\nomenclature[B]{\(\Upsilon\)}{Decay coefficient}
-\nomenclature[B]{\(\varkappa\)}{An arbitrary function of \(\mathcal{A}\)}
-\nomenclature[B]{\(\Xi\)}{Matrix of experimental conditions}
-\nomenclature[B]{\(\xi\)}{Vector of experimental conditions}
+\nomenclature[C]{\(\alpha\)}{Temperature-dependent function in the P-R EoS \nomunit{[-]}}
+\nomenclature[C]{\(\Delta_\theta\)}{Residual term of the parameters \nomunit{g}}
+\nomenclature[C]{\(\Delta_y\)}{Residual term of the measurement error \nomunit{g}}
+\nomenclature[C]{\(\epsilon\)}{Unobservable error \nomunit{g}}
+\nomenclature[C]{\(\gamma\)}{Decaying function \nomunit{[-]}}
+\nomenclature[C]{\(\kappa\)}{Quadratic function of the acentric factor \nomunit{[-]}}
+\nomenclature[C]{\(\mu\)}{Sphericity coefficient \nomunit{[-]}}
+\nomenclature[C]{\(\phi\)}{Bed porosity \nomunit{[-]}}
+\nomenclature[C]{\(\pi\)}{Probability density \nomunit{[-]}}
+\nomenclature[C]{\(\rho_f\)}{Fluid density \nomunit{kg/$m^3$}}
+\nomenclature[C]{\(\rho_s\)}{Bulk density of solid \nomunit{kg/$m^3$}}
+\nomenclature[C]{\(\Sigma\)}{Covariance matrix \nomunit{[-]}}
+\nomenclature[C]{\(\Sigma_\theta\)}{Parameter uncertainty matrix \nomunit{[-]}}
+\nomenclature[C]{\(\Sigma_Y\)}{Measurement covariance matrix \nomunit{[-]}}
+\nomenclature[C]{\(\sigma\)}{Standard deviation \nomunit{[-]}}
+\nomenclature[C]{\(\Theta\)}{Parameter space \nomunit{[-]}}
+\nomenclature[C]{\(\theta\)}{Vector of analysed parameters \nomunit{[-]}}
+\nomenclature[C]{\(\Upsilon\)}{Decay coefficient \nomunit{[-]}}
+\nomenclature[C]{\(\varkappa\)}{An arbitrary function of \(\mathcal{A}\)}
+\nomenclature[C]{\(\Xi\)}{Matrix of experimental conditions \nomunit{[-]}}
+\nomenclature[C]{\(\xi\)}{Vector of experimental conditions \nomunit{[-]}}
 
 % Abbreviations
-\nomenclature[C]{BIC}{Broke-and-Intact Cell model}
-\nomenclature[C]{DoE}{Design of Experiment}
-\nomenclature[C]{HBD}{Hot Ball Diffusion}
-\nomenclature[C]{m-DoE}{Model-based Design of Experiment}
-\nomenclature[C]{P-R EoS}{Peng-Robinson Equation of State}
-\nomenclature[C]{SC}{Shrinking Core}
-\nomenclature[C]{SFE}{Supercritical Fluid Extraction}
+\nomenclature[D]{BIC}{Broke-and-Intact Cell model}
+\nomenclature[D]{DoE}{Design of Experiment}
+\nomenclature[D]{HBD}{Hot Ball Diffusion}
+\nomenclature[D]{m-DoE}{Model-based Design of Experiment}
+\nomenclature[D]{P-R EoS}{Peng-Robinson Equation of State}
+\nomenclature[D]{SC}{Shrinking Core}
+\nomenclature[D]{SFE}{Supercritical Fluid Extraction}
 \printnomenclature
 
+\clearpage
+\onecolumn
+\appendix
+\section{Literature Review} \label{CH: Literature}
+Table \ref{fig: SFE_Literature} provides a list of studies on SFE including the modeling part presented from 2014 onwards
+
+\begin{table*}[h!]
+	\centering
+	\resizebox{\textwidth}{!}{%
+	\begin{tabular}{|p{2.5cm}|p{2cm}|p{1.75cm}|p{4.5cm}|p{1.5cm}|p{1.5cm}|p{3cm}|}
+		\hline
+		\textbf{Reference} & \textbf{Substrate} & \textbf{Solvent} & \textbf{Model} & \textbf{T (°C)} & \textbf{P (MPa)} & \textbf{Flow-rate of CO$_2$} \\
+		\hline
+		\citet{Botelho2015} & Black sesame seed & CO$_2$ & BIC (\citet{Sovova1994}) \newline Local adsorption equilibrium model (\citet{Goto1993}) &  40, 60 & 20-40 & 5.9$\times 10^{-5}$ [kg/s]\\ \hline
+		\citet{Melo2014} & Eucalyptus globulus bark & CO$_2$, \newline Co-solvent: ethanol & Diffusion model (\citet{Crank1975}) \newline \citet{Brunner1994} \newline Desorption model (\citet{Cocero2001}) \newline SSP model (\citet{Gaspar2003})&  40 & 20 & 2.78$\times 10^{-3}$ [kg/s]\\ \hline
+		\citet{Liu2014} & Calycopteris floribunda leaves & CO$_2$, \newline Co-solvent: ethanol & BIC (\citet{Sovova1994}) \newline Diffusion model (\citet{Crank1975}) &  30–50 & 10-30 & 4.17$\times 10^{-4}$ [kg/s]\\ \hline
+		\citet{Tomita2014} & Rice bran & CO$_2$ & Partitioning coefficient model (\citet{Kubatova2002}) & 40–80 & 20-40 & 0.17-1.5$\times 10^{-4}$ [L/s]\\ 
+		\hline
+	\end{tabular} }
+	\caption{SFE studies encompassing modeling part}
+	\label{fig: SFE_Literature}
+\end{table*}
+
 \end{document}

### 2025-10-04 Article_Design_of_Experiment-Chamomile.tex
04.10

@@
 
+\usepackage[switch]{lineno}
+
 % --------------------------------------------------------------------
@@
 \section{Introduction}
-
+\linenumbers
 %\subfile{Sections/introduction_imp}
@@
 
+The aforementioned methods, along with many others, have been commonly employed for modeling the SFE process.
+Appendix \ref{CH: Literature} provides a list of studies on SFE, including modeling approaches, raw materials, and operating conditions.
+
 This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process.
@@
 
-		The residuals between the predicted and observed values were used to compute an unbiased estimate of the error variance.
+		The residuals between predicted and observed values were used to compute an unbiased estimate of the error variance.
 This variance, combined with the inverse of the design matrix's Gram matrix, yielded the covariance matrix of the coefficient estimates.
@@
 		\end{align}	}
+
+		The measurement error can be obtained based on the accuracy of the measuring device, or empirically from the spread of data around the model output.
+The first approach can be utilised only in the absence of external error sources.
+Given the imperfections of the experimental setup, such as delayed measurements and residuals of the product in pipes and the draining vessel, it was decided that the second approach is more suitable for this work.
+Based on the \citet{Sliczniuk2024}, the empirical measurement error was estimated to be 0.03.
 
@@
 					& P(t) \in \{100, 125, 150, 175, 200\} \, \text{bar}, \\
-					& 31^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\
+					& 30^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\
 					& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5}, \\
 					& \mathcal{R} = 
+					\begin{bmatrix} 
+						\mathcal{R}_{FF} & \mathcal{R}_{FT} \\ 
+						\mathcal{R}_{TT} & \mathcal{R}_{TF} 
+					\end{bmatrix}=
 					\begin{bmatrix} 
@@
 
+		To the authors knowledge, model-based dynamic design of experiments has not previously been applied to supercritical extraction, hence the authors cannot directly compare the obtained results against the literature.
+Nevertheless, some researchers proposed running an extraction process under dynamically changing operating conditions.
+For instance, \citet{Simandi1998} proposed a fractionated extraction of oregano with a stepwise increase in pressure (80, 120, 200, and 300 bar).
+As a result, the obtained yield curve exhibits non-monotonic patterns.
+\citet{Hiraga2025} suggested a pressure swing CO$_2$ extraction for the decaffeination of green coffee beans.
+The authors varied the pressure up and down during the operation, achieving a high degree of decaffeination with a reduced CO$_2$ supply.
+As a result, nearly 100\% decaffeination was achieved at 353 K and 30 MPa, using 80\% of the CO$_2$ supply compared to the case of constant pressure operation.
+Some of the extraction yield plots presented by \citet{Hiraga2025} are characterised by non-monotonic behaviour.
+It can be concluded that non-monotonic extraction curves have been reported in the literature.
+
 		The results and observations discussed in this article are local and should be considered valid only for the model presented in \citet{Sliczniuk2024}.
@@
 Moreover, the model predicts the data set in a region which has not been validated during previous experiments.
-On the one hand, this leaves room for model validation, while on the other hand, the obtained set of data points might differ from the predictions.
+This leaves room for model validation, while on the other hand, the obtained set of data points might differ from the predictions.
 
@@
 
-\clearpage
+%\clearpage
 %\newpage
@@
 \section{Literature Review} \label{CH: Literature}
-Table \ref{fig: SFE_Literature} provides a list of studies on SFE including the modeling part presented from 2014 onwards
+Table \ref{fig: SFE_Literature} provides a list of studies on SFE including the modelling part presented from 2014 onwards
 
@@
 		\citet{Liu2014} & Calycopteris floribunda leaves & CO$_2$, \newline Co-solvent: ethanol & BIC (\citet{Sovova1994}) \newline Diffusion model (\citet{Crank1975}) &  30–50 & 10-30 & 4.17$\times 10^{-4}$ [kg/s]\\ \hline
-		\citet{Tomita2014} & Rice bran & CO$_2$ & Partitioning coefficient model (\citet{Kubatova2002}) & 40–80 & 20-40 & 0.17-1.5$\times 10^{-4}$ [L/s]\\ 
-		\hline
+		\citet{Tomita2014} & Rice bran & CO$_2$ & Partitioning coefficient model (\citet{Kubatova2002}) & 40–80 & 20-40 & 0.17-1.5$\times 10^{-4}$ [L/s]\\ \hline
+		\citet{Kupski2017} & Hop pellet & CO$_2$ & BIC (\citet{Sovova1994}) \newline \citet{Reverchon1996} &  35-55 & 10-20 & 3.25$\times 10^{-5}$ [kg/s]\\ \hline
+		\citet{Pavlic2017} & Sage & CO$_2$ & \citet{Reverchon1996} \newline  \citet{Brunner1994} \newline \citet{Kandiah1990} &  40-60 & 10-30 & 5.56-11.1$\times 10^{-5}$ [kg/s]\\ \hline
+		\citet{Sartori2017} & Banana & CO$_2$ & \citet{Sovova1994} \newline  \citet{Reverchon1994} \newline \citet{Esquivel1999} &  40-80 & 20-50 & 1.01$\times 10^{-4}$ [L/s]\\ \hline
+		\citet{Hall2018} & Papaya seeds & CO$_2$ & \citet{Sovova1994} \newline  \citet{Goto1993} \newline \citet{Esquivel1999} &  40 & 15-30 & 6.11-19.4$\times 10^{-5}$ [kg/s]\\ \hline
+		\citet{Putra2018} & Peanut skin & CO$_2$, \newline Co-solvent: ethanol & \citet{Brunner1994} \newline \citet{Esquivel1999} &  40-70  & 10-30 & 5$\times 10^{-5}$ [L/s]\\ \hline
+		\citet{Putra2018} & Wheat germ & CO$_2$ & \citet{Brunner1994} \newline \citet{Esquivel1999} \newline \citet{Kandiah1990} \newline \citet{Reverchon1994} &  40-60  & 25-35 & 0.56 - 1.11 $\times 10^{-4}$ [kg/s]\\ \hline
+		\citet{Pavlic2020} & Raspberry seed & CO$_2$ & \citet{Brunner1994} \newline \citet{Esquivel1999} \newline \citet{Kandiah1990} \newline \citet{Reverchon1994} &  40-60  & 25-35 & 0.56 - 1.11 $\times 10^{-4}$ [kg/s]\\ \hline
+		\citet{Priyanka2020} & Carrot seed & CO$_2$, \newline Co-solvent: ethanol & BIC (\citet{Sovova1994}) \newline \citet{Reverchon1997} &  50-70  & 20-40 & 0.83 - 2.5 $\times 10^{-4}$ [kg/s]\\ \hline
+		\citet{Casas2021} & Acacia dealbata - ﬂowers & CO$_2$, \newline Co-solvent: ethanol & \citet{Esquivel1999} \newline \citet{Sovova1994} &  35-55  & 10-35 & 4.17 $\times 10^{-4}$ [kg/s]\\ \hline
+		\citet{Acosta2014} & Wood (\textit{Mezilaurus itauba}) & CO$_2$, \newline Co-solvent: ethanol (2\%, 5\%, 8\%) & BIC(\citet{Sovova1994}) &  38-52  & 8-22 & 5 $\times 10^{-5}$ [L/s]\\ \hline
+		\citet{Zekovic2014} & \textit{Ocimum basilicum L.} & CO$_2$ & \citet{Brunner1994} \newline \citet{Kandiah1990} \newline \citet{Esquivel1999} &  40-60  & 10-30 & 2.71 $\times 10^{-2}$ [L/s]\\ \hline
 	\end{tabular} }

### 2025-10-11 Article_Design_of_Experiment-Chamomile.tex
11.10

@@
 
-		{\footnotesize \begin{equation} j_L(\Xi) = \operatorname{trace} \left( Q \mathcal{A}^{-1}(\theta, \Xi) Q^\top \right) \end{equation} }
+		{\footnotesize 
+			\begin{equation} 
+				j_L(\Xi) = \operatorname{trace} \left( Q \mathcal{A}^{-1}(\theta, \Xi) Q^\top \right) 
+			\end{equation} }
 
@@
 
-		{\footnotesize \begin{equation} j_D(\Xi) = \det \mathcal{A}(\theta, \Xi) \end{equation} }
+		{\footnotesize 
+			\begin{equation} \label{EQ:D-optimality}
+				j_D(\Xi) = \det \mathcal{A}(\theta, \Xi) 
+			\end{equation} }
 
@@
 The matrix $\mathcal{R}$ represents the control cost matrix, with its entries chosen so that the control costs are one order of magnitude lower than $-\ln j_D$.
+The Appendix \ref{CH: Penalty_Terms} discusses in detail the selection of penalty weights and their impact on the final solution, namely $\mathcal{R}_{FF}$ and $\mathcal{R}_{TT}$.
 The problem formulation is given by Equation \ref{EQ:Formulation_2}:
@@
 
+\newpage
+\twocolumn
+\section{Analysis of the penalty terms weights} \label{CH: Penalty_Terms}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{Figures/Results/Y_Penalty_Analysis.png}
+	\caption{Yield curves obtained at different values of penalty terms}
+	\label{fig:Penalty_Analysis_Y}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{Figures/Results/T_Penalty_Analysis.png}
+	\caption{Inlet temperature profiles obtained at different values of penalty terms}
+	\label{fig:Penalty_Analysis_T}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{Figures/Results/F_Penalty_Analysis.png}
+	\caption{Mass flow rate profiles obtained at different values of penalty terms}
+	\label{fig:Penalty_Analysis_F}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{Figures/Results/Y_diff_Penalty_Analysis.png}
+	\caption{Yield curves obtained at different values of penalty terms}
+	\label{fig:Penalty_Analysis_Y_diff}
+\end{figure}
+
+To solve the optimization problem formulated by Equation \ref{EQ:Formulation_2}, it is necessary accurately solve the D-optimality criterion (given by Equation \ref{EQ:D-optimality}) but also to avoid unfeasible inputs which are difficult to incorporate the real life experiments.
+The penalty term is introduced into the objective function to ensure that the optimal solution doesn't exhibit properties of bang-bang control, which is forced by penalising rapid changes of the input variables.
+The weights of matrix $\mathcal{R}$ must be carefully selected to not distort the main problem (the D-optimality), and as such the value of the penalty terms should be less that the objective function itself.
+It is assumed that the inputs are independent and can be changed simultaneously, which translates to $\mathcal{R}_{FT}=\mathcal{R}_{TF}=0$.
+To decide on values of the renaming terms, namely $\mathcal{R}_{FF}$ and $\mathcal{R}_{TT}$, the same DoE problem was solved with different values of the penalty term as presented in Table \ref{tab:Penalty_Analysis}.
+
+\begin{table}[h!]
+	\centering
+	\resizebox{0.75\columnwidth}{!}{%
+		\begin{tabular}{ l| c | c | c | c | c  }
+			\hline
+			Simulation Case    & 1 &  2   &  3   &  4   &  5   \\ \hline
+			$\mathcal{R}_{FF}$ & 0 & 1e-2 & 1e-1 & 1e-0 & 1e-2 \\ \hline
+			$\mathcal{R}_{TT}$ & 0 & 1e-3 & 1e-2 & 1e-1 & 1e-1 \\ \hline
+		\end{tabular}%
+	}
+	\caption{Simulation cases for impact assessment of $\mathcal{R}$}
+	\label{tab:Penalty_Analysis}
+\end{table}
+
+All the simulation cases are solved starting from the same randomly generated input.
+It is noted that the purpose of this section is identification of the sufficient values for penalty terms, but not to obtain the optimal solution.
+Given that, the optimization problem is solved only once, and the obtain solution might not be globally optimal.
+The methodology on how to obtain global or near-global solution is presented in the main body of this manuscript.
+
+As presented in Figures \ref{fig:Penalty_Analysis_Y}, the obtained yield curves differs each other slightly.
+
 \end{document}
